---
title: "Exploratory_Analysis_Bias"
author: "Fournier Raphaël"
date: "`r Sys.Date()`"
output: html_document
---
## load packages ##
```{r load-pkg}
pkxg <- c("EMC2", "tidyverse", "RColorBrewer", "patchwork", "tidybayes", "DataExplorer","ggpubr", "paletteer")

lapply(pkxg, library, character.only = TRUE)
```

## plot settings ##

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face="bold"), 
          title = element_text(size = 18, face="bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

Load model
```{r}
#Exploratory model (with bias allowed to vary depending on the Response key)
load("Exp_1/models/LBA_exp1_v1_bias.RData")
```

#Quick plots
```{r}
#Bias model
plot_pars(LBA_exp1_v1_bias,selection="mu",layout=c(2,5), map = TRUE)
posterior_summary(LBA_exp1_v1_bias,selection="alpha",probs = c(0.025, 0.5, 0.975),map = TRUE)#for each participant
posterior_summary(LBA_exp1_v1_bias,selection="mu",probs = c(0.025, 0.5, 0.975),map = TRUE)#at group level
```

#Parameters per subjects
```{r}
#Remember:number of iters = 10000 / number of chains = 3 -> 10'000 x 30(subjects) x 3(number of chains) = 900'000 obs for each parameter
#Bias model
param_2_pid = EMC2::parameters(LBA_exp1_v1_bias, selection = "alpha", resample = TRUE, N = NULL)
```


###Model 2: bias
```{r}
split_tibble <- function(tibble, col = 'col') tibble %>% split(., .[, col])
array_theta_2 <- split_tibble(param_2_pid, "subjects")
array_theta_2<-do.call(rbind, array_theta_2)
array_theta_pid_2 <- array_theta_2 %>%
  pivot_longer(cols = c("v_SNovel:lMFALSE", "v_SLearned:lMFALSE", "v_SNovel:lMTRUE", "v_SLearned:lMTRUE", "sv_lMTRUE", "B_lRNovel", "B_lRLearned", "A_lRNovel", "A_lRLearned", "t0"), names_to = "param", values_to = "value")%>%
  add_column(datapoint = rep(1:30000,each=10,times=30))%>%
  rename(pid=subjects)
```


```{r}
theta_group_2 <- array_theta_pid_2 %>%
  group_by(datapoint,param) %>% 
  summarise(value = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  add_column(pid = "average") %>% ## add a column which makes clear it is the avg. not needed but useful for plotting later
  relocate(pid, .before = everything())
head(theta_group_2)
glimpse(theta_group_2)
```


## calculate quantiles ##

calculate quantiles per parameter at the group level

```{r}
library(tidybayes)
theta_group_2_q <- theta_group_2 %>%
  group_by(param) %>% 
  median_qi(value)
theta_group_2_q
```


and do the same per pid

```{r}
theta_pid_2_q <- array_theta_pid_2 %>%
  group_by(pid, param) %>% 
  median_qi(value)
theta_pid_2_q
```

## some quick and dirty plots with all of the parameters ##

plot the distribution per parameter using a tidybayes halfeye plot

```{r}
p2.1 <- ggplot(theta_group_2, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9) +
  labs(x = "parameter estimate", y = "") 
p2.1

ggsave("Exp_1/figures/all_params_2.jpeg",
       width = 8, height = 6)
```

plot avg and individual pid parameters

```{r}
p2.2 <- ggplot(theta_group_2, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9, position = position_nudge(y=-0.5)) +
  geom_pointinterval(data = theta_pid_2_q, aes(xmin=.lower, xmax=.upper, 
                                           colour = pid, fill = pid),
                     position = position_dodge(width = 0.7)) +
  labs(x = "parameter estimate", y = "") +
  facet_wrap(~param, scales = "free_y") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
p2.2

ggsave("Exp_1//figures/all_params_pid_2_1.jpeg",
       width = 8, height = 6)
```

# section 3 #

## plot thresholds separately ##

first, wrangle to make a separate dfs

thresholds df per pid

```{r}
thresh_pid_2 <- array_theta_pid_2 %>% 
  filter(str_detect(param, "B_")) %>% 
  mutate(response = if_else(str_detect(param, "lRNovel"), "Novel", "Learned"),
         response = factor(response,
                            levels = c("Novel", "Learned")))
head(thresh_pid_2)
str(thresh_pid_2)
summary(thresh_pid_2)

## data check
thresh_pid_2 %>% 
  distinct(param, response)
```



thresholds at the group level

```{r}
thresh_group_2 <- theta_group_2 %>% 
  filter(str_detect(param, "B_")) %>% 
  mutate(response = if_else(str_detect(param, "lRLearned"), "Learned", "Novel"),
         response = factor(response,
                            levels = c("Learned", "Novel")))
head(thresh_group_2)
str(thresh_group_2)
summary(thresh_group_2)
```

## plot ##



at the group level

```{r}
p3.1 <- ggplot(thresh_group_2, aes(x = value, y = fct_rev(response))) +
  stat_halfeye(alpha = 0.7, aes(fill = fct_rev(response))) +
  scale_fill_brewer(palette = "Paired") +
  scale_colour_brewer(palette = "Paired")  +
  labs(y="Response", x="Threshold", title=bquote("Group level: 
Threshold by key-press")) +
  labs(fill = "Response")
p3.1

## save a figure
 ggsave("Exp_1/figures/thresh2_bias.jpeg",width = 10, height = 6)
```

## caluclate a threshold response key difference ##

per pid

```{r}
thresh_diff_pid_2 <- thresh_pid_2 %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Novel - Learned)
head(thresh_diff_pid_2)
```



at the group level

```{r}
thresh_diff_2 <- thresh_group_2 %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Novel - Learned)
head(thresh_diff_2)
```

## quantiles on the difference score ##

per pid

```{r}
thresh_diff_pid_2_q <- thresh_diff_pid_2 %>%
  group_by(pid) %>% 
  median_qi(diff)
thresh_diff_pid_2_q
```

at the group level

```{r}
thresh_diff_2_q <- thresh_diff_2 %>%
  group_by(pid) %>%
  median_qi(diff)
thresh_diff_2_q
```

## plot the threshold difference score ##

plot the average difference

```{r}
p3.2 <- ggplot(thresh_diff_2, aes(x = diff, y = "")) +  
  stat_halfeye(alpha = 0.9, fill="firebrick") +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level: 
Threshold (unfamiliar > familiar)", 
       x = "Threshold", y="") 
p3.2
```

plot individual pids

```{r}
thresh_diff_pid_2$pid = with(thresh_diff_pid_2, reorder(pid, diff, mean))
p3.3 <- ggplot(thresh_diff_pid_2, aes(x = diff, y = pid,
                                    fill=pid)) +  
  stat_halfeye(alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Participant level: Threshold (unf_key > fam_key)", 
       x = "Threshold", y="participant") 
p3.3
```

plot the average difference and individual pids

```{r}
p3.4 <- ggplot(thresh_diff_2, aes(x = diff, y= pid)) +  
  stat_halfeye(alpha = 0.9, fill="firebrick",
               position = position_nudge(y=0)) +
  stat_halfeye(data = thresh_diff_pid_2,
               alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Threshold (unf_key > fam_key)", 
       x = "Threshold", y="participant ID")
p3.4
```

## plot together ##

```{r}
p3.5 <- p3.1 / p3.2 | p3.3 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.5

# save a figure
 ggsave("Exp_1/figures/thresh2.jpeg",
        width = 21, height = 10)
```

and now combine avg and pid difference plots

```{r}
p3.6 <- p3.1 | p3.2 +
  labs(caption = "80% and 95% credible intervals shown in black")
p3.6

# save a figure
ggsave("Exp_1/figures/thresh2_2.jpeg",
       width = 15, height = 10)
```

```{r}
p3.6 <- p3.1 | p3.4 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.6

# save a figure
ggsave("Exp_1/figures/thresh2_3.jpeg",
       width = 21, height = 10)
```


the exact layout, labels of factors and arrangement may need polishing and re-arranging.

But for now, the data seem to be what we want.

# section 4 #

## plot drift rate separately ##

## wrangle ##

create a drift-rate df

```{r}
drift_rate_pid_2 <- array_theta_pid_2 %>% 
  filter(str_detect(param, "v_S")) %>% 
  mutate(condition = if_else(str_detect(param, "Novel"), "Novel", "Learned"),
         accuracy = if_else(str_detect(param, "TRUE"), "True", "False"),
         condition = factor(condition,
                            levels = c("Novel", "Learned")),
         accuracy = factor(accuracy,
                            levels = c("False", "True")))
head(drift_rate_pid_2)
str(drift_rate_pid_2)
summary(drift_rate_pid_2)

## data check
drift_rate_pid_2 %>% 
  distinct(param, condition, accuracy)
```


drift rate at the group level

```{r}
drift_rate_group_2 <- theta_group_2 %>% 
  filter(str_detect(param, "v_S")) %>% 
  mutate(condition = if_else(str_detect(param, "Novel"), "Novel", "Learned"),
         accuracy = if_else(str_detect(param, "TRUE"), "True", "False"),
         condition = factor(condition,
                            levels = c("Novel", "Learned")),
         accuracy = factor(accuracy,
                            levels = c("False", "True"))) 
head(drift_rate_group_2)
str(drift_rate_group_2)
summary(drift_rate_group_2)
```

## plot ##

#Create a custom manual colour scale: drift_rate group

```{r}
library(RColorBrewer)
myColors_drift <- RColorBrewer::brewer.pal(12, "Dark2")[4:5]
names(myColors_drift) <- levels(drift_rate_group_2$accuracy)
colScale_drift <- scale_fill_manual(name = "accuracy", values = myColors_drift)
```

the average

```{r}
p4.1 <- ggplot(drift_rate_group_2, aes(x = value, y = fct_rev(condition), 
                               fill = accuracy)) +
  stat_halfeye(alpha = 0.7) +
  colScale_drift +
  labs(title = "Group level: True and False 
drift rate by familiarity condition", y="Familiarity", x="Drift rate") +
  guides(fill = guide_legend(title = "Accuracy"))
p4.1

ggsave("Exp_1/figures/drift_rate_2_bias.jpeg",
        width = 10, height = 6)
```

and now facet by pid

```{r}
p4.2 <- ggplot(drift_rate_pid_2, aes(x = value, y = fct_rev(condition), 
                               fill = accuracy)) +
  stat_halfeye(alpha = 0.7) +
  colScale_drift +
  labs(title = "Participant level: Drift-rate by condition",
       y="condition", x="Drift rate") +
  facet_wrap(~pid)
p4.2
```

take a look together

```{r}
p4.1 / p4.2
ggsave("Exp_1/figures/drift_rate_true_false_2.jpeg", 
       width = 16, height = 13)
```

## caluclate drift rate differences between conditions and accuracy ##

per pid

```{r}
## just true > false differences (accuracy)
drift_acc_diff_pid_2 <- drift_rate_pid_2 %>%
  pivot_wider(id_cols = -param,
               names_from = accuracy,
               values_from = value) %>%
  mutate(diff = True - False)
drift_acc_diff_pid_2

## unf > fam differences
drift_acc_cond_diff_pid_2 <- drift_acc_diff_pid_2 %>%
  pivot_wider(id_cols = -c("True", "False"), 
              names_from = condition,
              values_from = diff) %>%
  mutate(diff = Novel - Learned)
drift_acc_cond_diff_pid_2
```

at the group level

```{r}
## just true > false differences (accuracy)
drift_acc_diff_2 <- drift_rate_group_2 %>%
  pivot_wider(id_cols = -param,
               names_from = accuracy,
               values_from = value) %>%
  mutate(diff = True - False)
drift_acc_diff_2

## unf > fam differences
drift_acc_cond_diff_2 <- drift_acc_diff_2 %>%
  pivot_wider(id_cols = -c("True", "False"), 
              names_from = condition,
              values_from = diff) %>%
  mutate(diff = Novel - Learned)
drift_acc_cond_diff_2
```

## plot the differences ##

differences between true and false, separately for unf and fam

at the group average level

```{r}
myColors_drift_diff <- RColorBrewer::brewer.pal(12, "Paired")[c(1,2)]
names(myColors_drift_diff) <- levels(drift_acc_diff_2$condition)
colScale_drift_diff <- scale_fill_manual(name = "fct_rev(condition)", values = myColors_drift_diff)
```


plot

```{r}
p4.3 <- ggplot(drift_acc_diff_2, aes(x = diff, y = fct_rev(condition))) +
  stat_halfeye(aes(fill = condition), alpha = 0.7) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level: Drift rate (True > false)
by familiarity condition",
       x="Drift rate", y="Familiarity") +
  theme(legend.position = "none")
p4.3
```

quantiles

```{r}
drift_acc_diff_2_q <- drift_acc_diff_2 %>%
  group_by(condition) %>% 
  median_qi(diff)
drift_acc_diff_2_q
```

difference between unf (true and false) > fam (true > false)

plot

```{r}
p4.4 <- ggplot(drift_acc_cond_diff_2, aes(x = diff, y = "")) +
  stat_halfeye(fill = "firebrick", alpha = 0.9) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level:Drift rate (Novel > Learned)",
       x="Drift rate", y="") +
  xlim(0,5)
p4.4
```

quantiles

```{r}
drift_acc_cond_diff_2_q <- drift_acc_cond_diff_2 %>%
  median_qi(diff)
drift_acc_cond_diff_2_q
```

## plot together ##

```{r}
p4.5 <- p4.3 | p4.4 +
  labs(caption = "80% and 95% credible intervals shown in black")
p4.5

# save a figure
ggsave("Exp_1/figures/drift_rat_mini_2_bias.jpeg",
       width = 15, height = 10)
```

## plot the average difference and pid differences ##

```{r}
drift_acc_cond_diff_pid_2$pid = with(drift_acc_cond_diff_pid_2, reorder(pid, diff, mean))
p4.6 <- ggplot(drift_acc_cond_diff_2, aes(x = diff, y=pid)) +  
  stat_halfeye(alpha = 0.9, fill="firebrick") +
  stat_halfeye(data = drift_acc_cond_diff_pid_2,
               alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Individual and average 
drift rate difference", 
       x = "Drift rate", y="participant ID") 
p4.6
```

## combine drift rate plots ##

```{r}
p4.7 <- p4.3 / p4.4 | p4.6 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p4.7 

# save a figure
ggsave("Exp_1/figures/drift_rate_pid_2.jpeg",
       width = 15, height = 10)
```


## plot bias separately ##
```{r}
bias_pid <- array_theta_pid_2 %>% 
  filter(str_detect(param, "A_")) %>% 
  mutate(response = if_else(str_detect(param, "lRNovel"), "Novel", "Learned"),
         response = factor(response,
                            levels = c("Novel", "Learned")))
head(bias_pid)
str(bias_pid)
summary(bias_pid)

## data check
bias_pid %>% 
  distinct(param, response)
```

bias at the group level

```{r}
bias_group <- theta_group_2 %>% 
  filter(str_detect(param, "A_")) %>% 
  mutate(response = if_else(str_detect(param, "lRLearned"), "Learned", "Novel"),
         response = factor(response,
                            levels = c("Learned", "Novel")))
head(bias_group)
str(bias_group)
summary(bias_group)
```

## plot ##



at the group level

```{r}
p3.1 <- ggplot(bias_group, aes(x = value, y = fct_rev(response))) +
  stat_halfeye(alpha = 0.7, aes(fill = fct_rev(response))) +
  scale_fill_brewer(palette = "Paired") +
  scale_colour_brewer(palette = "Paired")  +
  labs(y="Response", x="Bias parameter", title=bquote("Group level: 
Bias by key-press")) +
  labs(fill = "Response")
p3.1

## save a figure
 ggsave("Exp_1/figures/bias_2_bias.jpeg",width = 10, height = 6)
```

## calculate a bias response key difference ##

per pid

```{r}
bias_diff_pid <- bias_pid %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Novel - Learned)
head(bias_diff_pid)
```

at the group level

```{r}
bias_diff <- bias_group %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Novel - Learned)
head(bias_diff)
```

## quantiles on the difference score ##

per pid

```{r}
bias_diff_pid_q <- bias_diff_pid %>%
  group_by(pid) %>% 
  median_qi(diff)
bias_diff_pid_q
```

at the group level

```{r}
bias_diff_q <- bias_diff %>%
  group_by(pid) %>%
  median_qi(diff)
bias_diff_q
```

## plot the threshold difference score ##

plot the average difference

```{r}
p3.2 <- ggplot(bias_diff, aes(x = diff, y = "")) +  
  stat_halfeye(alpha = 0.9, fill="firebrick") +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level: 
Bias (Novel > Learned)", 
       x = "Bias", y="") 
p3.2
```

plot individual pids

```{r}
bias_diff_pid$pid = with(bias_diff_pid, reorder(pid, diff, mean))
p3.3 <- ggplot(bias_diff_pid, aes(x = diff, y = pid,
                                    fill=pid)) +  
  stat_halfeye(alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Participant level: Bias (Novel > Learned)", 
       x = "Bias", y="participant") 
p3.3
```

plot the average difference and individual pids

```{r}

p3.4 <- ggplot(bias_diff, aes(x = diff, y=pid)) +  
  stat_halfeye(data = bias_diff_pid,
               alpha = 0.7) +
    stat_halfeye(alpha = 0.9, fill="firebrick",
               position = position_nudge(y=0)) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Bias (Novel > Learned)", 
       x = "Bias", y="participant ID")
p3.4
```

## plot together ##

```{r}
p3.5 <- p3.1 / p3.2 | p3.3 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.5

# save a figure
 ggsave("Exp_1/figures/bias_2_bias.jpeg",
        width = 21, height = 10)
```

and now combine avg and pid difference plots

```{r}
p3.6 <- p3.1 | p3.2 +
  labs(caption = "80% and 95% credible intervals shown in black")
p3.6

# save a figure
ggsave("Exp_1/figures/bias2_2.jpeg",
       width = 15, height = 10)
```

```{r}
p3.6 <- p3.1 | p3.4 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.6

# save a figure
ggsave("Exp_1/figures/bias2_3.jpeg",
       width = 21, height = 10)
```



### Criterion and correlations with bias parameter

#Compute and plot correlation: D' - Drift rate diff.

Decision criterion computation: (-z(hit rate) + z(false alarm rate))/2

#Load data
```{r}
data<-read_csv("/Users/rfournier/Rstudio/EMC_WP1_1/EMC_WP1_1/data/data.csv")
```
```{r}
source("dprime_lab.R") # label indiviudal trilas (i.e., rows in a dataframe) as hits, false alarm, or correct rejection

source("dprime_cat.R") # total number of hits, misses, false alarms, and correct rejections for each participant
```

#Calculate Hit rate and False Alarm rate
```{r}
data_prime <- data %>%
  mutate(keys = if_else(keypress == "q", "fam", "unf"),
         keys = as.factor(keys)) %>%
  select(pid,cond,keys,acc) %>%
  rename(correct = acc)


data_prime.dprime <- dprime_lab("cond", "keys", "correct", data = data_prime)
df.cat <- dprime_cat(data_prime.dprime,pid)
```

#Compute criterion
```{r}
criterion <- df.cat %>%
  mutate(hit_rate_fam = Hits/TotalTarg,
         false_alarm_fam = FalseAlarms/TotalDis,
         hit_rate_unf = CorrectRejs/TotalDis,
         false_alarm_unf = Misses/TotalTarg,
         criterion_fam = -(qnorm(hit_rate_fam) - qnorm(false_alarm_unf))/2,
         criterion_unf = -(qnorm(hit_rate_unf) - qnorm(false_alarm_fam))/2) %>%
  mutate(pid = as.numeric(as.factor(pid)))%>%
  filter(!false_alarm_fam == 0)
```

#Plotting criterion

```{r}
#More wrangle for correlations plotting
test_bias <- theta_pid_2_q %>%
  select(pid,param,value) %>%
  pivot_wider(names_from = param, values_from = value)
bias_corr <- test_bias %>%
  select(pid,A_lRfam, A_lRunf) %>%
  rename(Bias_Learned = "A_lRfam", Bias_New = "A_lRunf") %>%
  select(pid,Bias_Learned,Bias_New) %>%
  mutate(pid = as.numeric(as.factor(pid))) %>%
  filter(!pid == "1",
         !pid == "27")

bias_corr$crit_fam = criterion$criterion_fam
bias_corr$crit_unf = criterion$criterion_unf

```

```{r}
c_plot <- bias_corr %>%
  select(pid, crit_fam, crit_unf) %>%
  rename(Learned = "crit_fam", New = "crit_unf") %>%
  pivot_longer(!pid, names_to = "cond", values_to = "Criterion") %>%
  group_by(cond) %>%
  median_qi(Criterion) %>% 
  mutate(sd = sd(Criterion))%>% 
  ggplot(aes(cond, Criterion, fill = cond)) +
    geom_col() +
    geom_errorbar(aes(cond, ymin = Criterion-sd, ymax = Criterion+sd), width = 0.4, colour= "black", alpha = .9) +
    xlab("Condition") +
    ylab("d'") +
    labs(title = "Criterion per condition") +
    ylim(-2,0.5) 
c_plot
ggsave("figures/crit_comp.jpeg")
```
Corr plots
```{r}
#Learned faces
bias_corr <- bias_corr %>%
  rename(Criterion_Learned = "crit_fam", Criterion_New = "crit_unf")
mat_cor<-plot_correlation(bias_corr[2:5])
mat_cor
ggsave("figures/mat_cor_bias.jpeg")
c1 <- ggplot(bias_corr, aes(x = Bias_Learned, y = Criterion_Learned)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y~x)+
  labs(title = "Learned faces: Correlation between criterion 
and bias parameter") +
  xlab("Bias for Learned faces")+
  ylab("Criterion for Learned faces") +
  stat_cor(method = "pearson")
c1
ggsave("figures/learned_corr_bias.jpeg", width = 10, height = 6)
#New faces
c2 <- ggplot(bias_corr, aes(x = Bias_New, y = Criterion_New)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y~x)+
  labs(title = "Learned faces: Correlation between criterion 
and bias parameter") +
  xlab("Bias for New faces")+
  ylab("Criterion for New faces")+
  stat_cor(method = "pearson")
c2
ggsave("figures/new_corr.jpeg", width = 10, height = 6)
```



