---
title: "model"
author: "Raph & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

This file fits the pre-registered LBA model for Exp 1 in the face familiarity study.

```{r}
#| label: setup
#| include: false

pkgs <- c(
  "EMC2", "tidyverse", "RColorBrewer", "patchwork", "here"
  )
vapply(
  pkgs, library, logical(1), character.only = TRUE, logical.return = TRUE
  )

```

# 1. read in the raw data and wrangle

raw data

```{r}
raw <- read_csv("exp_1/data/data_exp_1.csv")
head(raw)
glimpse(raw)
```

wrangle 

```{r}
data_emc <- raw |>
  select(pid, cond, keypress, rt) |>
  rename(subjects = pid, S = cond, R = keypress) |>
  mutate(
    subjects = factor(subjects),
    S = factor(S,
      levels = c("Novel", "Learned")
    ),
    R = if_else(R == "q", "Learned", "Novel"),
    R = factor(R,
      levels = c("Novel", "Learned")
    )
  ) |>
  as.data.frame() ## in DMC, post predict need a df and not a tibble. Same for EMC2 I think.
head(data_emc)
str(data_emc)
```

# 2. Preregistered model #

# 2.1 build model #

## set the match factor  ##

```{r}
matchfun=function(d)d$S==d$lR
```

```{r}
design_exp1_v1 <- design(
  data = data_emc, model = LBA, matchfun = matchfun,
  formula = list(v ~ 0 + S:lM, sv ~ 0 + lM, B ~ 0 + lR, A ~ 1, t0 ~ 1),
  constants = c(sv_lMFALSE = log(1))
)
```

```{r}
p_vector <- c(
  "v_SNovel:lMFALSE" = 4, "v_SLearned:lMFALSE" = 4, "v_SNovel:lMTRUE" = 4, "v_SLearned:lMTRUE" = 4,
  sv_lMTRUE = log(.5),
  B_lNovel = log(2), B_lRLearned = log(2),
  A = log(.5), t0 = log(.3)
)

mapped_pars(p_vector, x = design_exp1_v1)
```

## set priors ##

I made the A and t0 sd priors smaller as they are fixed values and it seemed odd to sample a wide range when they are fixed at .5 and .3, respectively.

```{r}
mu_mean <- c(
  "v_SNovel:lMFALSE" = 0, "v_SLearned:lMFALSE" = 0, "v_SNovel:lMTRUE" = 1, "v_SLearned:lMTRUE" = 1,
  sv_lMTRUE = log(.5),
  B_lRNovel = log(1), B_lRLearned = log(1),
  A = log(.5), t0 = log(.3)
)

mu_sd <- c(
  "v_SNovel:lMFALSE" = 2, "v_SLearned:lMFALSE" = 2, "v_SNovel:lMTRUE" = 2, "v_SLearned:lMTRUE" = 2,
  sv_lMTRUE = .5,
  B_lRNovel = .5, B_lRLearned = .5,
  A = .3, t0 = .3
)

prior_exp1_v1 <- prior(design_exp1_v1, type = "standard", mu_mean = mu_mean, mu_sd = mu_sd)

plot(x = prior_exp1_v1)
```            

## fit the model ##

Note that I changed iter and step_size to make the model fit better and sample quicker.

```{r}
LBA_exp1_v1 <- make_emc(data_emc, design_exp1_v1, type = "standard", prior = prior_exp1_v1)
LBA_exp1_v1 <- fit(LBA_exp1_v1,
  cores_per_chain = 3, fileName = "exp_1/models/tmp.RData",
  iter = 10000, step_size = 500
)
save(LBA_exp1_v1, file = "exp_1/models/LBA_exp1_v1.RData")
load("exp_1/models/LBA_exp1_v1.RData")
```

# 2.2 check the model #

convergence 
efficiency

```{r}
check(LBA_exp1_v1)
get_pars(LBA_exp1_v1, map = TRUE)
```

plot pars

```{r}
plot_pars(LBA_exp1_v1,selection="mu",layout=c(2,5))
```

# 2.3 calculate and plot posterior predictions #

```{r}
pp_LBA_exp1_v1 <- predict(LBA_exp1_v1, n_cores = 10)
save(pp_LBA_exp1_v1, file = "exp_1/models/pp_LBA_exp1_v1.RData")
plot_fit(data_emc, pp_LBA_exp1_v1, factors = c("S"), layout = c(2, 3))
```
