---
title: "Modelling_Exp1_full_emc2"
author: "Fournier Raphaël"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load the libraries that we will be using #

## load packages ##

```{r load-pkg}
pkxg <- c("EMC2", "tidyverse", "RColorBrewer", "patchwork")

lapply(pkxg, library, character.only = TRUE)
```

## plot settings ##

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face="bold"), 
          title = element_text(size = 18, face="bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 1. read in the raw data and wrangle

## read in the wrangled data ##

Load data (30 pids)

```{r}
raw <- read_csv("data/data.csv")
head(raw)
str(raw)
```

Wrangle
```{r}
data_emc <- raw %>%
  select(pid, cond, keypress, rt) %>% 
  rename(subjects = pid, S = cond, R = keypress) %>% 
  mutate(subjects=factor(subjects),
         S=factor(S,
                  levels = c("unf", "fam")),
         R=if_else(R == "q", "fam", "unf"),
         R=factor(R,
                  levels = c("unf", "fam"))) %>% 
  as.data.frame() ## in DMC, post predict need a df and not a tibble. Same for EMC2 I think.
head(data_emc)
str(data_emc)
```
# 2. build model with t0 #

## set the match factor  ##

```{r}
matchfun=function(d)d$S==d$lR
```

```{r}
design_exp1_v1_full <- design(data = data_emc,model=LBA,matchfun=matchfun,
                       formula=list(v~0+S:lM,sv~0+lM,B~0+lR,A~0+lR,t0~0+S),
                       constants=c(sv_lMFALSE=log(1)))
```

```{r}
p_vector_full <- c("v_Sunf:lMFALSE"=4,"v_Sfam:lMFALSE"=4, "v_Sunf:lMTRUE"=4, "v_Sfam:lMTRUE"=4,
              sv_lMTRUE=log(.5), 
              B_lRunf=log(2), B_lRfam=log(2),
              A_lRunf=log(.5), A_lRfam = log(.5),
              t0_Sunf=log(.3),t0_Sfam=log(.3))

mapped_par(p_vector_full, design_exp1_v1_full)
```

## set priors ##

try to copy dmc priors.

I made the t0 and sd priors smaller as they are fixed values and it seemed odd to sample a wide range when they are fixed at .5 and .3, respectively.

```{r}
mu_mean_full=c("v_Sunf:lMFALSE"=0,"v_Sfam:lMFALSE"=0, "v_Sunf:lMTRUE"=1, "v_Sfam:lMTRUE"=1,
          sv_lMTRUE=log(.5), 
          B_lRunf=log(1), B_lRfam=log(1),
          A_lRunf=log(.5), A_lRfam = log(.5),
          t0_Sunf=log(.3),t0_Sfam=log(.3))

mu_sd_full=c("v_Sunf:lMFALSE"=2,"v_Sfam:lMFALSE"=2, "v_Sunf:lMTRUE"=2, "v_Sfam:lMTRUE"=2,
          sv_lMTRUE=.5, 
          B_lRunf=.5, B_lRfam=.5,
          A_lRunf=.3, A_lRfam = .3,
          t0_Sunf=log(.3),t0_Sfam=log(.3))

prior_exp1_v1_full <- prior(design_exp1_v1_full, type ='standard',mu_mean=mu_mean_full,mu_sd=mu_sd_full)

plot_prior(prior = prior_exp1_v1_full, design = design_exp1_v1_full,layout=c(3,3))
```            

## fit the model ##

Note that I changed iter and step_size to make the model fit better and sample quicker.

```{r}
LBA_exp1_v1_full <- make_emc(data_emc,design_exp1_v1_full,type="standard",  prior=prior_exp1_v1_full)
LBA_exp1_v1_full <- fit(LBA_exp1_v1_full, cores_per_chain = 3, fileName="models/tmp.RData",
                     iter = 10000, step_size = 500)
save(LBA_exp1_v1_full,file="models/LBA_exp1_v1_full.RData") 
load("models/LBA_exp1_v1_full.RData")
```

# 3. check the model #

convergence 
efficiency?

```{r}
check(LBA_exp1_v1_full)
get_pars(LBA_exp1_v1_full, map = TRUE)
```

plot pars

```{r}
plot_pars(LBA_exp1_v1_full,selection="mu",layout=c(2,5))
```

# 4. calculate and plot posterior predictions #

```{r}
pp_LBA_exp1_v1_full <- predict(LBA_exp1_v1_full, n_cores = 10)
save(pp_LBA_exp1_v1_full,file="models/pp_LBA_exp1_v1_full.RData")
plot_fit(data_emc, pp_LBA_exp1_v1_full, factors = c("S"),layout=c(2,3))
```

#5. Model check

