---
title: "model - exploratory"
author: "Raph & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

This file fits exploratory (not pre-registered) LBA models for Exp 1 in the face familiarity study.
Three models are fit: bias (A varies by response), t0 (non-decision time varies
by condition), and full (both A and t0 vary). Results are compared against the
preregistered model at the end.

```{r}
#| label: setup
#| include: false

pkgs <- c(
  "EMC2", "tidyverse", "RColorBrewer", "patchwork", "here"
  )
vapply(
  pkgs, library, logical(1), character.only = TRUE, logical.return = TRUE
  )

```

# 1. Data

```{r}
#| label: wrangle

data_emc <- read_csv(here("exp_1", "data", "data_exp_1.csv")) |>
  select(pid, cond, keypress, rt) |>
  rename(subjects = pid, S = cond, R = keypress) |>
  mutate(
    subjects = factor(subjects),
    S = factor(S, levels = c("novel", "learned")),
    R = if_else(R == "q", "learned", "novel"),
    R = factor(R, levels = c("novel", "learned"))
  ) |>
  as.data.frame()
```

# 2. Shared settings

```{r}
#| label: shared-settings

# match function — same for all models
matchfun <- function(d) d$S == d$lR

# shared drift rate and sv priors
v_mean <- c(
  "v_SNovel:lMFALSE" = 0, "v_SLearned:lMFALSE" = 0,
  "v_SNovel:lMTRUE"  = 1, "v_SLearned:lMTRUE"  = 1,
  sv_lMTRUE = log(.5)
)
v_sd <- c(
  "v_SNovel:lMFALSE" = 2, "v_SLearned:lMFALSE" = 2,
  "v_SNovel:lMTRUE"  = 2, "v_SLearned:lMTRUE"  = 2,
  sv_lMTRUE = .5
)
```

# 3. Bias model

A varies by response key (Novel/Learned), t0 fixed.

```{r}
#| label: design-bias

design_bias <- design(
  data     = data_emc,
  model    = LBA,
  matchfun = matchfun,
  formula  = list(
    v  ~ 0 + S:lM,
    sv ~ 0 + lM,
    B  ~ 0 + lR,
    A  ~ 0 + lR,
    t0 ~ 1
  ),
  constants = c(sv_lMFALSE = log(1))
)

mu_mean_bias <- c(v_mean,
  B_lRNovel = log(1), B_lRLearned = log(1),
  A_lRNovel = log(.5), A_lRLearned = log(.5),
  t0 = log(.3)
)

mu_sd_bias <- c(v_sd,
  B_lRNovel = .5, B_lRLearned = .5,
  A_lRNovel = .3, A_lRLearned = .3,
  t0 = .3
)

prior_bias <- prior(design_bias, type = "standard",
                    mu_mean = mu_mean_bias, mu_sd = mu_sd_bias)
```

```{r}
#| label: fit-bias
#| eval: false

LBA_exp1_v1_bias <- make_emc(data_emc, design_bias,
                              type = "standard", prior = prior_bias)
LBA_exp1_v1_bias <- fit(LBA_exp1_v1_bias,
  cores_per_chain = 3,
  fileName        = here("exp_1", "models", "tmp.RData"),
  iter            = 10000,
  step_size       = 500
)
save(LBA_exp1_v1_bias, file = here("exp_1", "models", "LBA_exp1_v1_bias.RData"))
```

```{r}
#| label: check-bias

load(here("exp_1", "models", "LBA_exp1_v1_bias.RData"))
check(LBA_exp1_v1_bias)
plot_pars(LBA_exp1_v1_bias, selection = "mu", layout = c(2, 5))
```

```{r}
#| label: pp-bias
#| eval: false

pp_bias <- predict(LBA_exp1_v1_bias, n_cores = 10)
save(pp_bias, file = here("exp_1", "models", "pp_LBA_exp1_v1_bias.RData"))
```

```{r}
load(here("exp_1", "models", "pp_LBA_exp1_v1_bias.RData"))
plot_fit(data_emc, pp_bias, factors = "S", layout = c(2, 3))
```

# 4. T0 model

Non-decision time varies by stimulus condition (Novel/Learned), A fixed.

```{r}
#| label: design-t0

design_t0 <- design(
  data     = data_emc,
  model    = LBA,
  matchfun = matchfun,
  formula  = list(
    v  ~ 0 + S:lM,
    sv ~ 0 + lM,
    B  ~ 0 + lR,
    A  ~ 1,
    t0 ~ 0 + S
  ),
  constants = c(sv_lMFALSE = log(1))
)

mu_mean_t0 <- c(v_mean,
  B_lRNovel = log(1), B_lRLearned = log(1),
  A = log(.5),
  t0_SNovel = log(.3), t0_SLearned = log(.3)
)

mu_sd_t0 <- c(v_sd,
  B_lRNovel = .5, B_lRLearned = .5,
  A = .3,
  t0_SNovel = .3, t0_SLearned = .3
)

prior_t0 <- prior(design_t0, type = "standard",
                  mu_mean = mu_mean_t0, mu_sd = mu_sd_t0)
```

```{r}
#| label: fit-t0
#| eval: false

LBA_exp1_v1_t0 <- make_emc(data_emc, design_t0,
                            type = "standard", prior = prior_t0)
LBA_exp1_v1_t0 <- fit(LBA_exp1_v1_t0,
  cores_per_chain  = 3,
  cores_for_chains = 2,
  fileName         = here("exp_1", "models", "tmp.RData"),
  iter             = 10000,
  step_size        = 100
)
save(LBA_exp1_v1_t0, file = here("exp_1", "models", "LBA_exp1_v1_t0.RData"))
```

```{r}
#| label: check-t0

load(here("exp_1", "models", "LBA_exp1_v1_t0.RData"))
check(LBA_exp1_v1_t0)
plot_pars(LBA_exp1_v1_t0, selection = "mu", layout = c(2, 5))
```

```{r}
#| label: pp-t0
#| eval: false

pp_t0 <- predict(LBA_exp1_v1_t0, n_cores = 10)
save(pp_t0, file = here("exp_1", "models", "pp_LBA_exp1_v1_t0.RData"))
```

```{r}
load(here("exp_1", "models", "pp_LBA_exp1_v1_t0.RData"))
plot_fit(data_emc, pp_t0, factors = "S", layout = c(2, 3))
```

# 5. Full model

Both A and t0 vary.

```{r}
#| label: design-full

design_full <- design(
  data     = data_emc,
  model    = LBA,
  matchfun = matchfun,
  formula  = list(
    v  ~ 0 + S:lM,
    sv ~ 0 + lM,
    B  ~ 0 + lR,
    A  ~ 0 + lR,
    t0 ~ 0 + S
  ),
  constants = c(sv_lMFALSE = log(1))
)

mu_mean_full <- c(v_mean,
  B_lRNovel = log(1), B_lRLearned = log(1),
  A_lRNovel = log(.5), A_lRLearned = log(.5),
  t0_SNovel = log(.3), t0_SLearned = log(.3)
)

mu_sd_full <- c(v_sd,
  B_lRNovel = .5, B_lRLearned = .5,
  A_lRNovel = .3, A_lRLearned = .3,
  t0_SNovel = .3, t0_SLearned = .3
)

prior_full <- prior(design_full, type = "standard",
                    mu_mean = mu_mean_full, mu_sd = mu_sd_full)
```

```{r}
#| label: fit-full
#| eval: false

LBA_exp1_v1_full <- make_emc(data_emc, design_full,
                              type = "standard", prior = prior_full)
LBA_exp1_v1_full <- fit(LBA_exp1_v1_full,
  cores_per_chain  = 3,
  cores_for_chains = 2,
  fileName         = here("exp_1", "models", "tmp.RData"),
  iter             = 10000,
  step_size        = 100
)
save(LBA_exp1_v1_full, file = here("exp_1", "models", "LBA_exp1_v1_full.RData"))
```

```{r}
#| label: check-full

load(here("exp_1", "models", "LBA_exp1_v1_full.RData"))
check(LBA_exp1_v1_full)
plot_pars(LBA_exp1_v1_full, selection = "mu", layout = c(2, 5))
```

```{r}
#| label: pp-full
#| eval: false

pp_full <- predict(LBA_exp1_v1_full, n_cores = 10)
save(pp_full, file = here("exp_1", "models", "pp_LBA_exp1_v1_full.RData"))
```

```{r}
load(here("exp_1", "models", "pp_LBA_exp1_v1_full.RData"))
plot_fit(data_emc, pp_full, factors = "S", layout = c(2, 3))
```

# 6. Model comparison

```{r}
#| label: model-comparison

load(here("exp_1", "models", "LBA_exp1_v1.RData"))
load(here("exp_1", "models", "LBA_exp1_v1_bias.RData"))
load(here("exp_1", "models", "LBA_exp1_v1_t0.RData"))
load(here("exp_1", "models", "LBA_exp1_v1_full.RData"))

model_list <- list(
  preregistered = LBA_exp1_v1,
  bias          = LBA_exp1_v1_bias,
  t0            = LBA_exp1_v1_t0,
  full          = LBA_exp1_v1_full
)

compare(model_list, cores_per_prop = 2)
```
