---
title: "EMC_modelling_WP1_1"
author: "Fournier Raphaël"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load the libraries that we will be using #

## load packages ##

```{r load-pkg}
pkxg <- c("EMC2", "tidyverse", "RColorBrewer", "patchwork")

lapply(pkxg, library, character.only = TRUE)
```

## plot settings ##

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face="bold"), 
          title = element_text(size = 18, face="bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 1. read in the raw data and wrangle

## read in the wrangled data ##

Load data (30 pids)

```{r}
raw <- read_csv("Exp_1/data/data.csv")
head(raw)
str(raw)
```

#Wrangle
```{r}
data_emc <- raw %>%
  select(pid, cond, keypress, rt) %>% 
  rename(subjects = pid, S = cond, R = keypress) %>% 
  mutate(subjects=factor(subjects),
         S=factor(S,
                  levels = c("Novel", "Learned")),
         R=if_else(R == "q", "Learned", "Novel"),
         R=factor(R,
                  levels = c("Novel", "Learned"))) %>% 
  as.data.frame() ## in DMC, post predict need a df and not a tibble. Same for EMC2 I think.
head(data_emc)
str(data_emc)
```


### 2. Preregistered model ###

# 2.1 build model #

## set the match factor  ##

```{r}
matchfun=function(d)d$S==d$lR
```

```{r}
design_exp1_v1 <- design(data = data_emc,model=LBA,matchfun=matchfun,
                       formula=list(v~0+S:lM,sv~0+lM,B~0+lR,A~1,t0~1),
                       constants=c(sv_lMFALSE=log(1)))
```

```{r}
p_vector <- c("v_SNovel:lMFALSE"=4,"v_SLearned:lMFALSE"=4, "v_SNovel:lMTRUE"=4, "v_SLearned:lMTRUE"=4,
              sv_lMTRUE=log(.5), 
              B_lNovel=log(2), B_lRLearned=log(2),
              A=log(.5),t0=log(.3))

mapped_pars(p_vector, x=design_exp1_v1)
```

## set priors ##

try to copy dmc priors.

I made the A and t0 sd priors smaller as they are fixed values and it seemed odd to sample a wide range when they are fixed at .5 and .3, respectively.

```{r}
mu_mean=c("v_SNovel:lMFALSE"=0,"v_SLearned:lMFALSE"=0, "v_SNovel:lMTRUE"=1, "v_SLearned:lMTRUE"=1,
          sv_lMTRUE=log(.5), 
          B_lRNovel=log(1), B_lRLearned=log(1),
          A=log(.5),t0=log(.3))

mu_sd=c("v_SNovel:lMFALSE"=2,"v_SLearned:lMFALSE"=2, "v_SNovel:lMTRUE"=2, "v_SLearned:lMTRUE"=2,
          sv_lMTRUE=.5, 
          B_lRNovel=.5, B_lRLearned=.5,
          A=.3,t0=.3)

prior_exp1_v1 <- prior(design_exp1_v1, type ='standard',mu_mean=mu_mean,mu_sd=mu_sd)

plot(x = prior_exp1_v1)
```            

## fit the model ##

Note that I changed iter and step_size to make the model fit better and sample quicker.

```{r}
LBA_exp1_v1 <- make_emc(data_emc,design_exp1_v1,type="standard",  prior=prior_exp1_v1)
LBA_exp1_v1 <- fit(LBA_exp1_v1, cores_per_chain = 3, fileName="Exp_1/models/tmp.RData",
                     iter = 10000, step_size = 500)
save(LBA_exp1_v1,file="Exp_1/models/LBA_exp1_v1.RData") 
load("Exp_1/models/LBA_exp1_v1.RData")
```

# 2.2 check the model #

convergence 
efficiency?

```{r}
check(LBA_exp1_v1)
get_pars(LBA_exp1_v1, map = TRUE)
```

plot pars

```{r}
plot_pars(LBA_exp1_v1,selection="mu",layout=c(2,5))
```

# 2.3 calculate and plot posterior predictions #

```{r}
pp_LBA_exp1_v1 <- predict(LBA_exp1_v1, n_cores = 10)
save(pp_LBA_exp1_v1,file="Exp_1/models/pp_LBA_exp1_v1.RData")
plot_fit(data_emc, pp_LBA_exp1_v1, factors = c("S"),layout=c(2,3))
```


### 3. Bias model ###

# 3.1 build model with bias #

## set the match factor  ##

```{r}
matchfun=function(d)d$S==d$lR
```

```{r}
design_exp1_v1_bias <- design(data = data_emc,model=LBA,matchfun=matchfun,
                       formula=list(v~0+S:lM,sv~0+lM,B~0+lR,A~0+lR,t0~1),
                       constants=c(sv_lMFALSE=log(1)))
```
```{r}
p_vector_bias <- c("v_SNovel:lMFALSE"=4,"v_SLearned:lMFALSE"=4, "v_SNovel:lMTRUE"=4, "v_SLearned:lMTRUE"=4,
              sv_lMTRUE=log(.5), 
              B_lRNovel=log(2), B_lRLearned=log(2),
              A_lRNovel=log(.5), A_lRLearned = log(.5),
              t0=log(.3))

mapped_pars(p_vector_bias, x=design_exp1_v1_bias)
```

## set priors ##

try to copy dmc priors.

I made the t0 and sd priors smaller as they are fixed values and it seemed odd to sample a wide range when they are fixed at .5 and .3, respectively.

```{r}
mu_mean_start=c("v_SNovel:lMFALSE"=0,"v_SLearned:lMFALSE"=0, "v_SNovel:lMTRUE"=1, "v_SLearned:lMTRUE"=1,
          sv_lMTRUE=log(.5), 
          B_lRNovel=log(1), B_lRLearned=log(1),
          A_lRNovel=log(.5),A_lRLearned=log(.5),
          t0=log(.3))

mu_sd_start=c("v_SNovel:lMFALSE"=2,"v_SLearned:lMFALSE"=2, "v_SNovel:lMTRUE"=2, "v_SLearned:lMTRUE"=2,
          sv_lMTRUE=.5, 
          B_lRNovel=.5, B_lRLearned=.5,
          A_lRNovel=.3,A_lRLearned=.3,
          t0=.3)

prior_exp1_v1_bias <- prior(design_exp1_v1_bias, type ='standard',mu_mean=mu_mean_bias,mu_sd=mu_sd_bias)

plot(x = prior_exp1_v1_bias)
```            

## fit the model ##

Note that I changed iter and step_size to make the model fit better and sample quicker.

```{r}
LBA_exp1_v1_bias <- make_emc(data_emc,design_exp1_v1_bias,type="standard",  prior=prior_exp1_v1_bias)
LBA_exp1_v1_bias <- fit(LBA_exp1_v1_bias, cores_per_chain = 3, fileName="Exp_1/models/tmp.RData",
                     iter = 10000, step_size = 500)
save(LBA_exp1_v1_bias,file="Exp_1/models/LBA_exp1_v1_bias.RData") 
load("Exp_1/models/LBA_exp1_v1_bias.RData")
```

# 3.2 check the model #

convergence 
efficiency?

```{r}
check(LBA_exp1_v1_bias)
get_pars(LBA_exp1_v1_bias, map = TRUE)
```

plot pars

```{r}
plot_pars(LBA_exp1_v1_bias,selection="mu",layout=c(2,5))
```

# 3.3 calculate and plot posterior predictions #

```{r}
pp_LBA_exp1_v1_bias <- predict(LBA_exp1_v1_bias, n_cores = 10)
save(pp_LBA_exp1_v1_bias,file="Exp_1/models/pp_LBA_exp1_v1_bias.RData")
plot_fit(data_emc, pp_LBA_exp1_v1_bias, factors = c("S"),layout=c(2,3))
```

### 4. T0 model ###

# 4.1 build model with t0 #

## set the match factor  ##

```{r}
matchfun=function(d)d$S==d$lR
```

```{r}
design_exp1_v1_t0 <- design(data = data_emc,model=LBA,matchfun=matchfun,
                       formula=list(v~0+S:lM,sv~0+lM,B~0+lR,A~1,t0~0+S),
                       constants=c(sv_lMFALSE=log(1)))
```

```{r}
p_vector_t0 <- c("v_SNovel:lMFALSE"=4,"v_SLearned:lMFALSE"=4, "v_SNovel:lMTRUE"=4, "v_SLearned:lMTRUE"=4,
              sv_lMTRUE=log(.5), 
              B_lRNovel=log(2), B_lRLearned=log(2),
              A=log(.5),
              t0_SNovel=log(.3),t0_SLearned=log(.3))

mapped_pars(p_vector_t0, x=design_exp1_v1_t0)
```

## set priors ##

try to copy dmc priors.

I made the t0 and sd priors smaller as they are fixed values and it seemed odd to sample a wide range when they are fixed at .5 and .3, respectively.

```{r}
mu_mean_t0=c("v_SNovel:lMFALSE"=0,"v_SLearned:lMFALSE"=0, "v_SNovel:lMTRUE"=1, "v_SLearned:lMTRUE"=1,
          sv_lMTRUE=log(.5), 
          B_lRNovel=log(1), B_lRLearned=log(1),
          A=log(.5),
          t0_SNovel=log(.3),t0_SLearned=log(.3))

mu_sd_t0=c("v_SNovel:lMFALSE"=2,"v_SLearned:lMFALSE"=2, "v_SNove:lMTRUE"=2, "v_SLearned:lMTRUE"=2,
          sv_lMTRUE=.5, 
          B_lRNovel=.5, B_lRLearned=.5,
          A=.3,
          t0_SNovel=log(.3),t0_SLearned=log(.3))

prior_exp1_v1_t0 <- prior(design_exp1_v1_t0, type ='standard',mu_mean=mu_mean_t0,mu_sd=mu_sd_t0)

plot(x = prior_exp1_v1_t0)
```            

## fit the model ##

Note that I changed iter and step_size to make the model fit better and sample quicker.

```{r}
LBA_exp1_v1_t0 <- make_emc(data_emc,design_exp1_v1_t0,type="standard",  prior=prior_exp1_v1_t0)
LBA_exp1_v1_t0 <- fit(LBA_exp1_v1_t0, cores_per_chain = 3, cores_for_chains = 2, fileName="Exp_1/models/tmp.RData",
                     iter = 10000, step_size = 100)
save(LBA_exp1_v1_t0,file="Exp_1/models/LBA_exp1_v1_t0.RData") 
load("Exp_1/models/LBA_exp1_v1_t0.RData")
```

# 4.2 check the model #

convergence 
efficiency?

```{r}
check(LBA_exp1_v1_t0)
get_pars(LBA_exp1_v1_t0, map = TRUE)
```

plot pars

```{r}
plot_pars(LBA_exp1_v1_t0,selection="mu",layout=c(2,5))
```

# 4.3 calculate and plot posterior predictions #

```{r}
pp_LBA_exp1_v1_t0 <- predict(LBA_exp1_v1_t0, n_cores = 10)
save(pp_LBA_exp1_v1_t0,file="Exp_1/models/pp_LBA_exp1_v1_t0.RData")
plot_fit(data_emc, pp_LBA_exp1_v1_t0, factors = c("S"),layout=c(2,3))
```

### 5. Full model ###

# 5.1 build full model #

## set the match factor  ##

```{r}
matchfun=function(d)d$S==d$lR
```

```{r}
design_exp1_v1_full <- design(data = data_emc,model=LBA,matchfun=matchfun,
                       formula=list(v~0+S:lM,sv~0+lM,B~0+lR,A~0+lR,t0~0+S),
                       constants=c(sv_lMFALSE=log(1)))
```

```{r}
p_vector_full <- c("v_SNovel:lMFALSE"=4,"v_SLearned:lMFALSE"=4, "v_SNovel:lMTRUE"=4, "v_SLearned:lMTRUE"=4,
              sv_lMTRUE=log(.5), 
              B_lRNovel=log(2), B_lRLearned=log(2),
              A_lRNovel=log(.5), A_lRLearned = log(.5),
              t0_SNovel=log(.3),t0_SLearned=log(.3))

mapped_pars(p_vector_full, x=design_exp1_v1_full)
```

## set priors ##

try to copy dmc priors.

I made the t0 and sd priors smaller as they are fixed values and it seemed odd to sample a wide range when they are fixed at .5 and .3, respectively.

```{r}
mu_mean_full=c("v_SNovel:lMFALSE"=0,"v_SLearned:lMFALSE"=0, "v_SNovel:lMTRUE"=1, "v_SLearned:lMTRUE"=1,
          sv_lMTRUE=log(.5), 
          B_lRNovel=log(1), B_lRLearned=log(1),
          A_lRNovel=log(.5), A_lRLearned = log(.5),
          t0_SNovel=log(.3),t0_SLearned=log(.3))

mu_sd_full=c("v_SNovel:lMFALSE"=2,"v_SLearned:lMFALSE"=2, "v_SNovel:lMTRUE"=2, "v_SLearned:lMTRUE"=2,
          sv_lMTRUE=.5, 
          B_lRNovel=.5, B_lRLearned=.5,
          A_lRNovel=.3, A_lRLearned = .3,
          t0_SNovel=log(.3),t0_SLearned=log(.3))

prior_exp1_v1_full <- prior(design_exp1_v1_full, type ='standard',mu_mean=mu_mean_full,mu_sd=mu_sd_full)

plot(x = prior_exp1_v1_full)
```            

## fit the model ##

Note that I changed iter and step_size to make the model fit better and sample quicker.

```{r}
LBA_exp1_v1_full <- make_emc(data_emc,design_exp1_v1_full,type="standard",  prior=prior_exp1_v1_full)
LBA_exp1_v1_full <- fit(LBA_exp1_v1_full, cores_per_chain = 3, fileName="Exp_1/models/tmp.RData",
                     iter = 10000, step_size = 100, cores_for_chains = 2)
save(LBA_exp1_v1_full,file="Exp_1/models/LBA_exp1_v1_full.RData") 
load("Exp_1/models/LBA_exp1_v1_full.RData")
```

# 5.2 check the model #

convergence 
efficiency?

```{r}
check(LBA_exp1_v1_full)
get_pars(LBA_exp1_v1_full, map = TRUE)
```

plot pars

```{r}
plot_pars(LBA_exp1_v1_full,selection="mu",layout=c(2,5))
```

# 5.3 calculate and plot posterior predictions #

```{r}
pp_LBA_exp1_v1_full <- predict(LBA_exp1_v1_full, n_cores = 10)
save(pp_LBA_exp1_v1_full,file="Exp_1/models/pp_LBA_exp1_v1_full.RData")
plot_fit(data_emc, pp_LBA_exp1_v1_full, factors = c("S"),layout=c(2,3))
```



### 6. Models comparison ###

```{r}
load("Exp_1/models/LBA_exp1_v1_full.RData")
load("Exp_1/models/LBA_exp1_v1_t0.RData")
load("Exp_1/models/LBA_exp1_v1.RData")
load("Exp_1/models/LBA_exp1_v1_bias.RData")

list <- list(LBA_exp1_v1, LBA_exp1_v1_bias, LBA_exp1_v1_t0, LBA_exp1_v1_full)
compare(list, cores_per_prop = 2)
```

