---
title: "wrangle"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file wrangles the pilot data for the familiarity face perception study.

## load the libraries that we will be using ## 

## install ##

```{r install-pkg}
# install.packages(c("tidyverse", "RColorBrewer", "patchwork"))
```

take a snapshot of loaded packages and update the lock.file using renv

```{r snapshot-renv}
# take a snapshot and update the lock.file
renv::snapshot() # this is only necessary when new packages or installed or packages are updated.
```

## load ##

```{r load-pkg}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "gtsummary", "paletteer")

lapply(pkg, library, character.only = TRUE)
```

## plot settings ##

```{r}
## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 20), 
          title = element_text(size = 22),
          legend.position = "bottom")
)
```

## section 1 - read in the raw data ##

This chunk reads in the main raw data file

```{r}
raw <- list.files(path = "/Users/rfournier/Rstudio/pilot5_dmc/data_exp_1", pattern = "^raw.*csv", full.names = TRUE,
                  recursive = TRUE) %>% # check out list.files for info on selecting a bunch of files
  set_names() %>% 
  map_dfr(read_csv, col_names = c("subj", "block", "trial", "keypress", "rt",
                                  "ori", "stim")) %>% # map makes read_csv iterative across the file names
  mutate(pid = as.numeric(str_sub(subj, 2, -1))) %>% # make a numerical pid variable
  select(pid, everything(), -subj) # reorder things
head(raw)
glimpse(raw)
summary(raw)
```

data check

```{r}
raw %>% 
   distinct(subj, pid)
```

save raw data file
```{r}
write_csv(raw,"/Users/rfournier/Rstudio/EMC_WP1_1_git/EMC_WP1_1/data/raw_data_exp_1.csv")
```

this is the stimulus coding for the familiar stimuli

```{r}
## read in the stim file and pivot longer
fstim <- list.files(path = "/Users/rfournier/Rstudio/pilot5_dmc/data_exp_1", pattern = "^S.*csv", 
                    full.names = TRUE, recursive = TRUE) %>% # list.files again, but search for particular string
  set_names() %>% 
  map_dfr(read_csv, col_names = 1:length(cols)) %>% # use map to read files
  mutate(pid = row_number()) %>% # add a pid variable per rownumber
  pivot_longer(cols = -pid,
               names_to = "ftrial",
               values_to = "fstim") %>% # make the file into long (tidy) format
  select(-ftrial)  # remove stuff we don't want
head(fstim)
str(fstim)
glimpse(fstim)
```
Save the stim file
```{r}
write_csv(fstim,"/Users/rfournier/Rstudio/EMC_WP1_1_git/EMC_WP1_1/data/fam_stim_exp_1.csv")
```


## section 2 - do some more wrangling ##

This section gets the data in a format ready for plotting

make a long version of fstim and a trial counter. The reason for doing so is so
that we have a variable that lists the familiar stimuli per pid that is the same 
length as the rest of the data. This is important and makes life easier when we can
join dataframes of a similar lenghth. Then we can just look through the variable for
familiar stim and see if it matches the stim in that trial to code whether or
not it is familiar. 

This is hacky and I'm sure it can be done more efficiently with a join, but it is
a pain when there is no clear corresponding key like trial number (e.g., there is
a trial number but not in the familiar stimuli dataframe that is recorded).

Here we just use bind_rows() to add fstim to itself and therefore make it double
the length. Then we create a trial count so that it can link with the main dataset
in a subsequent join.

```{r}
## make a long version with twice the number of observations - this is hacky and 
## simply binds them together and re-arranges
long_fstim <- fstim %>% 
  bind_rows(fstim) %>% 
  arrange(pid) %>% 
  group_by(pid) %>% 
  mutate(trial = 1:60) %>% 
  select(pid, trial, fstim)
head(long_fstim)
```

data check

```{r}
long_fstim %>% 
  distinct(pid, fstim)
```

join with the main data

```{r}
data <- raw %>%
  left_join(long_fstim, join_by(pid, trial))
data
```

mutate and create factors

```{r}
data <- data %>%
  group_by(pid) %>% 
  mutate(fam = if_else(stim %in% fstim, 1, 0),
         cond = if_else(fam == 1, "Learned", "Novel"),
         cond = factor(cond, 
                       levels = c("Novel", "Learned")),
         block = factor(block))
data
```

data check

```{r}
data %>%
  group_by(pid, block, fam, cond) %>% 
  tally()
```

calculate accuracy

```{r}
data <- data %>% 
  mutate(acc = case_when(
         cond == "Learned" & keypress == "q" ~ 1,
         cond == "Novel" & keypress == "p" ~ 1,
         TRUE ~ 0)) %>%
  mutate(cond = fct_relevel(cond,"Novel", "Learned")) %>%
  
head(data)
```

data check

```{r}
data %>% 
  distinct(pid, block, cond, acc)

data %>%
  group_by(pid, block, cond) %>% 
  tally(acc)

```

RT < 2.5 by OSF registration
```{r}
data <- data %>% 
  mutate(rt_OSF = if_else(
         rt < 2.5, "yes", "no"))
head(data)
```



## section 3 - create summary data ##

first, create summary data for rt and accuracy at the pid level and at the 
group level

### rt ###

checking for each participant the percentage or RT < 2.5
```{r}
data %>%
  select(pid,rt_OSF) %>%
  tbl_summary(
    by = pid) %>%
  bold_labels()
```


removing 1st participant
```{r}
data <- data %>%
  filter(!pid == "1") %>%
  filter(!rt > 2.5)
```



just a few quick and dirty plots for now
load data
```{r}
write_csv(data, "Exp_1/data/data.csv")
data<-read_csv("Exp_1/data/data.csv") %>%
  mutate(cond = fct_relevel(cond,"Novel", "Learned"))

```



at the pid level

```{r}
rt_pid <- data %>% 
  group_by(pid, block, cond) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_pid
```

at the group level

```{r}
rt_group <- data %>% 
  group_by(block, cond) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_group
```

### acc ###

at the pid level

```{r}
acc_pid <- data %>% 
  group_by(pid, block, cond) %>% 
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid
```

at the group level

```{r}
acc_group <- acc_pid %>% 
  group_by(block, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group
```

### without block###
## rt ##
```{r}
rt_group_wblock <- data %>% 
  group_by(cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)

rt_group_wblock
```

## acc ##
```{r}
acc_group_wblock <- acc_pid %>% 
  group_by(cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_wblock
```


## section 4 - plot ##


density

rt

```{r}
p4.1 <- ggplot(data, aes(x=rt, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Response time by block and condition") +
   facet_wrap(~block) +
   xlab("Response time [s]") +
   ylab("Density")
p4.1

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/rt_density_pid.jpeg",
       #width = 8, height = 6)
```

rt when acc = 0
```{r}
data_fam <- data %>%
  filter(cond=="fam")
p4.1.1 <- ggplot(data_fam, aes(x=rt, fill=acc, colour=acc)) +
   geom_density(alpha=0.5) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Learned faces: Response time by block and accuracy") +
   facet_wrap(~block) +
   xlab("Response time [s]") +
   ylab("Density")
p4.1.1
```

rt when acc = 1
```{r}
data_unf <- data %>%
  filter(cond=="unf")
p4.1.2 <- ggplot(data_unf, aes(x=rt, fill=acc, colour=acc)) +
   geom_density(alpha=0.5) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("New faces: Response time by block and accuracy") +
   facet_wrap(~block) +
   xlab("Response time [s]") +
   ylab("Density")
p4.1.2
```




acc

```{r}
p4.2 <- ggplot(data, aes(x=acc, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Accuracy by block and condition") +
   facet_wrap(~block) +
   xlab("Accuracy") +
   ylab("Density")  
p4.2 

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_density_pid.jpeg",
       #width = 8, height = 6)
```

summary plots

rt

```{r}
p4.3 <- ggplot(rt_pid, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond)) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Mean response time by block and condition") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
  ylim(0,3)
p4.3

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/rt_line_pid.jpeg",
      # width = 8, height = 6)
```

acc

```{r}
p4.4 <- ggplot(acc_pid, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond)) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Accuracy by block and condition") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Accuracy [%]")
p4.4

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_line_pid.jpeg",
      # width = 8, height = 6)
```

group level summary data

rt

```{r}
p4.5 <- ggplot(rt_group, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Response time by block and condition") +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
   ylim(0,2)
p4.5

ggsave("Exp_1/figures/rt_line_group.jpeg",
        width = 8, height = 6)
```

acc

```{r}
p4.6 <- ggplot(acc_group, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
  scale_fill_paletteer_d("rcartocolor::Safe") +
  scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Accuracy by block and condition") +
   xlab("Blocks") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6

 ggsave("Exp_1/figures/acc_line_group.jpeg",
        width = 8, height = 6)
```

plot group data together

```{r}
p4.7 <- p4.5 | p4.6
p4.7

ggsave("Exp_1/figures/rt_acc_line.jpeg",
        width = 15, height = 6)
```

add pid dots to the group data

rt

```{r}
p4.8 <- ggplot(rt_group, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_jitter(data = rt_pid,
               position=position_jitterdodge(dodge.width =1), 
               alpha = 1, colour = "darkgrey") +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
   scale_fill_brewer(palette = "Paired") +
   scale_colour_brewer(palette = "Paired") +
   ggtitle("rt by block and condition") +
   ylim(0,2.5)
p4.8
```

acc

```{r}
p4.9 <- ggplot(acc_group, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_jitter(data = acc_pid,
               position=position_jitterdodge(dodge.width =1), 
               alpha = 1, colour = "darkgrey") +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
   scale_fill_brewer(palette = "Paired") +
   scale_colour_brewer(palette = "Paired") +
   ggtitle("acc by block and condition") +
   ylim(0,100)
p4.9
```

plot group data together

```{r}
p4.10 <- p4.8 | p4.9
p4.10

ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/rt_acc_line_dots.jpeg",
       width = 10, height = 6)
```

## section 5 - save out some files ##

This is useful for future modelling and/or plotting without re-doing the wrangle
file.

barplot

Accuracy
```{r}
p.4.11 <- ggplot(acc_group_wblock, aes(x = cond,y=perc, 
                           fill=cond, colour=cond)) +
   geom_col() +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem), col = "black",
                width=.2, position=pd2) +
   scale_fill_paletteer_d("rcartocolor::Safe") +
   scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Accuracy by familiarity condition") +
   xlab("Familiarity") +
   ylab("Accuracy [%]") +
   ylim(0,100) +
   theme(legend.position = "none")

p.4.11

ggsave("Exp_1/figures/acc_barplot_group.jpeg",
        width = 8, height = 8)
```

Reaction times
```{r}
p.4.12 <- ggplot(rt_group_wblock, aes(x = cond,y=mean, 
                           fill=cond, colour=cond)) +
   geom_col() +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem), col = "black",
                width=.2, position=pd2) +
   scale_fill_paletteer_d("rcartocolor::Safe") +
   scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Response time by familiarity condition") +
   xlab("Familiarity") +
   ylab("Response time [s]") +
   ylim(0,1.5)+
   theme(legend.position = "none")

p.4.12

ggsave("Exp_1/figures/rt_barplot_group.jpeg",
        width = 8, height = 8)
```


##section 6 - exploratory analysis ##

Here I just want to have a look at the reaction times and accuracy for the different head orientations

#RT At pid level
1st orientation
```{r}
rt_ori_1 <- data %>%
  group_by(pid, block, cond, ori) %>% 
  filter(ori == 1) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_ori_1
```
Plot
```{r}

p5.1 <- ggplot(rt_ori_1, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond))+
   ggtitle("Orientation 1") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]")
p5.1
```

2nd orientation
```{r}
rt_ori_2 <- data %>%
  group_by(pid, block, cond, ori) %>% 
  filter(ori == 2) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_ori_2
```
Plot
```{r}

p5.2 <- ggplot(rt_ori_2, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond))+
   ggtitle("Orientation 2") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]")
p5.2
```

3rd orientation
```{r}
rt_ori_3 <- data %>%
  group_by(pid, block, cond, ori) %>% 
  filter(ori == 3) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_ori_3
```
Plot
```{r}

p5.3 <- ggplot(rt_ori_3, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond))+
   ggtitle("Orientation 3") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]")
p5.3
```

```{r}
p5.4 <-p5.1 | p5.2 | p5.3
p5.4
```

#At group level

RT
```{r}
rt_group_ori <- data %>% 
  group_by(block, ori) %>% 
  mutate(ori = as.factor(ori))%>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_group_ori
```
Plot
```{r}
p5.5 <- ggplot(rt_group_ori, aes(x=block, y=mean, 
                           fill=ori, colour=ori)) +
   geom_bar(alpha = 3, position = pd2, stat = "identity") +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
   ggtitle("Response time by block and orientation of picture") +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
   ylim(0,3)
p5.5
ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/rt_bar_ori_blocks.jpeg",
       width = 10, height = 6)
```


Acc / block

```{r}
acc_pid_ori<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori
```

```{r}
acc_group_ori <- acc_pid_ori %>% 
  group_by(block, ori) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori

```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori, aes(x=block, y=perc, 
                           fill=ori, colour=ori)) +
   geom_bar(aes(group = ori), position = pd2, stat = "identity") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
  
   ggtitle("Accuracy by block and condition") +
   xlab("Blocks") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6
ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_bar_ori_blocks.jpeg",
       width = 10, height = 6)
```

Acc / block / familiarity level
#Block 1
```{r}
acc_pid_ori_block_1<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  filter(block == "1")%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori
```

```{r}
acc_group_ori_block_1 <- acc_pid_ori_block_1 %>% 
  group_by(block, ori, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori_block_1
```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori_block_1, aes(x= ori, y=perc, colour=cond)) +
   geom_bar(aes(group = cond), position = position_dodge(1), stat = "identity", fill = "white") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem, col = cond),
                width=.2, position=position_dodge(1)) +
   ggtitle("Block 1: Accuracy by picture orientation and condition") +
   xlab("Picture orientation") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6

ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_bar_ori_block_1.jpeg",
       width = 10, height = 6)
```

#Block 2
```{r}
acc_pid_ori_block_2<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  filter(block == "2")%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori_block_2
```

```{r}
acc_group_ori_block_2 <- acc_pid_ori_block_2 %>% 
  group_by(block, ori, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori_block_2
```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori_block_2, aes(x= ori, y=perc, colour=cond)) +
   geom_bar(aes(group = cond), position = position_dodge(1), stat = "identity", fill = "white") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem, col = cond),
                width=.2, position=position_dodge(1)) +
   ggtitle("Block 2: Accuracy by picture orientation and condition") +
   xlab("Picture orientation") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6

ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_bar_ori_block_2.jpeg",
       width = 10, height = 6)
```

#Block 3
```{r}
acc_pid_ori_block_3<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  filter(block == "3")%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori_block_3
```

```{r}
acc_group_ori_block_3 <- acc_pid_ori_block_3 %>% 
  group_by(block, ori, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori_block_3
```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori_block_3, aes(x= ori, y=perc, colour=cond)) +
   geom_bar(aes(group = cond), position = position_dodge(1), stat = "identity", fill = "white") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem, col = cond),
                width=.2, position=position_dodge(1)) +
   ggtitle("Block 3: Accuracy by picture orientation and condition") +
   xlab("Picture orientation") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6

ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_bar_ori_block_3.jpeg",
       width = 10, height = 6)
```

### Hit rate and false alarm rate analysis ###


#Calculating hit rate "fam"
```{r}
data_fam_HR <- data %>%
  select(pid,block,trial,keypress,rt,fam,cond) %>%
  filter(cond == "fam") %>%
  mutate(hit = case_when(
         cond == "fam" & keypress == "q" ~ 1,
         cond == "fam" & keypress == "p" ~ 0,
         TRUE ~ 0))
```

at the pid level

```{r}
hit_pid_fam <- data_fam_HR %>% 
  group_by(pid, block,cond) %>% 
  summarise(sum = sum(hit),
            n = n(), # n here is the total trials per grouping
            HR = sum/n) #hit rate = nbr of hit/(nbr of hit + nbr of miss)
```

at the group level

```{r}
hit_group_fam <- hit_pid_fam %>% 
  group_by(block, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_HR= mean(HR),
            sd=sd(HR),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum)
hit_group_fam
```


#Calculating false alarm for "fam" response

```{r}
data_fam_FA <- data %>%
  select(pid,block,trial,keypress,rt,fam,cond) %>%
  filter(cond == "unf") %>%
  mutate(false = case_when(
         cond == "unf" & keypress == "q" ~ 1,
         cond == "unf" & keypress == "p" ~ 0,
         TRUE ~ 0))
```

at the pid level

```{r}
false_pid_fam <- data_fam_FA %>% 
  group_by(pid, block, cond) %>%
  summarise(sum = sum(false),
            n = n(),
            FA = sum/n)
```

at the group level

```{r}
false_group_fam <- false_pid_fam%>% 
  group_by(block,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_FA = mean(FA),
            sd=sd(FA),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum)
false_group_fam
```

#Calculating D'
```{r}
data_d_pid_fam <- hit_pid_fam %>%
  left_join(false_pid_fam, join_by(pid, block))

data_d_pid_fam <- data_d_pid_fam %>%
  select(pid, block, HR, FA) %>%
  mutate(
    zscoreHR = (HR - 0.671585)/0.1648843,
    zscoreFA = (FA - 0.1664701)/0.1385968,
    d_prime = zscoreHR - zscoreFA)
```

## New faces

#Calculating hit rate "unf"
```{r}
data_unf_HR <- data %>%
  select(pid,block,trial,keypress,rt,fam,cond) %>%
  filter(cond == "unf") %>%
  mutate(hit = case_when(
         cond == "unf" & keypress == "p" ~ 1,
         cond == "unf" & keypress == "q" ~ 0,
         TRUE ~ 0))
```

at the pid level

```{r}
hit_pid_unf <- data_unf_HR %>% 
  group_by(pid, block,cond) %>% 
  summarise(sum = sum(hit),
            n = n(), # n here is the total trials per grouping
            HR = sum/n) #hit rate = nbr of hit/(nbr of hit + nbr of miss)
```

at the group level

```{r}
hit_group_unf <- hit_pid_unf %>% 
  group_by(block, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_HR= mean(HR),
            sd=sd(HR),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum)
hit_group_unf
```


#Calculating false alarm for "fam" response

```{r}
data_unf_FA <- data %>%
  select(pid,block,trial,keypress,rt,fam,cond) %>%
  filter(cond == "fam") %>%
  mutate(false = case_when(
         cond == "fam" & keypress == "p" ~ 1,
         cond == "fam" & keypress == "q" ~ 0,
         TRUE ~ 0))
```

at the pid level

```{r}
false_pid_unf <- data_unf_FA %>% 
  group_by(pid, block, cond) %>%
  summarise(sum = sum(false),
            n = n(),
            FA = sum/n)
```

at the group level

```{r}
false_group_unf <- false_pid_unf %>% 
  group_by(block,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_FA = mean(FA),
            sd=sd(FA),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum)
false_group_unf
```

#Calculating D'
```{r}
data_d_pid_unf <- hit_pid_unf %>%
  left_join(false_pid_unf, join_by(pid, block))

data_d_pid_unf <- data_d_pid_unf %>%
  select(pid, block, HR, FA)%>%
  mutate(
    zscoreHR = (HR - 0.671585)/0.1648843,
    zscoreFA = (FA - 0.1664701)/0.1385968,
    d_prime = zscoreHR - zscoreFA)
```

### Bayesian estimation approahc to multilevel modelling (McElreatch,2020) ###
Import brms
```{r}
library("brms")
```

```{r}

```





