---
title: "exploratory analysis"
author: "Fournier Raphaël"
date: "`r Sys.Date()`"
output: html_document
---


## load packages ##
```{r load-pkg}
pkxg <- c("EMC2", "tidyverse", "RColorBrewer", "patchwork", "tidybayes", "DataExplorer","ggpubr", "paletteer")

lapply(pkxg, library, character.only = TRUE)
```


## plot settings ##
#Colors
```{r}
myColors <- c("Novel" = paletteer_d("rcartocolor::Safe",4)[1],"Famous" =  paletteer_d("rcartocolor::Safe",4)[3])
```


theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face="bold"), 
          title = element_text(size = 18, face="bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```


#Load models
```{r}
#Preregistered model
load("Exp_3/models/LBA_exp3_t0.RData")
```

#Quick plots
```{r}
#Preregistered model, map = FALSE
plot_pars(LBA_exp2_v1,selection="mu",layout=c(2,5),map = FALSE)
posterior_summary(LBA_exp2_v1,selection="alpha",probs = c(0.025, 0.5, 0.975),map = FALSE)#for each participant
posterior_summary(LBA_exp2_v1,selection="mu",probs = c(0.025, 0.5, 0.975),map = FALSE)#at group level


#Preregistered model, map = TRUE
plot_pars(LBA_exp2_v1,selection="mu",layout=c(2,5),map = TRUE)
posterior_summary(LBA_exp2_v1,selection="alpha",probs = c(0.025, 0.5, 0.975),map = TRUE)#for each participant
posterior_summary(LBA_exp2_v1,selection="mu",probs = c(0.025, 0.5, 0.975),map = TRUE)#at group level
```

#Parameters per subjects
```{r}
#Preregistered model
param_1_pid_t0 = EMC2::parameters(LBA_exp3_t0,selection="alpha",N = NULL)
#Remember:number of iters = 10000 / number of chains = 3 -> 10'000 x 30(subjects) x 3(number of chains) = 900'000 obs for each parameter
```


### T0 model

# section 2 #


##Wrangle
Pid level
```{r}
split_tibble <- function(tibble, col = 'col') tibble %>% split(., .[, col])
array_theta_1_t0 <- split_tibble(param_1_pid_t0, "subjects")
array_theta_1_t0 <-do.call(rbind, array_theta_1_t0)
array_theta_1_pid_t0 <- array_theta_1_t0 %>%
  pivot_longer(cols = c("v_SNovel:lMTRUE", "v_SNovel:lMFALSE", "v_SFamous:lMFALSE", "v_SFamous:lMTRUE", "sv_lMTRUE", "B_lRNovel", "B_lRFamous", "A", "t0_SFamous", "t0_SNovel"), names_to = "param", values_to = "value")%>%
  add_column(datapoint = rep(1:15000,each=10,times=30))%>% #here 30'000 = number of chains (3) x number of iteration (10'000)
  rename(pid=subjects)
```

Average across participants
```{r}
theta_group_1_t0 <- array_theta_1_pid_t0 %>%
  group_by(datapoint,param) %>% 
  summarise(value = mean(value, na.rm = T)) %>% 
  ungroup() %>% 
  add_column(pid = "average") %>% ## add a column which makes clear it is the avg. not needed but useful for plotting later
  relocate(pid, .before = everything())
head(theta_group_1_t0)
glimpse(theta_group_1_t0)
```

## calculate quantiles ##

calculate quantiles per parameter at the group level

```{r}
library(tidybayes)
theta_group_1_q_t0 <- theta_group_1_t0 %>%
  group_by(param) %>% 
  median_qi(value)
theta_group_1_q_t0
```

and do the same per pid

```{r}
theta_pid_1_q_t0 <- array_theta_1_pid_t0 %>%
  group_by(pid, param) %>% 
  median_qi(value)
theta_pid_1_q_t0
```

## some quick and dirty plots with all of the parameters ##

plot the distribution per parameter using a tidybayes halfeye plot

```{r}
p2.1 <- ggplot(theta_group_1_t0, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9) +
  labs(x = "parameter estimate", y = "") 
p2.1

ggsave("Exp_3/figures/all_params_1_t0.jpeg",
       width = 8, height = 6)
```

plot avg and individual pid parameters

```{r}
p2.2 <- ggplot(theta_group_1_t0, aes(x = value, y = fct_rev(param))) +  
  stat_halfeye(alpha = 0.9, position = position_nudge(y=-0.5)) +
  geom_pointinterval(data = theta_pid_1_q_t0, aes(xmin=.lower, xmax=.upper, 
                                           colour = pid, fill = pid),
                     position = position_dodge(width = 0.7)) +
  labs(x = "parameter estimate", y = "") +
  facet_wrap(~param, scales = "free_y") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
p2.2

ggsave("Exp_3/figures/all_params_pid_1_t0.jpeg",
       width = 8, height = 6)
```

# section 3 #

## plot thresholds separately ##

first, wrangle to make a separate dfs

thresholds df per pid

```{r}
thresh_pid_1_t0 <- array_theta_1_pid_t0 %>% 
  filter(str_detect(param, "B_")) %>% 
  mutate(response = if_else(str_detect(param, "lRFamous"), "Famous", "Novel"),
         response = factor(response,
                            levels = c("Novel", "Famous")))
head(thresh_pid_1_t0)
str(thresh_pid_1_t0)
summary(thresh_pid_1_t0)
## data check
thresh_pid_1_t0 %>% 
  distinct(param, response)
```

thresholds at the group level

```{r}
thresh_group_1_t0 <- theta_group_1_t0 %>% 
  filter(str_detect(param, "B_")) %>% 
  mutate(response = if_else(str_detect(param, "lRFamous"), "Famous", "Novel"),
         response = factor(response,
                            levels = c("Novel", "Famous")))

head(thresh_group_1_t0)
str(thresh_group_1_t0)
summary(thresh_group_1_t0)
```


at the group level

```{r}
p3.1 <- ggplot(thresh_group_1_t0, aes(x = exp(value), y = fct_rev(response))) +
  stat_halfeye(alpha = 0.7, aes(fill = response)) +
  scale_fill_manual(values = myColors) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(y="Response", x="Threshold", title=bquote("Group level: 
Threshold by response")) +
   theme(legend.position = "none")
  
p3.1

## save a figure
 ggsave("Exp_3/figures/thresh_t0.jpeg",width = 10, height = 6)
```

## caluclate a threshold response key difference ##

per pid

```{r}
thresh_diff_pid_1_t0 <- thresh_pid_1_t0 %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Famous - Novel)
head(thresh_diff_pid_1_t0)
```

at the group level

```{r}
thresh_diff_1_t0 <- thresh_group_1_t0 %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Famous - Novel)
head(thresh_diff_1_t0)
```

## quantiles on the difference score ##

per pid

```{r}
thresh_diff_pid_1_q_t0 <- thresh_diff_pid_1_t0 %>%
  group_by(pid) %>% 
  median_qi(diff)
thresh_diff_pid_1_q_t0
```

at the group level

```{r}
thresh_diff_1_q_t0 <- thresh_diff_1_t0 %>%
  group_by(pid) %>%
  median_qi(diff)
thresh_diff_1_q_t0
```

## plot the threshold difference score ##

plot the average difference

```{r}
p3.2 <- ggplot(thresh_diff_1_t0, aes(x = exp(diff), y = "")) +  
  stat_halfeye(alpha = 0.9, fill="firebrick") +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level: 
Threshold (Famous > Novel)", 
       x = "Threshold", y="") 
p3.2
```

plot individual pids

```{r}
thresh_diff_pid_1_t0$pid = with(thresh_diff_pid_1_t0, reorder(pid, diff, mean))
p3.3 <- ggplot(thresh_diff_pid_1_t0, aes(x = exp(diff), y = pid,
                                    fill=pid)) +  
  stat_halfeye(alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Participant level: Threshold (Famous > Novel)", 
       x = "Threshold", y="participant") 
p3.3
```

plot the average difference and individual pids

```{r}
p3.4 <- ggplot(thresh_diff_1_t0, aes(x = diff, y= reorder(pid, diff, mean))) +  
  stat_halfeye(data = thresh_diff_pid_1_t0,
               alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Individual and average
threshold differences", 
       x = "Threshold", y="participant ID") +
  stat_halfeye(alpha = 0.9, fill="firebrick",
               position = position_nudge(y=0)) 
p3.4
```

## plot together ##

```{r}
p3.5 <- p3.1 / p3.2 | p3.3 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.5

# save a figure
 ggsave("Exp_3/figures/thresh_1_t0.jpeg",
        width = 21, height = 10)
```

and now combine avg and pid difference plots

```{r}
p3.6 <- p3.1 | p3.2 +
  labs(caption = "80% and 95% credible intervals shown in black")
p3.6

# save a figure
ggsave("Exp_3/figures/thresh_2_t0.jpeg",
       width = 15, height = 10)
```

```{r}
p3.6 <- p3.1 | p3.4 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.6

# save a figure
ggsave("Exp_3/figures/thresh_3_t0.jpeg",
       width = 21, height = 10)
```


the exact layout, labels of factors and arrangement may need polishing and re-arranging.

But for now, the data seem to be what we want.

# section 4 #

## plot drift rate separately ##

## wrangle ##

create a drift-rate df

```{r}
drift_rate_pid_1_t0 <- array_theta_1_pid_t0 %>% 
  filter(str_detect(param, "v_S")) %>% 
  mutate(condition = if_else(str_detect(param, "Novel"), "Novel", "Famous"),
         accuracy = if_else(str_detect(param, "TRUE"), "True", "False"),
         condition = factor(condition,
                            levels = c("Novel", "Famous")),
         accuracy = factor(accuracy,
                            levels = c("False", "True")))
head(drift_rate_pid_1_t0)
str(drift_rate_pid_1_t0)
summary(drift_rate_pid_1_t0)

## data check
drift_rate_pid_1_t0 %>% 
  distinct(param, condition, accuracy)
```


drift rate at the group level

```{r}
drift_rate_group_1_t0 <- theta_group_1_t0 %>% 
  filter(str_detect(param, "v_S")) %>% 
  mutate(condition = if_else(str_detect(param, "Novel"), "Novel", "Famous"),
         accuracy = if_else(str_detect(param, "TRUE"), "True", "False"),
         condition = factor(condition,
                            levels = c("Novel", "Famous")),
         accuracy = factor(accuracy,
                            levels = c("False", "True")))
head(drift_rate_group_1_t0)
str(drift_rate_group_1_t0)
summary(drift_rate_group_1_t0)
```

## plot ##

#Create a custom manual colour scale: drift_rate group

```{r}
library(RColorBrewer)
myColors_drift <- RColorBrewer::brewer.pal(12, "Dark2")[4:5]
names(myColors_drift) <- levels(drift_rate_group_1_t0$accuracy)
colScale_drift <- scale_fill_manual(name = "Accuracy", values = myColors_drift)
```

the average

```{r}
p4.1 <- ggplot(drift_rate_group_1_t0, aes(x = value, y = fct_rev(condition), 
                               fill = accuracy)) +
  stat_halfeye(alpha = 0.7) +
  colScale_drift +
  labs(title = "Group level: True and False 
drift rate by familiarity condition", y="Familiarity", x="Drift rate") 
p4.1

ggsave("Exp_3/figures/drift_rate_1_t0.jpeg",
        width = 10, height = 6)
```

and now facet by pid

```{r}
p4.2 <- ggplot(drift_rate_pid_1_t0, aes(x = value, y = fct_rev(condition), 
                               fill = accuracy)) +
  stat_halfeye(alpha = 0.7) +
  colScale_drift +
  labs(title = "Participant level: Drift-rate by condition",
       y="condition", x="Drift rate") +
  facet_wrap(~pid)
p4.2
```

take a look together

```{r}
p4.1 / p4.2
ggsave("Exp_3/figures/drift_rate_true_false_1_t0.jpeg", 
       width = 16, height = 13)
```

## caluclate drift rate differences between conditions and accuracy ##

per pid

```{r}
## just true > false differences (accuracy)
drift_acc_diff_pid_1_t0 <- drift_rate_pid_1_t0 %>%
  pivot_wider(id_cols = -param,
               names_from = accuracy,
               values_from = value) %>%
  mutate(diff = True - False)
drift_acc_diff_pid_1_t0

## fam > unfam differences
drift_acc_cond_diff_pid_1_t0 <- drift_acc_diff_pid_1_t0 %>%
  pivot_wider(id_cols = -c("True", "False"), 
              names_from = condition,
              values_from = diff) %>%
  mutate(diff = Famous - Novel)
drift_acc_cond_diff_pid_1_t0
```

at the group level

```{r}
## just true > false differences (accuracy)
drift_acc_diff_1_t0 <- drift_rate_group_1_t0 %>%
  pivot_wider(id_cols = -param,
               names_from = accuracy,
               values_from = value) %>%
  mutate(diff = True - False)
drift_acc_diff_1_t0

## unf > fam differences
drift_acc_cond_diff_1_t0 <- drift_acc_diff_1_t0 %>%
  pivot_wider(id_cols = -c("True", "False"), 
              names_from = condition,
              values_from = diff) %>%
  mutate(diff = Famous - Novel)
drift_acc_cond_diff_1_t0
```

## plot the differences ##

differences between true and false, separately for unf and fam

at the group average level


plot

```{r}
p4.3 <- ggplot(drift_acc_diff_1_t0, aes(x = diff, y = fct_rev(condition))) +
  stat_halfeye(aes(fill = condition, alpha = 0.7)) +
  scale_fill_manual(values = myColors) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level: Drift rate (True > false)
by familiarity condition",
       x="Drift rate", y="Familiarity") +
  xlim(-1,4) +
   theme(legend.position = "none")
  
p4.3
```

quantiles

```{r}
drift_acc_diff_1_q_t0 <- drift_acc_diff_1_t0 %>%
  group_by(condition) %>% 
  median_qi(diff)
drift_acc_diff_1_q_t0
```

difference between unf (true and false) > fam (true > false)

plot

```{r}
p4.4 <- ggplot(drift_acc_cond_diff_1_t0, aes(x = diff, y = "")) +
  stat_halfeye(fill = "firebrick", alpha = 0.9) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level: Drift rate (Famous > Novel)",
       x="Drift rate", y="") +
  xlim(-1,3)
p4.4
```

quantiles

```{r}
drift_acc_cond_diff_1_q_t0 <- drift_acc_cond_diff_1_t0 %>%
  median_qi(diff)
drift_acc_cond_diff_1_q_t0
```

## plot together ##

```{r}
p4.5 <- p4.3 | p4.4 +
  labs(caption = "80% and 95% credible intervals shown in black")
p4.5

# save a figure
ggsave("Exp_3/figures/drift_rat_mini_1_t0.jpeg",
       width = 15, height = 10)
```

## plot the average difference and pid differences ##

```{r}
drift_acc_cond_diff_pid_1_t0$pid = with(drift_acc_cond_diff_pid_1_t0, reorder(pid, diff, mean))
p4.6 <- ggplot(drift_acc_cond_diff_1_t0, aes(x = diff, y=pid)) +  
  stat_halfeye(alpha = 0.9, fill="firebrick") +
  stat_halfeye(data = drift_acc_cond_diff_pid_1_t0,
               alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Individual and average 
drift rate differences", 
       x = "Drift rate", y="participant ID") 
p4.6
```

## combine drift rate plots ##

```{r}
p4.7 <- p4.3 / p4.4 | p4.6 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p4.7 

# save a figure
ggsave("Exp_3/figures/drift_rate_pid_1_t0.jpeg",
       width = 15, height = 10)
```


## compare threshold and drift rate ##

```{r}
p3.4 | p4.6
```


## Plotting T0

t0 df per pid

```{r}
t0_pid_1_t0 <- array_theta_1_pid_t0 %>% 
  filter(str_detect(param, "t0_")) %>% 
  mutate(response = if_else(str_detect(param, "SFamous"), "Famous", "Novel"),
         response = factor(response,
                            levels = c("Novel", "Famous")), 
         value = exp(value))
head(t0_pid_1_t0)
str(t0_pid_1_t0)
summary(t0_pid_1_t0)

## data check
t0_pid_1_t0 %>% 
  distinct(param, response)
```

t0 at the group level

```{r}
t0_group_1_t0 <- theta_group_1_t0 %>% 
  filter(str_detect(param, "t0_")) %>% 
  mutate(response = if_else(str_detect(param, "SFamous"), "Famous", "Novel"),
         response = factor(response,
                            levels = c("Novel", "Famous")), 
         value = exp(value))

head(t0_group_1_t0)
str(t0_group_1_t0)
summary(t0_group_1_t0)
```


at the group level

```{r}
p3.1 <- ggplot(t0_group_1_t0, aes(x = value, y = fct_rev(response))) +
  stat_halfeye(alpha = 0.7, aes(fill = response)) +
  scale_fill_manual(values = myColors) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(y="Stimulus", x="Non-decision time", title=bquote("Group level: 
Non-decision time by condition")) +
   theme(legend.position = "none")
  
p3.1

## save a figure
 ggsave("Exp_3/figures/t0_t0.jpeg",width = 10, height = 6)
```

## caluclate a threshold response key difference ##

per pid

```{r}
t0_diff_pid_1_t0 <- t0_pid_1_t0 %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Famous - Novel)
head(t0_diff_pid_1_t0)
```

at the group level

```{r}
t0_diff_1_t0 <- t0_group_1_t0 %>%
  pivot_wider(id_cols = -param,
              names_from = "response",
              values_from = "value") %>% 
  mutate(diff = Famous - Novel)
head(t0_diff_1_t0)
```

## quantiles on the difference score ##

per pid

```{r}
t0_diff_pid_1_q_t0 <- t0_diff_pid_1_t0 %>%
  group_by(pid) %>% 
  median_qi(diff)
t0_diff_pid_1_q_t0
```

at the group level

```{r}
t0_diff_1_q_t0 <- t0_diff_1_t0 %>%
  group_by(pid) %>%
  median_qi(diff)
t0_diff_1_q_t0
```

## plot the threshold difference score ##

plot the average difference

```{r}
p3.2 <- ggplot(t0_diff_1_t0, aes(x = diff, y = "")) +  
  stat_halfeye(alpha = 0.9, fill="firebrick") +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Group level: 
Non-decision time (Famous > Novel)", 
       x = "Non-decision time", y="") 
p3.2
```

plot individual pids

```{r}
t0_diff_pid_1_t0$pid = with(t0_diff_pid_1_t0, reorder(pid, diff, mean))
p3.3 <- ggplot(t0_diff_pid_1_t0, aes(x = diff, y = pid,
                                    fill=pid)) +  
  stat_halfeye(alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Participant level: Non-decision time (Famous > Novel)", 
       x = "Non-decision time", y="participant") 
p3.3
```

plot the average difference and individual pids

```{r}
p3.4 <- ggplot(t0_diff_1_t0, aes(x = diff, y= reorder(pid, diff, mean))) +  
  stat_halfeye(data = t0_diff_pid_1_t0,
               alpha = 0.7) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  labs(title = "Individual and average
non-decision time differences", 
       x = "Non-decision time", y="participant ID") +
  stat_halfeye(alpha = 0.9, fill="firebrick",
               position = position_nudge(y=0)) 
p3.4
```

## plot together ##

```{r}
p3.5 <- p3.1 / p3.2 | p3.3 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.5

# save a figure
 ggsave("Exp_3/figures/t0_1_t0.jpeg",
        width = 21, height = 10)
```

and now combine avg and pid difference plots

```{r}
p3.6 <- p3.1 | p3.2 +
  labs(caption = "80% and 95% credible intervals shown in black")
p3.6

# save a figure
ggsave("Exp_3/figures/t0_2_t0.jpeg",
       width = 15, height = 10)
```

```{r}
p3.6 <- p3.1 | p3.4 +
  labs(caption = "80% and 95% quantile intervals shown in black")
p3.6

# save a figure
ggsave("Exp_3/figures/t0_3_t0.jpeg",
       width = 21, height = 10)
```

