---
title: "wrangle"
author: "Raph & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

This file wrangles data for Exp 3 in the face familiarity study.
Note: No LBA model is fit for Exp 3 due to a timing quantisation artefact
in data collection (responses recorded in ~80ms bins).

```{r}
#| label: setup
#| include: false

pkgs <- c(
  "tidyverse", "here"
  )
vapply(
  pkgs, library, logical(1), character.only = TRUE, logical.return = TRUE
  )

theme_set(
  theme_bw() +
    theme(
      text  = element_text(size = 15, face = "bold"),
      title = element_text(size = 15, face = "bold"),
      legend.position = "none"
    )
)

safe_pal   <- paletteer::paletteer_d("rcartocolor::Safe", 4)

myColors_2 <- c("Novel" = safe_pal[1], "Famous" = safe_pal[3])

pd2        <- position_dodge(1)
```

# 1. Read in raw data

Raw data files are not stored in the repo. This section reads them in and
saves a combined file. Skip to section 2 if the combined file already exists.

```{r}
#| label: read-raw
#| eval: false

raw <- list.files(
  path       = here("exp_3", "data", "raw"),
  pattern    = "^raw.*csv",
  full.names = TRUE,
  recursive  = TRUE
) |>
  set_names() |>
  map(read_csv,
      col_names = c("subj", "block", "trial", "keypress", "rt", "ori", "stim", "fam")
  ) |>
  list_rbind(names_to = "file") |>
  mutate(pid = as.integer(str_sub(subj, 2, -1))) |>
  select(pid, block, trial, keypress, rt, ori, stim, fam)

write_csv(raw, here("exp_3", "data", "raw_data_exp_3.csv"))
```

# 2. Wrangle

```{r}
#| label: read-combined

raw <- read_csv(here("exp_3", "data", "raw_data_exp_3.csv"))
```

```{r}
#| label: wrangle-ratings

data_ratings <- list.files(
  path       = here("exp_3", "data"),
  pattern    = "Ratings.*csv",
  full.names = TRUE,
  recursive  = TRUE
) |>
  set_names() |>
  map(read_csv,
      col_names = c("Image_ID", "Fam_ratings", "Val_ratings", "Chosen_name")
  ) |>
  list_rbind(names_to = "file") |>
  mutate(pid = rep(1:40, each = 60)) |>
  select(-file)
```

```{r}
#| label: wrangle

data <- raw |>
  mutate(
    fam  = as.integer(fam),
    cond = if_else(fam == 1, "Famous", "Novel"),
    cond = factor(cond, levels = c("Famous", "Novel")),
    acc  = case_when(
      cond == "Famous" & keypress == "q" ~ 1L,
      cond == "Novel"  & keypress == "p" ~ 1L,
      TRUE                               ~ 0L
    ),
    block = as.integer(block)
  ) |>
  select(pid, block, trial, cond, keypress, acc, rt, ori, stim, fam)

write_csv(data, here("exp_3", "data", "wrangle_data_exp_3.csv"))
```

# 3. Exclusions

```{r}
#| label: exclusions

# Familiarity ratings exclusion — fewer than 30 ratings >= 7
exclude_ratings <- data_ratings |>
  group_by(pid) |>
  summarise(n_fam = sum(Fam_ratings > 6)) |>
  filter(n_fam < 30) |>
  pull(pid)

# Apply ratings exclusion first
data <- data |>
  filter(!pid %in% exclude_ratings)

# RT exclusion — participants with >25% missed trials
exclude_rt <- data |>
  group_by(pid) |>
  summarise(perc_excluded = mean(is.na(rt)) * 100) |>
  filter(perc_excluded > 25) |>
  pull(pid)

# Accuracy exclusion — on remaining participants
exclude_acc <- data |>
  filter(!pid %in% exclude_rt) |>
  drop_na(rt) |>
  group_by(pid) |>
  summarise(perc_acc = mean(acc) * 100) |>
  filter(perc_acc < 55 | perc_acc > 95) |>
  pull(pid)

# Apply all exclusions and remove missed trials
data <- data |>
  filter(
    !pid %in% exclude_rt,
    !pid %in% exclude_acc,
    !is.na(rt)
  )
```

```{r}
# old_data <- read_csv(here("exp_3", "data", "from_raph", "data_exp_3.csv"))
# 
# # compare row counts and participants
# nrow(old_data)
# nrow(data)
# n_distinct(old_data$pid)
# n_distinct(data$pid)
# 
# # check for any rt > 0.9 (the response deadline for exp 3)
# old_data |> filter(rt > 0.9) |> nrow()
# data |> filter(rt > 0.9) |> nrow()
# 
# # check for any rt < 0.2 
# old_data |> filter(rt < 0.2) |> nrow()
# data |> filter(rt < 0.2) |> nrow()
# 
# # pids in old data
# old_pids <- old_data |> distinct(pid) |> arrange(pid) |> pull(pid)
# 
# # pids in new data
# new_pids <- data |> distinct(pid) |> arrange(pid) |> pull(pid)
# 
# # are they identical?
# identical(old_pids, new_pids)
# 
# # if not, what differs?
# setdiff(old_pids, new_pids)  # in old but not new
# setdiff(new_pids, old_pids)  # in new but not old
```

```{r}
#| label: data-check

# trials per pid, block, condition
data |>
  group_by(pid, block, cond) |>
  summarise(n = n(), .groups = "drop")

# accuracy per pid, block, condition
data |>
  group_by(pid, block, cond) |>
  summarise(acc = mean(acc), .groups = "drop")

# exclusion summary
cat("Ratings exclusions:", length(exclude_ratings), "\n")
cat("RT exclusions:",      length(exclude_rt),      "\n")
cat("Accuracy exclusions:", length(exclude_acc),    "\n")
cat("Final n:",            n_distinct(data$pid),    "\n")
```

# 4. Summary statistics

```{r}
#| label: summary-rt-acc

# RT
rt_pid <- data |>
  group_by(pid, block, cond) |>
  summarise(
    mean = mean(rt),
    sd   = sd(rt),
    n    = n(),
    sem  = sd / sqrt(n),
    .groups = "drop"
  )

rt_group <- data |>
  group_by(cond) |>
  summarise(
    mean = mean(rt),
    sd   = sd(rt),
    n    = length(unique(pid)),
    sem  = sd / sqrt(n),
    .groups = "drop"
  )

# Accuracy
acc_pid <- data |>
  group_by(pid, block, cond) |>
  summarise(
    sum  = sum(acc),
    n    = n(),
    perc = sum / n * 100,
    .groups = "drop"
  )

acc_group <- acc_pid |>
  group_by(cond) |>
  summarise(
    mean_perc = mean(perc),
    sd        = sd(perc),
    n         = n(),
    sem       = sd / sqrt(n),
    .groups = "drop"
  )
```

# 5. Plots

```{r}
#| label: plot-rt-bar

if (!dir.exists(here("exp_3", "figures"))) {
  dir.create(here("exp_3", "figures"), recursive = TRUE)
}

p_rt <- ggplot(rt_group, aes(x = cond, y = mean, fill = cond, colour = cond)) +
  geom_col() +
  geom_errorbar(
    aes(ymin = mean - sem, ymax = mean + sem),
    colour = "black", width = 0.2
  ) +
  geom_point(
    data     = rt_pid |> group_by(pid, cond) |> summarise(mean = mean(mean), .groups = "drop"),
    aes(y    = mean),
    colour   = "black",
    alpha    = 0.7,
    position = pd2
  ) +
  scale_fill_manual(values   = myColors_2) +
  scale_colour_manual(values = myColors_2) +
  coord_cartesian(ylim = c(0, 2)) +
  labs(x = "Condition", y = "Mean RT [s]")

p_rt

```

```{r}
#| label: plot-acc-bar

p_acc <- ggplot(acc_group, aes(x = cond, y = mean_perc, fill = cond, colour = cond)) +
  geom_col() +
  geom_errorbar(
    aes(ymin = mean_perc - sem, ymax = mean_perc + sem),
    colour = "black", width = 0.2
  ) +
  geom_point(
    data     = acc_pid |> group_by(pid, cond) |> summarise(mean_perc = mean(perc), .groups = "drop"),
    aes(y    = mean_perc),
    colour   = "black",
    alpha    = 0.7,
    position = pd2
  ) +
  scale_fill_manual(values   = myColors_2) +
  scale_colour_manual(values = myColors_2) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(x = "Condition", y = "Accuracy [%]")

p_acc

```

```{r}
#| label: plot-rt-density

p_rt_density <- ggplot(data, aes(x = rt, fill = cond, colour = cond)) +
  geom_density(alpha = 0.7) +
  scale_fill_manual(values   = myColors_2) +
  scale_colour_manual(values = myColors_2) +
  labs(x = "RT [s]")

p_rt_density

```

```{r}
#| label: combined-plots

(p_rt | p_acc) / p_rt_density

ggsave(here("exp_3", "figures", "rt_acc.jpeg"), width = 8, height = 6)
```

# 6. Save

```{r}
#| label: save

write_csv(data, here("exp_3", "data", "data_exp_3.csv"))
```
