---
title: "Modelling_WP1_2_full_emc2"
author: "Fournier Raphaël"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load the libraries that we will be using #

## load packages ##

```{r load-pkg}
pkxg <- c("EMC2", "tidyverse", "RColorBrewer", "patchwork")

lapply(pkxg, library, character.only = TRUE)
```

## plot settings ##

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face="bold"), 
          title = element_text(size = 18, face="bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

# 1. read in the raw data and wrangle

## read in the wrangled data ##

Load data (30 pids)

```{r}
raw <- read_csv("Exp_2/data/data_exp_2/data_WP1_2_model.csv")
head(raw)
str(raw)
```

#Wrangle
```{r}
data_emc <- raw %>%
  select(pid, cond, keypress, rt) %>% 
  rename(subjects = pid, S = cond, R = keypress) %>% 
  mutate(subjects=factor(subjects),
         S=factor(S,
                  levels = c("Novel", "Famous")),
         R=if_else(R == "q", "Famous", "Novel"),
         R=factor(R,
                  levels = c("Novel", "Famous"))) %>% 
  as.data.frame() ## in DMC, post predict need a df and not a tibble. Same for EMC2 I think.
head(data_emc)
str(data_emc)
```

# 2. build model #

## set the match factor  ##

```{r}
matchfun=function(d)d$S==d$lR
```

```{r}
design_exp2_v4_full <- design(data = data_emc,model=LBA,matchfun=matchfun,
                       formula=list(v~0+S:lM,sv~0+lM,B~0+lR,A~0+lR,t0~0+S),
                       constants=c(sv_lMFALSE=log(1)))
```

```{r}
p_vector <- c("v_SNovel:lMFALSE"=4,"v_SFamous:lMFALSE"=4, "v_SNovel:lMTRUE"=4, "v_SFamous:lMTRUE"=4,
              sv_lMTRUE=log(.5), 
              B_lRNovel=log(2), B_lRFamous=log(2),
              A_lRNovel=log(.5), A_lRFamous=log(.5),
              t0_SNovel=log(.3), t0_SFamous=log(.3))

mapped_pars(p_vector, x=design_exp2_v4_full)
```

## set priors ##

try to copy dmc priors.

I made the A and t0 sd priors smaller as they are fixed values and it seemed odd to sample a wide range when they are fixed at .5 and .3, respectively.

```{r}
mu_mean=c("v_SNovel:lMFALSE"=0,"v_SFamous:lMFALSE"=0, "v_SNovel:lMTRUE"=1, "v_SFamous:lMTRUE"=1,
          sv_lMTRUE=log(.5), 
          B_lRNovel=log(1), B_lRFamous=log(1),
          A_lRNovel=log(.5),A_lRFamous=log(.5),
          t0_SNovel=log(.3), t0_SFamous=log(.3))

mu_sd=c("v_SNovel:lMFALSE"=2,"v_SFamous:lMFALSE"=2, "v_SNovel:lMTRUE"=2, "v_SFamous:lMTRUE"=2,
          sv_lMTRUE=.5, 
          B_lRNovel=.5, B_lRFamous=.5,
          A_lRNovel=.3,A_lRFamous=.3,
          t0_SNovel=.3, t0_SFamous=.3)

prior_exp2_v4_full <- prior(design_exp2_v4_full, type ='standard',mu_mean=mu_mean,mu_sd=mu_sd)

plot(x = prior_exp2_v4_full)
```            

## fit the model ##

Note that I changed iter and step_size to make the model fit better and sample quicker.

```{r}
LBA_exp2_v4_full <- make_emc(data_emc,design_exp2_v4_full,type="standard",  prior=prior_exp2_v4_full)
LBA_exp2_v4_full <- fit(LBA_exp2_v4_full, cores_per_chain = 2, fileName="Exp_2/models/tmp.RData",
                     iter = 10000, step_size = 500)
save(LBA_exp2_v3_t0,file="Exp_2/models/LBA_exp2_v4_full.RData") 
load("Exp_2/models/LBA_exp2_v4_full.RData")
```

# 3. check the model #

convergence 
efficiency?

```{r}
check(LBA_exp2_v4_full)
get_pars(LBA_exp2_v4_full, map = TRUE)
```

plot pars

```{r}
plot_pars(LBA_exp2_v4_full,selection="mu",layout=c(2,5))
```

# 4. calculate and plot posterior predictions #

```{r}
pp_LBA_exp2_v4_full <- predict(LBA_exp2_v4_full, n_cores = 10)
save(pp_LBA_exp2_v4_full,file="models/pp_LBA_exp2_v4_full.RData")
plot_fit(data_emc, pp_LBA_exp2_v4_full, factors = c("S"),layout=c(2,3))
```

# 5. Models'comparison
```{r}
load("Exp_2/models/LBA_exp2_v1.RData")
load("Exp_2/models/LBA_exp2_v2_bias.RData")
load("Exp_2/models/LBA_exp2_v3_t0.RData")
load("Exp_2/models/LBA_exp2_v4_full.RData")

models = list(LBA_exp2_v1,LBA_exp2_v2_bias,LBA_exp2_v3_t0,LBA_exp2_v4_full)
compare(models, cores_per_prop = 2)
```

