---
title: "wrangle"
author: "Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file wrangles the pilot data for the familiarity face perception study.

## load the libraries that we will be using ## 

## install ##

```{r install-pkg}
# install.packages(c("tidyverse", "RColorBrewer", "patchwork"))
```

take a snapshot of loaded packages and update the lock.file using renv

```{r snapshot-renv}
# take a snapshot and update the lock.file
renv::snapshot() # this is only necessary when new packages or installed or packages are updated.
```

## load ##

```{r load-pkg}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "gtsummary", "paletteer")

lapply(pkg, library, character.only = TRUE)
```

## plot settings ##

```{r}
## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 20), 
          title = element_text(size = 22),
          legend.position = "bottom")
)
```
custom_color
```{r}
myColors <- c("Novel" = paletteer_d("rcartocolor::Safe",4)[1],"Famous" =  paletteer_d("rcartocolor::Safe",4)[3])
```

## section 1 - read in the raw data ##

This chunk reads in the main raw data file

```{r}
raw <- list.files(path = "/Users/rfournier/Documents/PhD_Exp/WP1/Exp_2/Data/Exp_2", pattern = "^raw.*csv", full.names = TRUE,
                  recursive = TRUE) %>% # check out list.files for info on selecting a bunch of files
  set_names() %>% 
  map_dfr(read_csv, col_names = c("subj", "block", "trial", "keypress", "rt",
                                  "ori", "stim", "fam")) %>% # map makes read_csv iterative across the file names
  mutate(pid = as.numeric(str_sub(subj, 2, -1)),
         keypress = as.factor(keypress),
         cond = if_else(fam == 1, "Famous", "Novel"),
         cond = factor(cond, 
                       levels = c("Novel", "Famous")),
         block = factor(block)) %>%# make a numerical pid variable
  select(pid, everything(), -subj) # reorder things
head(raw)
glimpse(raw)
summary(raw)
```

data check

```{r}
raw %>% 
   distinct(pid)
```


### Wrangle the Familiarity ratings ###
```{r}
data_ratings <- list.files(path = "/Users/rfournier/Documents/PhD_Exp/WP1/Exp_2/Data/Exp_2", pattern = "Ratings.*csv", full.names = TRUE, recursive = TRUE)%>% # check out list.files for info on selecting a bunch of files
  set_names() %>% 
  map_dfr(read_csv, col_names = c("Image_ID", "Fam_ratings", "Val_ratings", "Chosen_name")) %>%
  add_column(pid = rep(1:40, each = 60), .before = "Image_ID") 

#list of participants with number of fam ratings between 7-10 is lower than 30
number_ratings <- data_ratings %>%
  select(pid, Fam_ratings) %>%
  group_by(pid) %>%
  mutate(number_fam = sum(Fam_ratings > 6)) %>%
  select(pid, number_fam) %>%
  distinct() %>%
  filter(number_fam < 30)
```

```{r}
#remove these participants
raw <- raw %>%
  filter(pid != 16,
         pid != 21,
         pid != 23,
         pid != 24,
         pid != 29,
         pid != 30,
         pid != 33,
         pid != 36,
         pid != 37)
```

### Exclusion criteria (preregistration OSF) ###

## Missed trials

# Calculate the number of missed trials for each participant and removing the ones with more than 40% of missed trials (72 trials)
```{r}
raw <- raw %>% 
  mutate(missed_trial = if_else(
        is.na(keypress), "yes", "no"))
filtered_subjects <- raw %>%  
  group_by(pid) %>%
  summarise(missed_count = sum(missed_trial == "yes", na.rm = TRUE)) %>%
  filter(missed_count > 45)#here 45 is 25% of the total number of trials (180)
raw <- raw %>%
  filter(!pid %in% filtered_subjects$pid)
```

#Checking for each participant the percentage of missed trials
```{r}
raw %>%
  select(pid,missed_trial) %>%
  tbl_summary(
    by = pid) %>%
  bold_labels()
```

#If needed, remove participants with percentage of missed trials > 40%
```{r}
#Here code
```


## Accuracy 

# Calculate accuracy
```{r}
data <- raw %>% 
  mutate(acc = case_when(
         cond == "Famous" & keypress == "q" ~ 1,
         cond == "Novel" & keypress == "p" ~ 1,
         TRUE ~ 0))%>%
  mutate(cond = fct_relevel(cond,"Novel", "Famous")) %>%
  drop_na(rt) #Removing the missed trials 
head(data)
```

data check

```{r}
data %>% 
  distinct(pid, block, cond, acc)

data %>%
  group_by(pid, block, cond) %>% 
  tally(acc)

```

#Checking participant on accuracy (Overall and per condtion) for each subject
```{r}
#Check overall accuracy
acc_pid_check <- data %>%
  group_by(pid) %>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)

#Check accuracy per condition
acc_pid_check_cond <- data %>%
  group_by(pid,cond) %>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
```

#Plot check overall accuracy
```{r}
p.acc <-ggplot(acc_pid_check, aes(x=pid, y=perc)) +
   geom_bar(stat="identity") +
   geom_hline(yintercept = 95, linetype = "dashed", color = "red")+
   geom_hline(yintercept = 55, linetype = "dashed", color = "red")+
   scale_fill_paletteer_d("rcartocolor::Safe") +
   scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Overall accuracy") +
   xlab("Pid") +
   ylab("Accuracy [%]") + ylim(c(0,100))
p.acc
ggsave("Exp_2/figures/acc_pid_barplot.jpeg",
       width = 8, height = 6)
```

#Remove participants if overall accuracy is <55% or >95%
```{r}
filtered_subjects_acc <- data %>%  
  group_by(pid) %>%
  summarise(accuracy = sum(acc),
            n = n(),
            perc = accuracy/n*100) %>%
  filter(perc > 95 | perc < 55)
data <- data %>%
  filter(!pid %in% filtered_subjects_acc$pid)
```

#Plot check overall accuracy again
```{r}
#Check overall accuracy
acc_pid_check_without <- data %>%
  group_by(pid) %>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)

p.acc_without <-ggplot(acc_pid_check_without, aes(x=pid, y=perc)) +
   geom_bar(stat="identity") +
   geom_hline(yintercept = 95, linetype = "dashed", color = "red")+
   geom_hline(yintercept = 55, linetype = "dashed", color = "red")+
   scale_fill_paletteer_d("rcartocolor::Safe") +
   scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Overall accuracy") +
   xlab("Pid") +
   ylab("Accuracy [%]") + ylim(c(0,100))
p.acc_without
ggsave("Exp_2/figures/acc_pid_barplot_without.jpeg",
       width = 8, height = 6)
```

##saving data
```{r}
write_csv(data, "Exp_2/data/data_exp_2/data_WP1_2_model.csv")
data<-read_csv("Exp_2/data/data_exp_2/data_WP1_2_model.csv")
data <- data %>%
    mutate(cond = fct_relevel(cond,"Novel", "Famous")) 
```


## section 3 - create summary data ##

first, create summary data for rt and accuracy at the pid level and at the 
group level

at the pid level
### rt ###
```{r}
rt_pid <- data %>% 
  group_by(pid,block, cond) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_pid
```


### acc ###
```{r}
acc_pid <- data %>% 
  group_by(pid, block, cond) %>% 
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid
```

at the group level

### rt ###
```{r}
rt_group <- data %>% 
  group_by(block, cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_group
```

### acc ###
```{r}
acc_group <- acc_pid %>% 
  group_by(cond,block) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group
```


### without block###
## rt ##
```{r}
rt_group_wblock <- data %>% 
  group_by(cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_group_wblock
```

## acc ##
```{r}
acc_group_wblock <- acc_pid %>% 
  group_by(cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_wblock
```


## section 4 - plot ##

just a few quick and dirty plots for now

density

rt

```{r}
p4.1 <- ggplot(data, aes(x=rt, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by block and condition") +
   facet_wrap(~block) +
   xlab("Response time [s]") +
   ylab("Density") +
   xlim(0,1.75)
p4.1

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/rt_density_pid.jpeg",
       #width = 8, height = 6)
```

acc

```{r}
p4.2 <- ggplot(data, aes(x=acc, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by block and condition") +
   facet_wrap(~block) +
   xlab("Accuracy") +
   ylab("Density")  
p4.2 

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_density_pid.jpeg",
       #width = 8, height = 6)
```

summary plots

rt

```{r}
p4.3 <- ggplot(rt_pid, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond)) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Mean response time by block and condition") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
  ylim(0,1)
p4.3

ggsave("Exp_2/figures/rt_line_pid.jpeg",
      width = 8, height = 8)
```

acc

```{r}
p4.4 <- ggplot(acc_pid, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond)) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by block and condition") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Accuracy [%]") + ylim(c(0,100))
  
p4.4

ggsave("Exp_2/figures/acc_line_pid_prob.jpeg",
       width = 8, height = 8)
```

group level summary data

rt

```{r}
p4.5 <- ggplot(rt_group, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by block and condition") +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
   ylim(0,1)
p4.5

ggsave("Exp_2/figures/rt_line_group.jpeg",
        width = 7, height = 8)
```

acc

```{r}
p4.6 <- ggplot(acc_group, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by block and condition") +
   xlab("Blocks") +
   ylab("Accuracy [%]") +
   ylim(30,100)

p4.6

ggsave("Exp_2/figures/acc_line_group.jpeg",
        width = 7, height = 8)
```

plot group data together

```{r}
p4.7 <- p4.5 | p4.6
p4.7

ggsave("Exp_2/figures/rt_acc_line_group.jpeg",
        width = 15, height = 6)
```

add pid dots to the group data

rt

```{r}
p4.8 <- ggplot(rt_group, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_jitter(data = rt_pid,
               position=position_jitterdodge(dodge.width =1), 
               alpha = 1, colour = "darkgrey") +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("rt by block and condition") +
   ylim(0,2.5)
p4.8
```

acc

```{r}
p4.9 <- ggplot(acc_group, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_jitter(data = acc_pid,
               position=position_jitterdodge(dodge.width =1), 
               alpha = 1, colour = "darkgrey") +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("acc by block and condition") +
   ylim(0,100)
p4.9
```

plot group data together

```{r}
p4.10 <- p4.8 | p4.9
p4.10

ggsave("figures/rt_acc_line_dots.jpeg",
       width = 10, height = 6)
```





barplot acc
```{r}
p.4.11 <- ggplot(acc_group_wblock, aes(x = cond,y=perc, 
                           fill=cond, colour=cond)) +
   geom_col() +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem), col = "black",
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by familiarity condition") +
   xlab("Familiarity") +
   ylab("Accuracy [%]") +
   ylim(0,100)+
   theme(legend.position = "none")

p.4.11

ggsave("Exp_2/figures/acc_barplot_group.jpeg",
        width = 8, height = 8)
```

barplot rt
```{r}
p.4.12 <- ggplot(rt_group_wblock, aes(x = cond,y=mean, 
                           fill=cond, colour=cond)) +
   geom_col() +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem), col = "black",
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by familiarity condition") +
   xlab("Familiarity") +
   ylab("Response time [s]") +
   ylim(0,1)+
   theme(legend.position = "none")

p.4.12

ggsave("Exp_2/figures/rt_barplot_group.jpeg",
        width = 8, height = 8)
```


## section 5 - save out some files ##

This is useful for future modelling and/or plotting without re-doing the wrangle
file.



##section 6 - exploratory analysis ##

Here I just want to have a look at the reaction times and accuracy for the different head orientations

#RT At pid level
1st orientation
```{r}
rt_ori_1 <- data %>%
  group_by(pid, block, cond, ori) %>% 
  filter(ori == 1) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_ori_1
```
Plot
```{r}

p5.1 <- ggplot(rt_ori_1, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond))+
   ggtitle("Orientation 1") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]")
p5.1
```

2nd orientation
```{r}
rt_ori_2 <- data %>%
  group_by(pid, block, cond, ori) %>% 
  filter(ori == 2) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_ori_2
```
Plot
```{r}

p5.2 <- ggplot(rt_ori_2, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond))+
   ggtitle("Orientation 2") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]")
p5.2
```

3rd orientation
```{r}
rt_ori_3 <- data %>%
  group_by(pid, block, cond, ori) %>% 
  filter(ori == 3) %>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_ori_3
```
Plot
```{r}

p5.3 <- ggplot(rt_ori_3, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond))+
   ggtitle("Orientation 3") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]")
p5.3
```

```{r}
p5.4 <-p5.1 | p5.2 | p5.3
p5.4
```

#At group level

RT
```{r}
rt_group_ori <- data %>% 
  group_by(block, ori) %>% 
  mutate(ori = as.factor(ori))%>% 
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_group_ori
```
Plot
```{r}
p5.5 <- ggplot(rt_group_ori, aes(x=block, y=mean, 
                           fill=ori, colour=ori)) +
   geom_bar(alpha = 3, position = pd2, stat = "identity") +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
   ggtitle("Response time by block and orientation of picture") +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
   ylim(0,3)
p5.5
ggsave("figures/rt_bar_ori_blocks.jpeg",
       width = 10, height = 6)
```


Acc / block

```{r}
acc_pid_ori<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori
```

```{r}
acc_group_ori <- acc_pid_ori %>% 
  group_by(block, ori) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori

```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori, aes(x=block, y=perc, 
                           fill=ori, colour=ori)) +
   geom_bar(aes(group = ori), position = pd2, stat = "identity") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
  
   ggtitle("Accuracy by block and condition") +
   xlab("Blocks") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6
ggsave("figures/acc_bar_ori_blocks.jpeg",
       width = 10, height = 6)
```

Acc / block / familiarity level
#Block 1
```{r}
acc_pid_ori_block_1<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  filter(block == "1")%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori
```

```{r}
acc_group_ori_block_1 <- acc_pid_ori_block_1 %>% 
  group_by(block, ori, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori_block_1
```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori_block_1, aes(x= ori, y=perc, colour=cond)) +
   geom_bar(aes(group = cond), position = position_dodge(1), stat = "identity", fill = "white") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem, col = cond),
                width=.2, position=position_dodge(1)) +
   ggtitle("Block 1: Accuracy by picture orientation and condition") +
   xlab("Picture orientation") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6

ggsave("figures/acc_bar_ori_block_1.jpeg",
       width = 10, height = 6)
```

#Block 2
```{r}
acc_pid_ori_block_2<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  filter(block == "2")%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori_block_2
```

```{r}
acc_group_ori_block_2 <- acc_pid_ori_block_2 %>% 
  group_by(block, ori, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori_block_2
```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori_block_2, aes(x= ori, y=perc, colour=cond)) +
   geom_bar(aes(group = cond), position = position_dodge(1), stat = "identity", fill = "white") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem, col = cond),
                width=.2, position=position_dodge(1)) +
   ggtitle("Block 2: Accuracy by picture orientation and condition") +
   xlab("Picture orientation") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6

ggsave("figures/acc_bar_ori_block_2.jpeg",
       width = 10, height = 6)
```

#Block 3
```{r}
acc_pid_ori_block_3<- data %>% 
  group_by(pid, block, cond, ori) %>%
  mutate(ori = as.factor(ori))%>%
  filter(block == "3")%>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid_ori_block_3
```

```{r}
acc_group_ori_block_3 <- acc_pid_ori_block_3 %>% 
  group_by(block, ori, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_ori_block_3
```
Plot
```{r}
p4.6 <- ggplot(acc_group_ori_block_3, aes(x= ori, y=perc, colour=cond)) +
   geom_bar(aes(group = cond), position = position_dodge(1), stat = "identity", fill = "white") +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem, col = cond),
                width=.2, position=position_dodge(1)) +
   ggtitle("Block 3: Accuracy by picture orientation and condition") +
   xlab("Picture orientation") +
   ylab("Accuracy [%]") +
   ylim(0,100)
p4.6

ggsave("figures/acc_bar_ori_block_3.jpeg",
       width = 10, height = 6)
```

## Hit Rate and False Alarm Analysis ##


# Familiar condition #
Calculating hit rate "fam"
```{r}
data_fam <- data %>%
  select(pid,block,trial,keypress,rt,fam,cond) %>%
  filter(cond == "fam") %>%
  mutate(hit = case_when(
         cond == "fam" & keypress == "q" ~ 1,
         cond == "fam" & keypress == "p" ~ 0,
         TRUE ~ 0))
```

at the pid level

```{r}
hit_pid <- data_fam %>% 
  group_by(pid, block,cond) %>% 
  summarise(sum = sum(hit),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
```

at the group level

```{r}
hit_group <- hit_pid %>% 
  group_by(block, cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
hit_group
```

Calculating false alarm for "fam" response
```{r}
data_unfam <- data %>%
  select(pid,block,trial,keypress,rt,fam,cond) %>%
  filter(cond == "unf") %>%
  mutate(false = case_when(
         cond == "unf" & keypress == "q" ~ 1,
         cond == "unf" & keypress == "p" ~ 0,
         TRUE ~ 0))
```

at the pid level
```{r}
false_pid <- data_unfam %>% 
  group_by(pid, block, cond) %>%
  summarise(sum = sum(false),
            n = n(),
            perc = sum/n*100)
```

at the group level

```{r}
false_group <- false_pid %>% 
  group_by(block,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
false_group
```

#Merge two stats together and plot
```{r}
false_group$perc_hit <- hit_group$perc
p5.1 <- ggplot(false_group, aes(x = block, y = ))
```




