---
title: "sandpit"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

This file is useful to de-bug and try stuff out.

# The things I wanted to check are as follows:

1.  Different plot layouts for the raw RT and accuracy data.
2.  De-bug why the Exp 3 RT data looks so damn weird.
3.  Consider a summary figure in the discussion or results.

```{r}
#| label: setup
#| include: false

pkg <- c("tidyverse", "RColorBrewer", "patchwork", "paletteer", "here", "tidybayes", "styler")

lapply(pkg, library, character.only = TRUE)

knitr::opts_chunk$set(echo = FALSE)

theme_set(
  theme_bw() +
    theme(text = element_text(size = 15, face = "bold"), 
          title = element_text(size = 15, face = "bold"),
          legend.position = "right")
)
## plot settings ##
## Plot colors
myColors_1 <- c("Novel" = paletteer_d("rcartocolor::Safe",4)[1],"Learned" =  paletteer_d("rcartocolor::Safe",4)[2])
myColors_2 <- c("Novel" = paletteer_d("rcartocolor::Safe",4)[1],"Famous" =  paletteer_d("rcartocolor::Safe",4)[3])
myColors_3 <- c("Novel" = paletteer_d("rcartocolor::Safe",4)[1],"Learned" =  paletteer_d("rcartocolor::Safe",4)[2], "Famous" = paletteer_d("rcartocolor::Safe",4)[3])
## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)

#Color drift rate
myColors_drift <- RColorBrewer::brewer.pal(12, "Dark2")[4:5]
colScale_drift <- scale_fill_manual(name = "Accuracy", values = myColors_drift)

```

# 1. Different plots

## Separate analysis of response times and accuracy

The below code chunk was taken from the Manuscript Supps section. This code was written by Raph.

```{r}
#| label: rt-acc-all
#| include: false

#Load the RT and accuracy data for each experiment
data_1 <- read_csv(here("Exp_1", "data", "data.csv"))
data_2 <- read_csv(here("Exp_2", "data", "data_exp_2.csv"))
data_3 <- read_csv(here("Exp_3", "data", "data_exp_3.csv"))
data_4 <- read_csv(here("Exp_4", "data", "data_exp_4.csv")) %>%
  mutate(cond = fct_recode(cond, Famous = "familiar", Novel = "novel"))

#Create plots for accuracy for each experiment
#Exp1
acc_pid_1 <- data_1 %>% 
  group_by(pid, block, cond) %>% 
  summarise(sum = sum(acc),
            n = n(), 
            perc = sum/n*100)

acc_group_wblock_1 <- acc_pid_1 %>% 
  group_by(cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)

acc_pid_wblock_1 <- acc_pid_1 %>%
  mutate(pid = as.character(as.factor(pid))) %>%
  group_by(pid,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc) %>%
  left_join(acc_group_wblock_1, by = join_by(cond)) %>%
  mutate(Experiment = "Experiment 1")

#Exp2
acc_pid_2 <- data_2 %>% 
  group_by(pid, block, cond) %>% 
  summarise(sum = sum(acc),
            n = n(), 
            perc = sum/n*100)

acc_group_wblock_2 <- acc_pid_2 %>% 
  group_by(cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)

acc_pid_wblock_2 <- acc_pid_2 %>% 
  group_by(pid,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc) %>%
  left_join(acc_group_wblock_2, by = join_by(cond))%>%
  mutate(Experiment = "Experiment 2")

#Exp3
acc_pid_3 <- data_3 %>% 
  group_by(pid, block, cond) %>% 
  summarise(sum = sum(acc),
            n = n(), 
            perc = sum/n*100)

acc_group_wblock_3 <- acc_pid_3 %>% 
  group_by(cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)

acc_pid_wblock_3 <- acc_pid_3 %>%
  mutate(pid = as.character(as.factor(pid))) %>%
  group_by(pid,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc) %>%
  left_join(acc_group_wblock_3, by = join_by(cond))%>%
  mutate(Experiment = "Experiment 3")

#Exp4
acc_pid_4 <- data_4 %>% 
  group_by(pid, block, cond) %>% 
  summarise(sum = sum(acc),
            n = n(), 
            perc = sum/n*100)

acc_group_wblock_4 <- acc_pid_4 %>% 
  group_by(cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)

acc_pid_wblock_4 <- acc_pid_4 %>%
  mutate(pid = as.character(as.factor(pid))) %>%
  group_by(pid,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), 
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc) %>%
  left_join(acc_group_wblock_4, by = join_by(cond))%>%
  mutate(Experiment = "Experiment 4")

#Create plots for RT for each experiment
#Exp1
rt_group_wblock_1 <- data_1 %>% 
  group_by(cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)

rt_pid_wblock_1 <- data_1 %>% 
  mutate(pid = as.character(as.factor(pid))) %>%
  group_by(pid,cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96) %>%
  left_join(rt_group_wblock_1, by = join_by(cond)) %>%
  mutate(Experiment = "Experiment 1")

rt_density_1 <- data_1 %>%
  select(cond, rt) %>%
  mutate(Experiment = "Experiment 1")
#Exp2
rt_group_wblock_2 <- data_2 %>% 
  group_by(cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)

rt_pid_wblock_2 <- data_2 %>% 
  group_by(pid,cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96) %>%
  left_join(rt_group_wblock_2, by = join_by(cond)) %>%
  mutate(Experiment = "Experiment 2")

rt_density_2 <- data_2 %>%
  select(cond, rt) %>%
  mutate(Experiment = "Experiment 2")
#Exp3
rt_group_wblock_3 <- data_3 %>% 
  group_by(cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)

rt_pid_wblock_3 <- data_3 %>% 
  mutate(pid = as.character(as.factor(pid))) %>%
  group_by(pid,cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96) %>%
  left_join(rt_group_wblock_3, by = join_by(cond)) %>%
  mutate(Experiment = "Experiment 3")

rt_density_3 <- data_3 %>%
  select(cond, rt) %>%
  mutate(Experiment = "Experiment 3")

#Exp4
rt_group_wblock_4 <- data_4 %>% 
  group_by(cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)

rt_pid_wblock_4 <- data_4 %>% 
  group_by(pid,cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96) %>%
  left_join(rt_group_wblock_4, by = join_by(cond)) %>%
  mutate(Experiment = "Experiment 4")

rt_density_4 <- data_4 %>%
  select(cond, rt) %>%
  mutate(Experiment = "Experiment 4")
#Joining experiments data

acc_all <- acc_pid_wblock_1 %>%
  bind_rows(acc_pid_wblock_2) %>%
  bind_rows(acc_pid_wblock_3) %>%
  bind_rows(acc_pid_wblock_4)

rt_all <- rt_pid_wblock_1 %>%
  bind_rows(rt_pid_wblock_2) %>%
  bind_rows(rt_pid_wblock_3) %>%
  bind_rows(rt_pid_wblock_4)

rt_density <- rt_density_1 %>%
  bind_rows(rt_density_2) %>%
  bind_rows(rt_density_3) %>%
  bind_rows(rt_density_4)

#plot acc by experiment
plot_acc <- ggplot(acc_all, aes(x = factor(cond),y=perc.y, 
                           fill=cond, colour=cond)) +
   geom_col() +
   geom_errorbar(aes(ymin = perc.y-sem.y, ymax = perc.y+sem.y), col = "black",
                width=.2, position=pd2) +
   geom_point(aes(y = perc.x),
             colour = "black",
             stat = "identity",
             position=pd2,
             alpha = .7)+
   scale_fill_manual(values = myColors_3) +
   scale_color_manual(values = myColors_3) +
   xlab("Conditions") +
   ylab("Proportion correct [%]") +
   ylim(0,100) +
   facet_grid(~Experiment, scales = "free_x") +
   theme(legend.position = "none")

plot_rt <- ggplot(rt_all, aes(x = cond,y=mean.y, 
                           fill=cond, colour=cond)) +
   geom_bar(stat="summary") +
   geom_errorbar(aes(ymin = mean.y-sem.y, ymax = mean.y+sem.y), col = "black",
                width=.2, position=pd2) +
  geom_point(aes(y = mean.x),
             colour = "black",
             stat = "identity",
             position=pd2,
             alpha = .7)+
   scale_fill_manual(values = myColors_3) +
   scale_color_manual(values = myColors_3) +
   xlab("Conditions") +
   ylab("Mean response times [s]") +
   ylim(0,1.75)+
   theme(legend.position = "none") +
   facet_grid(~Experiment, scales = "free_x")

plot_rt_density_cond <- ggplot(rt_density, aes(x=rt, fill=cond, colour=cond)) +
  geom_density(alpha=0.5) +
  scale_fill_manual(values = myColors_3) +
  scale_colour_manual(values = myColors_3)  +
  facet_wrap(~block) +
  labs(fill = "Conditions", colour = "Conditions") +
  xlab("Response time [s]") +
  ylab("Density") +
  facet_grid(~Experiment, scales = "free_x") +
  theme(legend.position = c(.92,.82),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 8))
```

### A more compact way to do this

```{r}
# ── Libraries ────────────────────────────────────────────────────────────────
# library(tidyverse)
# library(here)

# ── Colours ────────────────────────────────────────────────────────────────

safe_pal <- paletteer_d("rcartocolor::Safe", 4)

myColors_3 <- c(
  "novel"   = safe_pal[1],
  "learned" = safe_pal[2],
  "famous"  = safe_pal[3]
)

# Subsets for single-experiment plots if still needed
myColors_1 <- myColors_3[c("novel", "learned")]
myColors_2 <- myColors_3[c("novel", "famous")]

# ── Load & normalise ─────────────────────────────────────────────────────────
# Each experiment gets labelled and pid coerced to character on read-in
read_exp <- function(path, exp_number, recode = NULL) {
  read_csv(here(path)) |>
    mutate(
      pid        = as.integer(factor(pid)),  # consistent across both formats
      experiment = as.integer(exp_number),
      block      = as.integer(block),
      cond       = str_to_lower(cond)
    ) |>
    (\(df) if (!is.null(recode)) mutate(df, cond = dplyr::recode(cond, !!!recode)) else df)() |>
    select(pid, block, experiment, cond, acc, rt)
}

data_all <- bind_rows(
  read_exp("Exp_1/data/data.csv",       1),
  read_exp("Exp_2/data/data_exp_2.csv", 2),
  read_exp("Exp_3/data/data_exp_3.csv", 3),
  read_exp("Exp_4/data/data_exp_4.csv", 4, recode = c(familiar = "famous", novel = "novel"))
)

head(data_all)

# ── Summary helpers ───────────────────────────────────────────────────────────
# Participant-level summary, then group-level summary joined back on
summarise_pid <- function(df, outcome_col, summary_fn) {
  summary_fn <- rlang::as_function(summary_fn)  # handles both mean and ~ mean(.x)*100
  
  pid_level <- df |>
    drop_na(all_of(outcome_col)) |>
    group_by(experiment, pid, cond) |>
    summarise(pid_val = summary_fn(.data[[outcome_col]]), .groups = "drop")

  grp_level <- pid_level |>
    group_by(experiment, cond) |>
    summarise(
      grp_val = mean(pid_val),
      sem     = sd(pid_val) / sqrt(n()),
      .groups = "drop"
    )

  left_join(pid_level, grp_level, by = c("experiment", "cond"))
}

acc_all <- summarise_pid(data_all, "acc", ~ mean(.x) * 100)
head(acc_all)
rt_all  <- summarise_pid(data_all, "rt",  mean)
head(rt_all)

# ── Shared plot scaffold ──────────────────────────────────────────────────────
base_bar <- function(df, ylab) {
  grp <- df |> distinct(experiment, cond, grp_val, sem)  # one row per group
  
  ggplot(df, aes(x = cond, fill = cond, colour = cond)) +
    geom_col(data = grp, aes(y = grp_val)) +
    geom_errorbar(
      data = grp,
      aes(ymin = grp_val - sem, ymax = grp_val + sem),
      colour = "black", width = 0.2
    ) +
    geom_point(aes(y = pid_val), colour = "black", alpha = 0.7,
               position = position_dodge(0.2)) +
    scale_fill_manual(values   = myColors_3) +
    scale_colour_manual(values = myColors_3) +
    facet_grid(~ experiment, scales = "free_x",
               labeller = labeller(experiment = ~ paste("Experiment", .x))) +
    labs(x = "Condition", y = ylab) +
    theme(legend.position = "none")
}

plot_acc <- base_bar(acc_all, "Proportion correct [%]") + coord_cartesian(ylim = c(0, 100))
plot_acc

plot_rt  <- base_bar(rt_all,  "Mean response time [s]") + coord_cartesian(ylim = c(0, 1.75))
plot_rt

plot_rt_density <- ggplot(
  data_all |> drop_na(rt),
  aes(x = rt, fill = cond, colour = cond)
) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values   = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  facet_grid(~ experiment, scales = "free_x",
               labeller = labeller(experiment = ~ paste("Experiment", .x))) +
  labs(x = "Response time [s]", y = "Density",
       fill = "Condition", colour = "Condition") +
  theme(
    legend.position  = c(.92, .82),
    legend.text      = element_text(size = 7),
    legend.title     = element_text(size = 8)
  )
plot_rt_density

ggsave("sandpit/figures/rt_density.png",
       width = 7, height = 4)
```

## And now the alternative approaches

Basically, avoid the bar plot because they don't offer much information, then maybe combine dots with density into one plot.

-   halfeye plot with jittered dots and slab (custom rain plot)

-   beeswarm plot - e.g., dots form the density plot.

halfeye plot

```{r}
# Define which conditions belong to which experiments
exp_conds <- tribble(
  ~experiment, ~cond,
  1, "learned", 1, "novel",
  2, "learned", 2, "novel",
  3, "famous",  3, "novel",
  4, "famous",  4, "novel"
)

# Filter rt_all and acc_all to only relevant conditions per experiment
rt_plot_data  <- rt_all  |> semi_join(exp_conds, by = c("experiment", "cond"))
acc_plot_data <- acc_all |> semi_join(exp_conds, by = c("experiment", "cond"))

# Shared plot function to avoid repetition
halfeye_plot <- function(df, yvar, ylab, ylims) {
  ggplot(df, aes(x = cond, y = {{ yvar }}, fill = cond, colour = cond)) +
    stat_halfeye(
      aes(x = as.numeric(factor(cond)) + 0.15),
      side = "right",
      scale = 0.4,
      alpha = 0.5,
      adjust = 1.5,
      point_interval = NULL
    ) +
    geom_point(
      aes(x = as.numeric(factor(cond)) - 0.1),
      position = position_jitter(width = 0.06, height = 0, seed = 42),
      alpha = 0.4,
      size = 1.5
    ) +
    # group mean + CI
    stat_summary(
      aes(x = as.numeric(factor(cond))),
      fun.data = mean_se,
      geom = "pointrange",
      colour = "black",
      size = 0.5,
      linewidth = 1,
      fun.args = list(mult = 1.96)
    ) +
    # line connecting group means
    stat_summary(
      aes(x = as.numeric(factor(cond)), group = experiment),
      fun = mean,
      geom = "line",
      colour = "black",
      linewidth = 0.8
    ) +
    scale_x_continuous(
      breaks = c(1, 2),
      labels = function(x) {
        # dynamically label based on conditions present in each facet
        levels(factor(df$cond))[x]
      },
      expand = expansion(add = c(0.4, 0.4))
    ) +
    scale_fill_manual(values = myColors_3) +
    scale_colour_manual(values = myColors_3) +
    facet_grid(
      ~experiment,
      scales = "free_x",
      labeller = labeller(experiment = ~ paste("Experiment", .x))
    ) +
    coord_cartesian(ylim = ylims) +
    labs(x = "Condition", y = ylab) +
    theme(
      axis.text.x = element_blank()
    )
}

plot_acc_halfeye <- halfeye_plot(acc_plot_data, pid_val, "Accuracy [%]",   c(0, 100))
plot_rt_halfeye  <- halfeye_plot(rt_plot_data,  pid_val, "Mean RT [s]",    c(0, 1.75))

plot_acc_halfeye / plot_rt_halfeye
```

alternative

```{r}
halfeye_plot <- function(df, yvar, ylab, ylims) {
  ggplot(df, aes(x = cond, y = {{ yvar }}, 
                 fill = cond, colour = cond)) +
    # per-participant lines
    geom_line(
      aes(group = pid),
      colour    = "grey70",
      linewidth = 0.3,
      alpha     = 0.5
    ) +
    # per-participant dots
    geom_point(
      position = position_jitter(width = 0.06, height = 0, seed = 123),
      alpha    = 0.5,
      size     = 1.5
    ) +
    # group mean + 95% CI
    stat_summary(
      fun.data  = mean_se,
      geom      = "pointrange",
      colour    = "black",
      size      = 0.6,
      linewidth = 1.2,
      fun.args  = list(mult = 1.96)
    ) +
    # line connecting group means
    stat_summary(
      aes(group = experiment),
      fun       = mean,
      geom      = "line",
      colour    = "black",
      linewidth = 0.8
    ) +
    scale_fill_manual(values   = myColors_3) +
    scale_colour_manual(values = myColors_3) +
    facet_grid(
      ~ experiment, scales = "free_x",
      labeller = labeller(experiment = ~ paste("Experiment", .x))
    ) +
    coord_cartesian(ylim = ylims) +
    labs(x = NULL, y = ylab) +
    theme(legend.position = "none")
}

plot_acc_paired <- halfeye_plot(acc_plot_data, pid_val, "Accuracy [%]",  c(0, 100))
plot_acc_paired

ggsave("sandpit/figures/plot_acc_paired.png",
       width = 7, height = 4)

plot_rt_paired  <- halfeye_plot(rt_plot_data,  pid_val, "Mean RT [s]",   c(0, 1.75))
plot_rt_paired

ggsave("sandpit/figures/plot_rt_paired.png",
       width = 7, height = 4)

plot_paired <- (plot_acc_paired / plot_rt_paired)
plot_paired

ggsave("sandpit/figures/plot_paired.png",
       width = 8, height = 6)
```

density

```{r}
# Annotation data - only for Exp 3
annotation_df <- tibble(
  experiment = 3,
  x          = 0.35,
  y          = 6.5,
  label      = "RT quantisation\nartefact (80ms bins)"
)

arrow_df <- tibble(
  experiment = 3,
  x          = 0.52,
  xend       = 0.58,
  y          = 5.8,
  yend       = 4.5
)

density_plot <- function(df, xlims) {
  ggplot(
    df |> semi_join(exp_conds, by = c("experiment", "cond")),
    aes(x = rt, fill = cond, colour = cond)
  ) +
    geom_density(alpha = 0.5) +
    scale_fill_manual(values   = myColors_3) +
    scale_colour_manual(values = myColors_3) +
    scale_x_continuous(
      breaks = seq(0, 10, by = 0.5),  # same increment everywhere
      limits = xlims
    ) +
    facet_grid(
      ~ experiment,
      labeller = labeller(experiment = ~ paste("Experiment", .x))
    ) +
    labs(x = "Response time [s]", y = "Density",
         fill = "Condition", colour = "Condition") +
    theme(legend.position = "none")
}

p_density_12 <- density_plot(
  data_all |> filter(experiment %in% c(1, 2)),
  xlims = c(0, 2.5)
)

p_density_34 <- density_plot(
  data_all |> filter(experiment %in% c(3, 4)),
  xlims = c(0, 1.1)
) +
  geom_text(
    data      = annotation_df,
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE,
    size        = 2.8,
    hjust       = 0,
    colour      = "grey40",
    lineheight  = 0.9
  ) +
  geom_segment(
    data      = arrow_df,
    aes(x = x, xend = xend, y = y, yend = yend),
    inherit.aes = FALSE,
    colour      = "grey40",
    linewidth   = 0.4,
    arrow       = arrow(length = unit(0.15, "cm"))
  )

p_density_all <- (p_density_12 | p_density_34) +
  plot_layout(
    axes = "collect",
    axis_titles = "collect"
  )
```

and another

```{r}
plot_rt_density <- ggplot(
  data_all |>
    drop_na(rt) |>
    semi_join(exp_conds, by = c("experiment", "cond")),
  aes(x = rt, fill = cond, colour = cond)
) +
  geom_density(alpha = 0.5) +
  # annotation targeting Exp 3 only
  geom_text(
    data = tibble(
      experiment = 3,
      x          = 0.22,
      y          = 7.2,
      label      = "RT \nartefact (80ms bins)"
    ),
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE,
    size = 2.5,
    hjust = 0,
    colour = "grey40",
    lineheight = 0.9
  ) +
  geom_segment(
    data = tibble(
      experiment = 3,
      x = 0.50, xend = 0.60,
      y = 6.8, yend = 5.5
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    inherit.aes = FALSE,
    colour = "grey40",
    linewidth = 0.4,
    arrow = arrow(length = unit(0.15, "cm"))
  ) +
  scale_fill_manual(values = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  scale_x_continuous(
    breaks = function(x) {
      seq(
        floor(min(x) * 2) / 2, # round down to nearest 0.5
        ceiling(max(x) * 2) / 2, # round up to nearest 0.5
        by = 0.5
      )
    }
  ) +
  facet_grid(
    ~experiment,
    scales   = "free_x", # each exp gets its own x range
    labeller = labeller(experiment = ~ paste("Experiment", .x))
  ) +
  labs(
    x      = "Response time [s]",
    y      = "Density",
    fill   = "Condition",
    colour = "Condition"
  ) +
  theme(
    legend.position  = c(0.9, 0.8),
    legend.text      = element_text(size = 7),
    legend.title     = element_text(size = 8)
  )
plot_rt_density
```

```{r}
plot_rt_density <- ggplot(
  data_all |> 
    drop_na(rt) |>
    semi_join(exp_conds, by = c("experiment", "cond")),
  aes(x = rt, fill = cond, colour = cond)
) +
  geom_density(alpha = 0.5) +
  geom_text(
    data = tibble(
      experiment = 3,
      x = 0.10, y = 7.5,
      label = "RT quantisation\nartefact (80ms bins)"
    ),
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE,
    size = 2.5, hjust = 0,
    colour = "grey40", lineheight = 0.9
  ) +
  geom_segment(
    data = tibble(
      experiment = 3,
      x = 0.48, xend = 0.58,
      y = 6.8,  yend = 5.5
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    inherit.aes = FALSE,
    colour = "grey40", linewidth = 0.4,
    arrow = arrow(length = unit(0.15, "cm"))
  ) +
  scale_fill_manual(values   = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  scale_x_continuous(
    breaks = seq(0, 3, by = 0.5),
    expand = expansion(add = c(0, 0))
  ) +
  facet_grid(
    ~ experiment,
    scales   = "free_x",
    labeller = labeller(experiment = ~ paste("Experiment", .x))
  ) +
  labs(
    x = "Response time [s]", y = "Density",
    fill = "Condition", colour = "Condition"
  ) +
  theme(
    legend.position  = c(0.97, 0.82),
    legend.text      = element_text(size = 7),
    legend.title     = element_text(size = 8)
  )
plot_rt_density
```

```{r}
density_12 <- data_all |>
  filter(experiment %in% c(1, 2)) |>
  drop_na(rt) |>
  semi_join(exp_conds, by = c("experiment", "cond")) |>
  ggplot(aes(x = rt, fill = cond, colour = cond)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values   = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  scale_x_continuous(breaks = seq(0, 2.5, by = 0.5)) +
  coord_cartesian(xlim = c(0, 2.5), ylim = c(0, 1.5)) +
  facet_grid(~ experiment,
             labeller = labeller(experiment = ~ paste("Experiment", .x))) +
  labs(x = "Response time [s]", y = "Density") +
  theme(legend.position = "none")

density_34 <- data_all |>
  filter(experiment %in% c(3, 4)) |>
  drop_na(rt) |>
  semi_join(exp_conds, by = c("experiment", "cond")) |>
  ggplot(aes(x = rt, fill = cond, colour = cond)) +
  geom_density(alpha = 0.5) +
  geom_text(
    data = tibble(experiment = 3, x = 0.08, y = 7.5,
                  label = "RT quantisation\nartefact (80ms bins)"),
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE, size = 2.5, hjust = 0,
    colour = "grey40", lineheight = 0.9
  ) +
  geom_segment(
    data = tibble(experiment = 3, x = 0.48, xend = 0.58, y = 6.8, yend = 5.5),
    aes(x = x, xend = xend, y = y, yend = yend),
    inherit.aes = FALSE, colour = "grey40", linewidth = 0.4,
    arrow = arrow(length = unit(0.15, "cm"))
  ) +
  scale_fill_manual(values   = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  scale_x_continuous(breaks = seq(0, 1.0, by = 0.5)) +
  coord_cartesian(xlim = c(0, 1.2), ylim = c(0, 8)) +
  facet_grid(~ experiment,
             labeller = labeller(experiment = ~ paste("Experiment", .x))) +
  labs(x = "Response time [s]", y = "Density",
       fill = "Condition", colour = "Condition") +
  theme(
    legend.position  = c(0.95, 0.80),
    legend.text      = element_text(size = 7),
    legend.title     = element_text(size = 8)
  )

density_12 | density_34
```

```{r}
# Dummy data to set x limits per experiment
dummy_limits <- tibble(
  experiment = c(1, 1, 2, 2, 3, 3, 4, 4),
  rt         = c(0, 2.5, 0, 2.5, 0, 1.1, 0, 1.1),
  cond       = "novel",
  density    = 0
)

plot_rt_density <- data_all |>
  drop_na(rt) |>
  semi_join(exp_conds, by = c("experiment", "cond")) |>
  ggplot(aes(x = rt, fill = cond, colour = cond)) +
  geom_density(alpha = 0.5) +
  # invisible points to set x range per facet
  geom_blank(
    data = dummy_limits,
    aes(x = rt),
    inherit.aes = FALSE
  ) +
  geom_text(
    data = tibble(experiment = 3, x = 0.08, y = 7,
                  label = "RT artefact\n (80ms bins)"),
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE, size = 2.5, hjust = 0,
    colour = "grey40", lineheight = 0.9
  ) +
  geom_segment(
    data = tibble(experiment = 3, x = 0.48, xend = 0.58, y = 6.7, yend = 5.5),
    aes(x = x, xend = xend, y = y, yend = yend),
    inherit.aes = FALSE, colour = "grey40", linewidth = 0.4,
    arrow = arrow(length = unit(0.15, "cm"))
  ) +
  scale_fill_manual(values   = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  scale_x_continuous(breaks = seq(0, 2.5, by = 0.5)) +
  facet_grid(
    ~ experiment,
    scales   = "free_x",
    labeller = labeller(experiment = ~ paste("Experiment", .x))
  ) +
  labs(x = "Response time [s]", y = "Density",
       fill = "Condition", colour = "Condition") +
  theme(
    legend.position  = c(0.92, 0.8),
    legend.text      = element_text(size = 7),
    legend.title     = element_text(size = 8)
  )
plot_rt_density

ggsave("sandpit/figures/rt_density_v2.png",
       width = 7, height = 4)

```

# 2. De-bug why the Exp 3 RT data looks so damn weird.

```{r}
# 1. First look at per-pid densities to spot outliers
exp3_rt_density_pid <- data_all |>
  filter(experiment == 3) |>
  ggplot(aes(x = rt, fill = cond, colour = cond)) +
  geom_density(alpha = 0.4) +
  facet_wrap(~ pid, scales = "free_y") +
  scale_fill_manual(values = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  labs(x = "Response time [s]", y = "Density")
exp3_rt_density_pid

ggsave("sandpit/figures/exp3_rt_density_pid.png",
       width = 12, height = 10)

# 2. Check summary stats per pid - look for very low SD or suspicious mean
data_all |>
  filter(experiment == 3) |>
  group_by(pid) |>
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    sd_rt   = sd(rt, na.rm = TRUE),
    min_rt  = min(rt, na.rm = TRUE),
    max_rt  = max(rt, na.rm = TRUE),
    n       = n()
  ) |>
  arrange(sd_rt) |>
  print(n = Inf)

# 3. Look at the raw RT distribution more carefully - are values discretised?
data_all |>
  filter(experiment == 3) |>
  pull(rt) |>
  round(3) |>
  table() |>
  sort(decreasing = TRUE) |>
  head(20)
```

The RT distribution itself looks fine — no discretisation issues, the values are continuous and the SD is reasonable across all participants. The spikiness in the famous condition is actually present in every participant — look at the per-pid plots, almost all of them show that characteristic double/triple peak in the famous (yellow) distribution. This is a real experimental effect, not a data quality issue.

```{r}
# Look at the famous condition specifically - is it bimodal?
data_all |>
  filter(experiment == 3) |>
  group_by(cond, pid) |>
  summarise(
    mean_rt = mean(rt),
    sd_rt   = sd(rt),
    n       = n(),
    .groups = "drop"
  ) |>
  group_by(cond) |>
  summarise(across(c(mean_rt, sd_rt, n), mean))

# Are the peaks in famous at consistent RT values across participants?
data_all |>
  filter(experiment == 3, cond == "famous") |>
  ggplot(aes(x = rt)) +
  geom_density() +
  facet_wrap(~ pid, scales = "free_y")

# Check if the multimodality relates to block or trial position
data_all |>
  filter(experiment == 3) |>
  ggplot(aes(x = rt, fill = cond, colour = cond)) +
  geom_density(alpha = 0.4) +
  facet_wrap(~ block) +
  scale_fill_manual(values = myColors_3) +
  scale_colour_manual(values = myColors_3)
```

is there an orientation effect?

```{r}
# Check if ori explains the bimodality in Exp 3
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  ggplot(aes(x = rt, fill = factor(ori), colour = factor(ori))) +
  geom_density(alpha = 0.4) +
  facet_wrap(~ pid, scales = "free_y")
```

```{r}
# Confirm the ori effect quantitatively across cond and experiment
# Simplest - just read raw file directly, no join needed
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  group_by(cond, ori) |>
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    sd_rt   = sd(rt, na.rm = TRUE),
    n       = n(),
    .groups = "drop"
  )
```

So orientation has essentially no effect on RT — the means are virtually identical across ori 1, 2, 3 for both conditions (differences of \~0.003s). That rules out orientation as the explanation for the bimodal distribution we saw visually. So we're back to the earlier per-pid density plots being the real clue. Looking at those again, the peaks in the famous distribution are consistent across participants but the earlier ori plot appeared to show separation — that was actually the many-to-many join artefact inflating the visual signal. The most likely remaining explanations:

```{r}
# 1. Check if the bimodality is driven by a subset of stimuli
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  group_by(stim) |>
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    sd_rt   = sd(rt, na.rm = TRUE),
    n       = n()
  ) |>
  arrange(mean_rt) |>
  print(n = Inf)

# 2. Check if fam (familiarity rating?) predicts the RT peaks
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  ggplot(aes(x = rt, fill = factor(fam), colour = factor(fam))) +
  geom_density(alpha = 0.4)
```

Both plots tell a clear story now. fam only has one level (1) in the famous condition — so it's just a flag meaning "this is a familiar/famous face", not a trial-level recognition indicator. That's not the source of the bimodality. The stim table is very revealing though — look at the n column. Most stimuli appear \~20-74 times, but a handful appear only 1-3 times (stims 91, 83, 153, 130, 110, 43). These look like stray novel face IDs that got miscoded as famous, or test/practice stimuli that leaked into the data. The multimodal density is almost certainly driven by the unequal number of presentations per stimulus creating clusters — the most-presented stimuli dominate the density and each creates its own little peak.

```{r}
# Confirm: plot density coloured by presentation frequency group
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  add_count(stim) |>
  mutate(freq_group = cut(n, breaks = c(0, 5, 30, Inf), 
                          labels = c("rare (<5)", "medium (5-30)", "common (>30)"))) |>
  ggplot(aes(x = rt, fill = freq_group, colour = freq_group)) +
  geom_density(alpha = 0.4)

# And flag the suspicious single-appearance stimuli
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  count(stim) |>
  filter(n < 5)
```

Yes, that makes perfect sense and completely explains the pattern! The design is:

Famous stimuli: repeated across blocks (hence n=30-74) → participants see the same famous faces multiple times Novel stimuli: each one appears only once across the whole experiment (hence n≈1 per stimulus in the novel condition)

So the spiky famous distribution is simply the result of within-participant repetition of the same faces — as participants see the same famous face 2-3 times across blocks, their RTs become more consistent/stereotyped for that specific stimulus, and the density of repeated identical stimuli creates those sharp peaks. You can verify this cleanly:

```{r}
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  count(stim, cond) |>
  group_by(cond) |>
  summarise(
    mean_n    = mean(n),
    median_n  = median(n),
    min_n     = min(n),
    max_n     = max(n),
    .groups = "drop"
  )
```

That confirms the design perfectly. Famous stimuli appear \~36 times (≈30 participants × \~1.2 blocks on average), novel stimuli appear \~20 times — so novel stimuli are also repeated, just less frequently than famous ones. This actually reframes the whole question. The novel condition is also repeated, yet its density is smooth. So repetition alone isn't causing the spikiness — the difference is that famous faces produce much more stereotyped, consistent RTs across repetitions than novel faces. Participants respond to the same famous face with very similar RTs each time they see it, whereas novel face RTs stay more variable across repetitions. This is actually a theoretically meaningful finding in itself — it suggests that familiarity creates a more automatised, consistent recognition response, whereas novel face processing stays variable. Worth flagging to your collaborator as a potentially interesting result rather than a data quality concern. The short summary of the whole investigation:

❌ Not a timing/discretisation issue ❌ Not driven by orientation ❌ Not outlier participants ❌ Not miscoded stimuli ✅ Famous faces produce highly stereotyped RTs across repetitions, creating sharp stimulus-specific peaks that sum to a spiky aggregate distribution — novel faces don't show this despite also being repeated

```{r}
# Check within-participant repetition for both conditions
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  count(pid, stim, cond) |>
  group_by(cond) |>
  summarise(
    max_per_pid  = max(n),
    mean_per_pid = mean(n),
    any_repeated = any(n > 1),
    .groups = "drop"
  )
```

check

```{r}
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "novel") |>
  count(pid, stim) |>
  filter(n > 1) 
```

Perfect — just 2 novel stimuli repeated, both from the same participant (pid 40). Almost certainly a randomisation glitch for that one participant rather than anything systematic. Completely negligible and nothing to worry about. So the full picture is now resolved:

Novel faces: shown once per participant ✅ (one minor exception: pid 40 saw 2 novel stimuli twice) Famous faces: shown \~3 times per participant across blocks ✅ Spiky RT distribution: a clean signature of within-participant RT stereotyping for repeatedly-seen famous faces ✅ Not a data quality, timing, orientation, or coding issue ✅

Worth documenting this somewhere — either as a note in the analysis script or flagging to your collaborator — since reviewers might also notice the unusual density shape and ask about it. A one-line comment in the code would suffice:

```{r}
# Note: the multimodal RT density for famous faces in Exp 3 reflects
# within-participant RT stereotyping across block repetitions (~3x per participant)
# of the same famous face stimuli. This is expected given the design and is not
# a data quality issue. Novel faces are shown once per participant (one exception:
# pid 40 saw stims 25 and 52 twice, likely a randomisation glitch).
```

## check Exp 4

```{r}
read_csv(here("Exp_4/data/data_exp_4.csv")) |>
  mutate(cond = str_to_lower(cond),
         cond = dplyr::recode(cond, familiar = "famous", novel = "novel")) |>
  count(pid, stim, cond) |>
  group_by(cond) |>
  summarise(
    max_per_pid  = max(n),
    mean_per_pid = mean(n),
    any_repeated = any(n > 1),
    .groups = "drop"
  )
```

```{r}
read_csv(here("Exp_4/data/data_exp_4.csv")) |>
  mutate(cond = str_to_lower(cond),
         cond = dplyr::recode(cond, familiar = "famous", novel = "novel")) |>
  group_by(pid, block) |>
  summarise(n = n(), .groups = "drop") |>
  summarise(
    n_blocks     = length(unique(block)),
    trials_block = mean(n)
  )
```

```{r}
# What do we have to work with?
read_csv(here("Exp_4/data/data_exp_4.csv")) |> glimpse()

# Compare RT distributions across blocks for Exp 3 vs Exp 4
data_all |>
  filter(experiment %in% c(3, 4)) |>
  mutate(experiment = paste("Experiment", experiment)) |>
  ggplot(aes(x = rt, fill = cond, colour = cond)) +
  geom_density(alpha = 0.4) +
  scale_fill_manual(values  = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  facet_grid(block ~ experiment, scales = "free_y") +
  labs(x = "Response time [s]", y = "Density")
```

```{r}
# Compare the famous vs novel RT and accuracy differences between Exp 3 and 4
data_all |>
  filter(experiment %in% c(3, 4)) |>
  group_by(experiment, cond) |>
  summarise(
    mean_rt  = mean(rt, na.rm = TRUE),
    mean_acc = mean(acc, na.rm = TRUE),
    n_trials = n(),
    .groups  = "drop"
  ) |>
  pivot_wider(names_from = cond, 
              values_from = c(mean_rt, mean_acc, n_trials)) |>
  mutate(
    rt_diff  = mean_rt_famous  - mean_rt_novel,
    acc_diff = mean_acc_famous - mean_acc_novel
  )
```

```{r}
# Check accuracy distribution across participants for Exp 4 famous
# to see if some participants are at chance
data_aldatal |>
  filter(experiment == 4) |>
  group_by(pid, cond) |>
  summarise(acc = mean(acc), .groups = "drop") |>
  ggplot(aes(x = acc, fill = cond, colour = cond)) +
  geom_histogram(alpha = 0.5, binwidth = 0.05, position = "identity") +
  scale_fill_manual(values  = myColors_3) +
  scale_colour_manual(values = myColors_3) +
  facet_wrap(~ cond) +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  labs(x = "Accuracy", y = "Count")
```

```{r}
# How many participants are at or below chance on famous in Exp 4?
data_all |>
  filter(experiment == 4) |>
  group_by(pid, cond) |>
  summarise(acc = mean(acc), .groups = "drop") |>
  filter(cond == "famous") |>
  summarise(
    n_at_chance    = sum(acc <= 0.5),
    n_below_chance = sum(acc < 0.5),
    n_total        = n(),
    prop_at_chance = mean(acc <= 0.5)
  )
```

check pids per exp

```{r}
data_all |>
  group_by(experiment) |>
  summarise(n_pids = n_distinct(pid))
  
```

and now all exps

```{r}
data_all |>
  filter(experiment == 4) |>
  group_by(pid, cond) |>
  summarise(acc = mean(acc), .groups = "drop") |>
  pivot_wider(names_from = cond, values_from = acc) |>
  mutate(overall = (famous + novel) / 2) |>
  summarise(
    n_famous_below_criterion  = sum(famous  < 0.55),
    n_novel_below_criterion   = sum(novel   < 0.55),
    n_overall_below_criterion = sum(overall < 0.55),
    n_total                   = n()
  )
```

```{r}
data_all |>
  group_by(experiment, pid, cond) |>
  summarise(acc = mean(acc), .groups = "drop") |>
  pivot_wider(names_from = cond, values_from = acc) |>
  mutate(overall = rowMeans(across(-c(experiment, pid)), na.rm = TRUE)) |>
  group_by(experiment) |>
  summarise(
    n_famous_below_criterion  = sum(famous  < 0.55, na.rm = TRUE),
    n_novel_below_criterion   = sum(novel   < 0.55, na.rm = TRUE),
    n_overall_below_criterion = sum(overall < 0.55, na.rm = TRUE),
    n_total                   = n()
  )
```

```{r}
# Per-stimulus mean RT in Exp 3 famous condition
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  group_by(stim) |>
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    sd_rt   = sd(rt, na.rm = TRUE),
    n       = n()
  ) |>
  filter(n > 5) |>  # exclude the rare/miscoded ones
  ggplot(aes(x = reorder(factor(stim), mean_rt), y = mean_rt)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_rt - sd_rt, ymax = mean_rt + sd_rt), width = 0.2) +
  labs(x = "Stimulus ID", y = "Mean RT [s]",
       title = "Exp 3: Per-stimulus mean RT (famous faces)") +
  theme(axis.text.x = element_text(angle = 90, size = 6))
```

And the key comparison — does this stimulus-level variability exist in Exp 1 novel faces (which are also repeated, just once each per participant)?

```{r}
# Compare stimulus-level RT variance across experiments
# Exp 3 famous
exp3_stim_var <- read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  group_by(stim) |>
  filter(n() > 5) |>
  summarise(mean_rt = mean(rt, na.rm = TRUE), .groups = "drop") |>
  summarise(
    sd_of_means = sd(mean_rt),
    range       = max(mean_rt) - min(mean_rt),
    experiment  = "Exp 3 (famous)"
  )

# Exp 1 learned - also repeated stimuli, for comparison
exp1_stim_var <- read_csv(here("Exp_1/data/data.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "learned") |>
  group_by(stim) |>
  filter(n() > 5) |>
  summarise(mean_rt = mean(rt, na.rm = TRUE), .groups = "drop") |>
  summarise(
    sd_of_means = sd(mean_rt),
    range       = max(mean_rt) - min(mean_rt),
    experiment  = "Exp 1 (learned)"
  )

bind_rows(exp3_stim_var, exp1_stim_var)
```

```{r}
# Confirm by checking RT range per experiment
data_all |>
  group_by(experiment) |>
  summarise(
    min_rt  = min(rt, na.rm = TRUE),
    max_rt  = max(rt, na.rm = TRUE),
    range   = max_rt - min_rt,
    sd_rt   = sd(rt, na.rm = TRUE)
  )
```

```{r}
# Per-stimulus mean RT by condition and experiment
# Need raw files for Exp 1 and 3 which have stim IDs
# Exp 2 and 4 don't have stim variable so we can't do this for those

exp1_stim_rt <- read_csv(here("Exp_1/data/data.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  group_by(stim, cond) |>
  filter(n() > 5) |>
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    sd_rt   = sd(rt, na.rm = TRUE),
    n       = n(),
    .groups = "drop"
  ) |>
  mutate(experiment = 1)

exp3_stim_rt <- read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  group_by(stim, cond) |>
  filter(n() > 5) |>
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    sd_rt   = sd(rt, na.rm = TRUE),
    n       = n(),
    .groups = "drop"
  ) |>
  mutate(experiment = 3)

stim_rt <- bind_rows(exp1_stim_rt, exp3_stim_rt)

# Plot
ggplot(stim_rt, aes(x = reorder(factor(stim), mean_rt), y = mean_rt, colour = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_rt - sd_rt, ymax = mean_rt + sd_rt), width = 0.2) +
  scale_colour_manual(values = myColors_3) +
  facet_grid(cond ~ experiment, scales = "free_x",
             labeller = labeller(experiment = ~ paste("Experiment", .x))) +
  labs(x = "Stimulus ID", y = "Mean RT [s]",
       title = "Per-stimulus mean RT by condition and experiment") +
  theme(axis.text.x  = element_text(angle = 90, size = 5),
        legend.position = "none")
```

```{r}
# Novel stimuli appear in both Exp 1 and Exp 3 - do the same IDs show 
# correlated mean RTs across experiments?
exp1_novel <- exp1_stim_rt |> filter(cond == "novel") |> select(stim, mean_rt_exp1 = mean_rt)
exp3_novel <- exp3_stim_rt |> filter(cond == "novel") |> select(stim, mean_rt_exp3 = mean_rt)

inner_join(exp1_novel, exp3_novel, by = "stim") |>
  ggplot(aes(x = mean_rt_exp1, y = mean_rt_exp3)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Mean RT Exp 1 [s]", y = "Mean RT Exp 3 [s]",
       title = "Same novel stimuli: Exp 1 vs Exp 3 mean RT")
```

common axis to scale the plot

```{r}
ggplot(stim_rt, aes(x = reorder(factor(stim), mean_rt), y = mean_rt, colour = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_rt - sd_rt, ymax = mean_rt + sd_rt), width = 0.2) +
  scale_colour_manual(values = myColors_3) +
  facet_grid(cond ~ experiment, scales = "free_x",   # free_x for stim IDs, but fixed y
             labeller = labeller(experiment = ~ paste("Experiment", .x))) +
  coord_cartesian(ylim = c(0, 2.5)) +   # common y axis across all panels
  labs(x = "Stimulus ID", y = "Mean RT [s]",
       title = "Per-stimulus mean RT by condition and experiment (common axis)") +
  theme(axis.text.x  = element_text(angle = 90, size = 5),
        legend.position = "none")
```

```{r}
# Compute within vs between stimulus variance per condition/experiment
stim_rt |>
  group_by(experiment, cond) |>
  summarise(
    between_sd = sd(mean_rt),        # SD of stimulus means = between-stimulus spread
    mean_within_sd = mean(sd_rt),    # average within-stimulus SD
    ratio = between_sd / mean_within_sd,  # signal-to-noise ratio
    .groups = "drop"
  )
```

```{r}
exp3_famous_raw <- read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous")

exp3_famous_stim <- exp3_famous_raw |>
  group_by(stim) |>
  filter(n() > 5) |>
  summarise(mean_rt = mean(rt, na.rm = TRUE))

ggplot() +
  geom_density(data = exp3_famous_raw, aes(x = rt), fill = "gold", alpha = 0.4) +
  geom_rug(data = exp3_famous_stim, aes(x = mean_rt), linewidth = 1, colour = "darkred") +
  labs(x = "RT [s]", y = "Density",
       title = "Exp 3 famous: aggregate RT density with per-stimulus means (rug)")
```

```{r}
# Look at the raw trial-level RT distribution more carefully
# Are the peaks at consistent absolute values across participants?
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  # Round to 2 decimal places and count
  mutate(rt_rounded = round(rt, 2)) |>
  count(rt_rounded) |>
  arrange(desc(n)) |>
  head(20)

# And check if peaks align with multiples of some base unit
# e.g., screen refresh rate (16.67ms at 60Hz)
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  mutate(rt_ms = rt * 1000,
         remainder_60hz = rt_ms %% (1000/60)) |>  # 16.67ms refresh
  ggplot(aes(x = remainder_60hz)) +
  geom_histogram(binwidth = 1) +
  labs(x = "RT mod 16.67ms (screen refresh)", y = "Count",
       title = "Are RTs quantised to screen refresh rate?")
```

```{r}
# Verify the 80ms spacing
top_rts <- c(0.62, 0.70, 0.78, 0.86)
diff(top_rts)  # should all be ~0.08
```

```{r}
# Final confirmation - are ALL the major peaks at multiples of 80ms?
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  mutate(rt_rounded = round(rt, 2),
         multiple_80ms = round(rt_rounded / 0.08)) |>
  count(multiple_80ms, rt_rounded) |>
  arrange(desc(n)) |>
  head(20)
```

```{r}
read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  filter(cond == "famous") |>
  mutate(rt_ms = rt * 1000) |>
  ggplot(aes(x = rt_ms)) +
  geom_histogram(binwidth = 1) +  # 1ms bins to see fine structure
  labs(x = "RT [ms]", y = "Count",
       title = "Exp 3 famous: RT distribution at 1ms resolution") +
  coord_cartesian(xlim = c(400, 900))
```

```{r}
# Check if novel condition shows the same quantisation
exp3 <- read_csv(here("Exp_3/data/data_exp_3.csv")) |>
  mutate(cond = str_to_lower(cond)) |>
  mutate(rt_ms = rt * 1000) |>
  ggplot(aes(x = rt_ms)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~ cond, ncol = 1) +
  labs(x = "RT [ms]", y = "Count",
       title = "Exp 3: RT distribution at 1ms resolution by condition") +
  coord_cartesian(xlim = c(400, 2000))
```

```{r}
exp1 <- read_csv(here("Exp_1/data/data.csv")) |>
  mutate(rt_ms = rt * 1000) |>
  ggplot(aes(x = rt_ms)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~ cond, ncol = 1) +
  labs(x = "RT [ms]", y = "Count",
       title = "Exp 1: RT distribution at 1ms resolution by condition") +
  coord_cartesian(xlim = c(400, 2000))
```

```{r}
p_exp12 <- data_all |>
  filter(experiment %in% c(1, 2)) |>
  mutate(rt_ms = rt * 1000) |>
  ggplot(aes(x = rt_ms)) +
  geom_histogram(binwidth = 1) +
  facet_grid(cond ~ experiment, scales = "free_y",
             labeller = labeller(experiment = ~ paste("Experiment", .x))) +
  labs(x = "RT [ms]", y = "Count") +
  coord_cartesian(xlim = c(400, 2000))

p_exp34 <- data_all |>
  filter(experiment %in% c(3, 4)) |>
  mutate(rt_ms = rt * 1000) |>
  ggplot(aes(x = rt_ms)) +
  geom_histogram(binwidth = 1) +
  facet_grid(cond ~ experiment, scales = "free_y",
             labeller = labeller(experiment = ~ paste("Experiment", .x))) +
  labs(x = "RT [ms]", y = "Count") +
  coord_cartesian(xlim = c(400, 1100))

(p_exp12 | p_exp34) +
  plot_annotation(title = "RT distribution at 1ms resolution by experiment and condition") +
  plot_layout(axes = "collect")

ggsave("sandpit/figures/rt_dist_1ms.png",
       width = 10, height = 7)
```

# 3. Consider a summary figure in the discussion or results.

```{r}
# Data
params <- tribble(
  ~experiment,     ~parameter,    ~direction,        ~effect_size,
  "Exp 1 & 2\n(visual familiarity)", "Drift rate\n(signal quality)",  "Novel > Familiar", "large",
  "Exp 1 & 2\n(visual familiarity)", "Threshold\n(response caution)", "Novel > Familiar", "small",
  "Exp 4\n(person knowledge)",       "Drift rate\n(signal quality)",  "Novel > Famous",   "large",
  "Exp 4\n(person knowledge)",       "Threshold\n(response caution)", "Novel > Famous",   "small"
) |>
  mutate(
    parameter   = fct_inorder(parameter),
    experiment  = fct_inorder(experiment),
    effect_size = factor(effect_size, levels = c("large", "small"))
  )

ggplot(params, aes(x = parameter, y = experiment, 
                   fill = effect_size, label = direction)) +
  geom_tile(colour = "white", linewidth = 2, width = 0.9, height = 0.7) +
  geom_text(size = 3.5, fontface = "bold") +
  scale_fill_manual(
    values = c("large" = "#1D9E75", "small" = "#888780"),
    labels = c("large" = "Large effect", "small" = "Small effect")
  ) +
  labs(
    x = NULL, y = NULL,
    fill = NULL,
    caption = "Net outcome: novel faces responded to faster and more accurately across experiments"
  ) +
  theme(
    legend.position   = "bottom",
    panel.grid        = element_blank(),
    axis.ticks        = element_blank(),
    panel.background  = element_blank()
  )
```

that looks rubbish

```{r}
params <- tribble(
  ~experiment, ~familiarity_type,  ~parameter,   ~median, ~lower,  ~upper,  ~excluded,
  # Drift rate differences (Novel - Familiar/Famous, positive = novel advantage)
  "Exp 1",    "Visual",            "Drift rate",   1.355,  1.086,   1.631,   FALSE,
  "Exp 2",    "Visual",            "Drift rate",   1.099,  0.849,   1.349,   FALSE,
  "Exp 3",    "Person knowledge",  "Drift rate",  -1.829, -2.193,  -1.480,   TRUE,
  "Exp 4",    "Person knowledge",  "Drift rate",   2.938,  1.480,   3.335,   FALSE,
  # Threshold differences (Novel - Learned/Famous, positive = novel advantage)
  "Exp 1",    "Visual",            "Threshold",    0.082,  0.014,   0.150,   FALSE,
  "Exp 2",    "Visual",            "Threshold",    0.194,  0.134,   0.254,   FALSE,
  "Exp 3",    "Person knowledge",  "Threshold",   -0.243, -0.284,  -0.204,   TRUE,
  "Exp 4",    "Person knowledge",  "Threshold",    0.311,  0.261,   0.363,   FALSE,
) |>
  mutate(
    experiment       = fct_inorder(experiment),
    familiarity_type = fct_inorder(familiarity_type),
    parameter        = factor(parameter, levels = c("Drift rate", "Threshold")),
    colour_group     = case_when(
      excluded                          ~ "excluded",
      median > 0 & parameter == "Drift rate" ~ "drift",
      median > 0 & parameter == "Threshold"  ~ "threshold",
      TRUE                              ~ "excluded"
    )
  )

ggplot(params, aes(x = median, y = experiment, colour = colour_group)) +
  # Reference line
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60", linewidth = 0.4) +
  # CI intervals
  geom_linerange(aes(xmin = lower, xmax = upper, alpha = excluded),
                 linewidth = 1.2) +
  # Points
  geom_point(aes(alpha = excluded, shape = excluded), size = 3.5, fill = "white") +
  # Excluded label
  geom_text(
    data = filter(params, excluded),
    aes(label = "excluded\n(timing artefact)"),
    hjust  = -0.15, size = 2.8, colour = "grey60", lineheight = 0.9
  ) +
  scale_colour_manual(
    values = c(
      "drift"     = "#1D9E75",
      "threshold" = "#888780",
      "excluded"  = "grey75"
    ),
    guide = "none"
  ) +
  scale_alpha_manual(values = c("FALSE" = 1, "TRUE" = 0.35), guide = "none") +
  scale_shape_manual(values  = c("FALSE" = 21, "TRUE" = 21),  guide = "none") +
  scale_x_continuous(breaks = seq(-2, 4, by = 1)) +
  facet_wrap(
    ~ parameter, ncol = 2, scales = "free_x",
    labeller = labeller(parameter = c(
      "Drift rate" = "Drift rate (signal quality)",
      "Threshold"  = "Threshold (response caution)"
    ))
  ) +
  labs(
    x = "Posterior median difference (Novel > Familiar/Famous) [95% CI]",
    y = NULL,
    caption = str_wrap(
      "Positive values indicate a novel face advantage. Points show posterior medians; 
       lines show 95% credible intervals. Exp 3 excluded from interpretation due to 
       RT timing quantisation artefact (see main text).",
      width = 90
    )
  ) +
  theme_bw() +
  theme(
    text             = element_text(size = 11),
    strip.text       = element_text(size = 11, face = "bold"),
    strip.background = element_rect(fill = "grey95", colour = "grey80"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_line(colour = "grey92"),
    axis.text.y      = element_text(size = 10),
    plot.caption     = element_text(size = 8, colour = "grey50", hjust = 0),
    plot.caption.position = "plot"
  )
```
