---
title: "model - exploratory"
author: "Raph & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

This file fits exploratory (not pre-registered) LBA models for Exp 4.
Three models are fit: bias (A varies by response), t0 (non-decision time varies
by condition), and full (both A and t0 vary). Results are compared against the
preregistered model at the end.

```{r}
#| label: setup
#| include: false

pkgs <- c(
  "EMC2", "tidyverse", "here", "parallel", "future"
  )
vapply(
  pkgs, library, logical(1), character.only = TRUE, logical.return = TRUE
  )

## set options
options(mc.cores = parallel::detectCores(),
        future.fork.enable = TRUE,
        future.rng.onMisuse = "ignore") ## automatically set in RStudio

supportsMulticore()

detectCores()

plan(multicore)
```

# 1. Data

raw data

```{r}
#| label: read-data

raw <- read_csv(here("exp_4", "data", "data_exp_4.csv"))
head(raw)
glimpse(raw)
```

```{r}
#| label: wrangle

data_emc <- raw |>
  select(pid, cond, keypress, rt) |>
  rename(subjects = pid, S = cond, R = keypress) |>
  mutate(
    subjects = factor(as.integer(factor(subjects))),
    S        = factor(S, levels = c("Novel", "Famous")),
    R        = if_else(R == "q", "Famous", "Novel"),
    R        = factor(R, levels = c("Novel", "Famous"))
  ) |>
  as.data.frame()
```

Models (if previously computed and necessary)

```{r}
#| label: read-models

# LBA_exp4_bias <- readRDS("exp_1/models/LBA_exp4_bias.rds")
# LBA_exp4_t0 <- readRDS("exp_1/models/LBA_exp4_t0.rds")
# LBA_exp4_full <- readRDS("exp_1/models/LBA_exp4_full.rds")
```

# 2. Shared settings

```{r}
#| label: shared-settings

matchfun <- function(d) d$S == d$lR

v_mean <- c(
  "v_SNovel:lMFALSE"  = 0, "v_SFamous:lMFALSE" = 0,
  "v_SNovel:lMTRUE"   = 1, "v_SFamous:lMTRUE"  = 1,
  sv_lMTRUE           = log(.5)
)
v_sd <- c(
  "v_SNovel:lMFALSE"  = 2, "v_SFamous:lMFALSE" = 2,
  "v_SNovel:lMTRUE"   = 2, "v_SFamous:lMTRUE"  = 2,
  sv_lMTRUE           = .5
)
```

# 3. Bias model

```{r}
#| label: design-bias

design_bias <- design(
  data     = data_emc,
  model    = LBA,
  matchfun = matchfun,
  formula  = list(
    v  ~ 0 + S:lM,
    sv ~ 0 + lM,
    B  ~ 0 + lR,
    A  ~ 0 + lR,
    t0 ~ 1
  ),
  constants = c(sv_lMFALSE = log(1))
)

mu_mean_bias <- c(v_mean,
  B_lRNovel = log(1), B_lRFamous = log(1),
  A_lRNovel = log(.5), A_lRFamous = log(.5),
  t0 = log(.3)
)

mu_sd_bias <- c(v_sd,
  B_lRNovel = .5, B_lRFamous = .5,
  A_lRNovel = .3, A_lRFamous = .3,
  t0 = .3
)

prior_bias <- prior(
  design_bias,
  type  = "standard",
  pmean = mu_mean_bias,
  psd   = mu_sd_bias
)
```

```{r}
#| label: fit-bias
#| eval: false

LBA_exp4_bias <- make_emc(
  data_emc, 
  design_bias,
  type = "standard", 
  prior = prior_bias,
  compress = TRUE
)

LBA_exp4_bias <- fit(
  LBA_exp4_bias,
  cores_for_chains = 3,
  cores_per_chain = 9,
  iter            = 5000,
  step_size       = 500,
  verbose         = TRUE,
  fileName        = here("exp_4", "models", "tmp.RData")
)

saveRDS(LBA_exp4_bias, "exp_4/models/LBA_exp4_bias.rds")
```

```{r}
#| label: load-bias

LBA_exp4_bias <- readRDS("exp_4/models/LBA_exp4_bias.rds")
```

```{r}
#| label: check-bias

check(LBA_exp4_bias)
summary(LBA_exp4_bias)
#plot(LBA_exp4_bias)
#get_pars(LBA_exp4_bias, map = TRUE)
```

```{r}
#| label: plot-bias

plot_pars(LBA_exp4_bias, selection = "mu", layout = c(2, 5))
```

```{r}
#| label: pp-bias
#| eval: false

pp_bias <- predict(LBA_exp4_bias, n_cores = 24)
saveRDS(pp_bias, "exp_4/models/pp_LBA_exp4_bias.rds")
```

```{r}
#| label: plot-fit-bias

pp_bias <- readRDS("exp_4/models/pp_LBA_exp4_bias.rds")

png("exp_4/figures/exploratory/pp_density_bias.png", width = 8, height = 6, units = "in", res = 150)
plot_density(
  data_emc, 
  pp_bias, 
  factors = "S"
)
dev.off()

png("exp_4/figures/exploratory/pp_cdf_bias.png", width = 8, height = 6, units = "in", res = 150)
plot_cdf(
  data_emc,
  pp_bias,  
  factors = "S"
)
dev.off()
```

# 4. T0 model

```{r}
#| label: design-t0

design_t0 <- design(
  data     = data_emc,
  model    = LBA,
  matchfun = matchfun,
  formula  = list(
    v  ~ 0 + S:lM,
    sv ~ 0 + lM,
    B  ~ 0 + lR,
    A  ~ 1,
    t0 ~ 0 + S
  ),
  constants = c(sv_lMFALSE = log(1))
)

mu_mean_t0 <- c(v_mean,
  B_lRNovel = log(1), B_lRFamous = log(1),
  A = log(.5),
  t0_SNovel = log(.3), t0_SFamous = log(.3)
)

mu_sd_t0 <- c(v_sd,
  B_lRNovel = .5, B_lRFamous = .5,
  A = .3,
  t0_SNovel = .3, t0_SFamous = .3
)

prior_t0 <- prior(
  design_t0,
  type  = "standard",
  pmean = mu_mean_t0,
  psd   = mu_sd_t0
)

```

```{r}
#| label: fit-t0
#| eval: false

LBA_exp4_t0 <- make_emc(
  data_emc, 
  design_t0,
  type = "standard", 
  prior = prior_t0,
  compress = TRUE
)

LBA_exp4_t0 <- fit(
  LBA_exp4_t0,
  cores_for_chains = 3,
  cores_per_chain = 9,
  iter            = 5000,
  step_size       = 500,
  verbose         = TRUE,
  fileName        = here("exp_4", "models", "tmp.RData")
)

LBA_exp4_t0 <- readRDS("exp_4/models/LBA_exp4_t0.rds")
```

```{r}
#| label: load-t0

LBA_exp4_t0 <- readRDS("exp_4/models/LBA_exp4_t0.rds")
```

```{r}
#| label: check-t0

check(LBA_exp4_t0)
summary(LBA_exp4_t0)
#plot(LBA_exp4_t0)
#get_pars(LBA_exp4_t0, map = TRUE)
```

```{r}
#| label: plot-t0

plot_pars(LBA_exp4_t0, selection = "mu", layout = c(2, 5))
```

```{r}
#| label: pp-t0
#| eval: false

pp_t0 <- predict(LBA_exp4_t0, n_cores = 24)
saveRDS(pp_t0, "exp_4/models/pp_LBA_exp4_t0.rds")
```

```{r}
#| label: plot-fit-t0

pp_t0 <- readRDS("exp_4/models/pp_LBA_exp4_t0.rds")

png("exp_4/figures/exploratory/pp_density_t0.png", width = 8, height = 6, units = "in", res = 150)
plot_density(
  data_emc, 
  pp_t0, 
  factors = "S"
)
dev.off()

png("exp_4/figures/exploratory/pp_cdf_t0.png", width = 8, height = 6, units = "in", res = 150)
plot_cdf(
  data_emc,
  pp_t0,  
  factors = "S"
)
dev.off()
```

# 5. Full model

```{r}
#| label: design-full

design_full <- design(
  data     = data_emc,
  model    = LBA,
  matchfun = matchfun,
  formula  = list(
    v  ~ 0 + S:lM,
    sv ~ 0 + lM,
    B  ~ 0 + lR,
    A  ~ 0 + lR,
    t0 ~ 0 + S
  ),
  constants = c(sv_lMFALSE = log(1))
)

mu_mean_full <- c(v_mean,
  B_lRNovel = log(1),  B_lRFamous = log(1),
  A_lRNovel = log(.5), A_lRFamous = log(.5),
  t0_SNovel = log(.3), t0_SFamous = log(.3)
)

mu_sd_full <- c(v_sd,
  B_lRNovel = .5, B_lRFamous = .5,
  A_lRNovel = .3, A_lRFamous = .3,
  t0_SNovel = .3, t0_SFamous = .3
)

prior_full <- prior(
  design_full,
  type  = "standard",
  pmean = mu_mean_full,
  psd   = mu_sd_full
)
```

```{r}
#| label: fit-full
#| eval: false

LBA_exp4_full <- make_emc(
  data_emc, 
  design_full,
  type = "standard", 
  prior = prior_full,
  compress = TRUE
)

LBA_exp4_full <- fit(
  LBA_exp4_full,
  cores_for_chains = 3,
  cores_per_chain = 9,
  iter            = 5000,
  step_size       = 500,
  verbose         = TRUE,
  fileName        = here("exp_4", "models", "tmp.RData")
)

saveRDS(LBA_exp4_full, "exp_4/models/LBA_exp4_full.rds")
```

```{r}
#| label: load-full

LBA_exp4_full <- readRDS("exp_4/models/LBA_exp4_full.rds")
```

```{r}
#| label: check-full

check(LBA_exp4_full)
summary(LBA_exp4_full)
#plot(LBA_exp4_full)
#get_pars(LBA_exp4_full, map = TRUE)
```

```{r}
#| label: plot-full

plot_pars(LBA_exp4_full, selection = "mu", layout = c(2, 5))
```

```{r}
#| label: pp-full
#| eval: false

pp_full <- predict(LBA_exp4_full, n_cores = 24)
saveRDS(pp_full, "exp_4/models/pp_LBA_exp4_full.rds")
```

```{r}
#| label: plot-fit-full

pp_full <- readRDS("exp_4/models/pp_LBA_exp4_full.rds")

png("exp_4/figures/exploratory/pp_density_full.png", width = 8, height = 6, units = "in", res = 150)
plot_density(
  data_emc, 
  pp_full, 
  factors = "S"
)
dev.off()

png("exp_4/figures/exploratory/pp_cdf_full.png", width = 8, height = 6, units = "in", res = 150)
plot_cdf(
  data_emc,
  pp_full,  
  factors = "S"
)
dev.off()
```

# 6. Model comparison

```{r}
#| label: model-comparison

LBA_exp4 <- readRDS("exp_1/models/LBA_exp4.rds")
LBA_exp4_bias <- readRDS("exp_1/models/LBA_exp4_bias.rds")
LBA_exp4_t0 <- readRDS("exp_1/models/LBA_exp4_t0.rds")
LBA_exp4_full <- readRDS("exp_1/models/LBA_exp4_full.rds")

model_list <- list(
  preregistered = LBA_exp4,
  bias          = LBA_exp4_bias,
  t0            = LBA_exp4_t0,
  full          = LBA_exp4_full
)

compare(model_list, cores_per_prop = 6)
```
