---
title: "wrangle"
author: "Fournier Raphaël"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load ##

```{r load-pkg}
pkg <- c("tidyverse", "RColorBrewer", "patchwork", "gtsummary", "paletteer", "here")

lapply(pkg, library, character.only = TRUE)
```

## plot settings ##

```{r}
## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

theme settings for ggplot

```{r, eval = F}
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face="bold"), 
          title = element_text(size = 18, face="bold"),
          legend.position = "bottom")
)
```
custom_color
```{r}
myColors <- c("novel" = paletteer_d("rcartocolor::Safe",4)[1],"familiar" =  paletteer_d("rcartocolor::Safe",4)[3])
```

## section 1 - read in the raw data ##

This chunk reads in the main raw data files

```{r}
raw <- list.files(here("Exp_4", "data", "data"), pattern = "*csv", full.names = TRUE,
                  recursive = TRUE) %>% # check out list.files for info on selecting a bunch of files
  lapply(read_csv)
```
#save raw_data
```{r}
write_csv(raw,here::here("Exp_4", "data","raw_exp_4.csv"))
```

```{r}
#Wrangle the raw data to extract the face recognition task data
wrangle <- raw %>%
  filter(!is.na(recognition_trial_number)) %>%
  dplyr::rename(keypress = `key_resp_recognition.keys`, cond = identity_type, rt = `key_resp_recognition.rt`, pid = participant)%>%
  relocate(pid, .before = keypress) %>%
  select(pid, keypress, cond, rt) %>%
  mutate(block = rep(1:3, each = 60, times = 46),
         cond = as.factor(cond),
         keypress = as.factor(keypress),
         acc = if_else(keypress == 'q' & cond == "familiar", 1,
                        if_else(keypress == 'p' & cond == "familiar", 0,
                        if_else(keypress == 'p' & cond == "novel", 1,
                        if_else(keypress == 'q' & cond == "novel", 0,0)))))%>%
  relocate(any_of(c("block", "cond")), .before = keypress) %>%
  arrange(pid)
```





data check

```{r}
wrangle %>% 
   distinct(pid)
```

#Save raw data
```{r}
write_csv(wrangle, here::here("Exp_4", "data","wrangle_exp_4.csv"))
```



### Wrangle the Familiarity ratings ###
```{r}
data_ratings <- raw %>%
  filter(!is.na(familiarity_rating)) %>%
  select(participant, familiarity_rating, valence_rating, name_correct) %>%
  mutate(rename(pid = "participant"))
  
```

```{r}
#list of participants with number of fam ratings between 7-10 is lower than 30
number_ratings <- data_ratings %>%
  select(pid, familiarity_rating) %>%
  group_by(pid) %>%
  mutate(number_fam = sum(familiarity_rating > 6)) %>%
  select(pid, number_fam) %>%
  distinct() %>%
  filter(number_fam < 30)
```

```{r}
#remove these participants
wrangle <- wrangle %>%
  filter(!pid %in% number_ratings$pid)
```

```{r}
#check participants
wrangle %>% 
   distinct(pid)
```

### Exclusion criteria (preregistration OSF) ###

## Missed trials

# Calculate the number of missed trials for each participant and removing the ones with more than 40% of missed trials (72 trials)
```{r}
wrangle <- wrangle %>% 
  mutate(missed_trial = if_else(
        is.na(keypress), "yes", "no"))
filtered_subjects <- wrangle %>%  
  group_by(pid) %>%
  summarise(missed_count = sum(missed_trial == "yes", na.rm = TRUE)) %>%
  filter(missed_count > 45)#here 45 is 25% of the total number of trials (180)
wrangle <- wrangle %>%
  filter(!pid %in% filtered_subjects$pid)
```

```{r}
#check participants
wrangle %>% 
   distinct(pid)
```

#Checking for each participant the percentage of missed trials
```{r}
wrangle %>%
  select(pid,missed_trial) %>%
  tbl_summary(
    by = pid) %>%
  bold_labels()
```

#Remove NA (missed trials)
```{r}
wrangle <- wrangle %>%
  drop_na(rt)
```
#Save_data
```{r}
write_csv(wrangle, here("Exp_4", "data", "data_exp_4.csv"))
```

## Accuracy 
data check

```{r}
data <- wrangle
data %>%
  distinct(pid, block, cond, acc)

data %>%
  group_by(pid, block, cond) %>% 
  tally(acc)

```

#Checking participant on accuracy (Overall and per condtion) for each subject
```{r}
#Check overall accuracy
acc_pid_check <- data %>%
  group_by(pid) %>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)

#Check accuracy per condition
acc_pid_check_cond <- data %>%
  group_by(cond) %>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100,
            sd = sd(sum(acc)))
```

#Plot check overall accuracy
```{r}
p.acc <-ggplot(acc_pid_check, aes(x=pid, y=perc)) +
   geom_bar(stat="identity") +
   geom_hline(yintercept = 95, linetype = "dashed", color = "red")+
   geom_hline(yintercept = 55, linetype = "dashed", color = "red")+
   scale_fill_paletteer_d("rcartocolor::Safe") +
   scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Overall accuracy") +
   xlab("Pid") +
   ylab("Accuracy [%]") + ylim(c(0,100))
p.acc
ggsave("Exp_4/figures/acc_pid_barplot.jpeg",
       width = 8, height = 6)
```

#Remove participants if overall accuracy is <55% or >95%
```{r}
filtered_subjects_acc <- data %>%  
  group_by(pid) %>%
  summarise(accuracy = sum(acc),
            n = n(),
            perc = accuracy/n*100) %>%
  filter(perc > 95 | perc < 55)
data <- data %>%
  filter(!pid %in% filtered_subjects_acc$pid)
```

#Plot check overall accuracy again
```{r}
#Check overall accuracy
acc_pid_check_without <- data %>%
  group_by(pid) %>%
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)

p.acc_without <-ggplot(acc_pid_check_without, aes(x=pid, y=perc)) +
   geom_bar(stat="identity") +
   geom_hline(yintercept = 95, linetype = "dashed", color = "red")+
   geom_hline(yintercept = 55, linetype = "dashed", color = "red")+
   scale_fill_paletteer_d("rcartocolor::Safe") +
   scale_colour_paletteer_d("rcartocolor::Safe")  +
   ggtitle("Overall accuracy") +
   xlab("Pid") +
   ylab("Accuracy [%]") + ylim(c(0,100))
p.acc_without
ggsave("Exp_4/figures/acc_pid_barplot_without.jpeg",
       width = 8, height = 6)
```

#Saving raw data
```{r}
write_csv(data, "Exp_4/data/data_exp_4.csv")
data<-read_csv("Exp_4/data/data_exp_4.csv")
```


## section 3 - create summary data ##

first, create summary data for rt and accuracy at the pid level and at the 
group level

at the pid level
### rt ###
```{r}
rt_pid <- data %>% 
  mutate(block = as.factor(block))%>%
  group_by(pid,block, cond) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = n(), # n here is the total trials per grouping
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_pid
```


### acc ###
```{r}
acc_pid <- data %>% 
  group_by(pid, block, cond) %>% 
  summarise(sum = sum(acc),
            n = n(), # n here is the total trials per grouping
            perc = sum/n*100)
acc_pid
```

at the group level

### rt ###
```{r}
rt_group <- data %>% 
  group_by(block, cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_group
```

### acc ###
```{r}
acc_group <- acc_pid %>% 
  group_by(cond,block) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group
```


### without block###
## rt group##
```{r}
rt_group_wblock <- data %>% 
  group_by(cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96)
rt_group_wblock
```

## rt pid ##
```{r}
rt_pid_wblock <- data %>% 
  group_by(pid,cond) %>% 
  drop_na(rt) %>%
  summarise(mean = mean(rt),
            sd = sd(rt),
            n = length(unique(pid)), # n here is the total subjs
            sem = (sd/sqrt(n)),
            ci = sem*1.96) %>%
  left_join(rt_group_wblock, by = join_by(cond))

rt_pid_wblock
```
## acc group##
```{r}
acc_group_wblock <- acc_pid %>% 
  group_by(cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc)
acc_group_wblock
```
## acc pid ##
```{r}
acc_pid_wblock <- acc_pid %>% 
  group_by(pid,cond) %>% 
  summarise(mean_sum = mean(sum),
            n = n(), # n here is the total trials per grouping
            mean_perc = mean(perc),
            sd=sd(perc),
            sem = (sd/sqrt(n))) %>% 
  rename(sum=mean_sum, perc=mean_perc) %>%
  left_join(acc_group_wblock, by = join_by(cond))
acc_pid_wblock
```

## section 4 - plot ##

just a few quick and dirty plots for now

density

rt

```{r}
p4.1 <- ggplot(data, aes(x=rt, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by block and condition") +
   facet_wrap(~block) +
   xlab("Response time [s]") +
   ylab("Density") +
   xlim(0,1.75)
p4.1

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/rt_density_pid.jpeg",
       #width = 8, height = 6)
```

acc

```{r}
p4.2 <- ggplot(data, aes(x=acc, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by block and condition") +
   facet_wrap(~block) +
   xlab("Accuracy") +
   ylab("Density")  
p4.2 

#ggsave("/Users/rfournier/Rstudio/pilot5_dmc/figures_exp_1/acc_density_pid.jpeg",
       #width = 8, height = 6)
```


checking error distribution
#By block
```{r}
data_error <- data %>%
  filter(acc == 0)

p.4.2.1 <- ggplot(data_error, aes(x=rt, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by block and condition for errors") +
   facet_wrap(~block) +
   xlab("Response time [s]") +
   ylab("Density") +
   xlim(0,1.75)
p.4.2.1

ggsave("Exp_4/figures/errors_distr_block.jpeg",
       width = 8, height = 8)
```

#Overall
```{r}

p.4.2.2 <- ggplot(data_error, aes(x=rt, fill=cond, colour=cond)) +
   geom_density(alpha=0.5) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by condition for errors") +
   xlab("Response time [s]") +
   ylab("Density") +
   xlim(0,1.75)
p.4.2.2

ggsave("Exp_4/figures/errors_distr.jpeg",
       width = 8, height = 8)
```


summary plots

rt

```{r}
p4.3 <- ggplot(rt_pid, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond)) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Mean response time by block and condition") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
  ylim(0,1)
p4.3

ggsave("Exp_4/figures/rt_line_pid.jpeg",
      width = 8, height = 8)
```

acc

```{r}
p4.4 <- ggplot(acc_pid, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3) +
   geom_line(aes(group = cond)) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by block and condition") +
   facet_wrap(~pid) +
   xlab("Blocks") +
   ylab("Accuracy [%]") + ylim(c(0,100))
  
p4.4

ggsave("Exp_4/figures/acc_line_pid_prob.jpeg",
       width = 8, height = 8)
```

group level summary data

rt

```{r}
p4.5 <- ggplot(rt_group, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by block and condition") +
   xlab("Blocks") +
   ylab("Mean response time [s]") +
   ylim(0,1)
p4.5

ggsave("Exp_4/figures/rt_line_group.jpeg",
        width = 7, height = 8)
```

acc

```{r}
p4.6 <- ggplot(acc_group, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by block and condition") +
   xlab("Blocks") +
   ylab("Accuracy [%]") +
   ylim(30,100)

p4.6

ggsave("Exp_4/figures/acc_line_group.jpeg",
        width = 7, height = 8)
```

plot group data together

```{r}
p4.7 <- p4.5 | p4.6
p4.7

ggsave("Exp_4/figures/rt_acc_line_group.jpeg",
        width = 15, height = 6)
```

add pid dots to the group data

rt

```{r}
p4.8 <- ggplot(rt_group, aes(x=block, y=mean, 
                           fill=cond, colour=cond)) +
   geom_jitter(data = rt_pid,
               position=position_jitterdodge(dodge.width =1), 
               alpha = 1, colour = "darkgrey") +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = mean-sem, ymax = mean+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("rt by block and condition") +
   ylim(0,1.5)
p4.8
```

acc

```{r}
p4.9 <- ggplot(acc_group, aes(x=block, y=perc, 
                           fill=cond, colour=cond)) +
   geom_jitter(data = acc_pid,
               position=position_jitterdodge(dodge.width =1), 
               alpha = 1, colour = "darkgrey") +
   geom_point(alpha = 3, position = pd2) +
   geom_line(aes(group = cond), position = pd2) +
   geom_errorbar(aes(ymin = perc-sem, ymax = perc+sem),
                width=.2, position=pd2) +
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("acc by block and condition") +
   ylim(0,100)
p4.9
```

plot group data together

```{r}
p4.10 <- p4.8 | p4.9
p4.10

ggsave("figures/rt_acc_line_dots.jpeg",
       width = 10, height = 6)
```





barplot acc
```{r}
p.4.11 <- ggplot(acc_pid_wblock, aes(x = factor(cond),y=perc.y, 
                           fill=cond, colour=cond)) +
   geom_col() +
   geom_errorbar(aes(ymin = perc.y-sem.y, ymax = perc.y+sem.y), col = "black",
                width=.2, position=pd2) +
   geom_point(aes(y = perc.x),
             colour = "black",
             stat = "identity",
             position=pd2,
             alpha = .7)+
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Accuracy by condition") +
   xlab("Conditions") +
   ylab("Accuracy [%]") +
   ylim(0,100)+
   theme(legend.position = "none")

p.4.11

ggsave("Exp_4/figures/acc_barplot_group.jpeg",
        width = 6, height = 8)
```

barplot rt
```{r}
p.4.12 <- ggplot(rt_pid_wblock, aes(x = factor(cond),y=mean.y, 
                           fill=cond, colour=cond)) +
   geom_col() +
   geom_errorbar(aes(ymin = mean.y-sem.y, ymax = mean.y+sem.y), col = "black",
                width=.2, position=pd2) +
   geom_point(aes(y = mean.x),
             colour = "black",
             stat = "identity",
             position=pd2,
             alpha = .7)+
   scale_fill_manual(values = myColors) +
   scale_color_manual(values = myColors) +
   ggtitle("Response time by condition") +
   xlab("Conditions") +
   ylab("Response time [s]") +
   ylim(0,1)+
   theme(legend.position = "none")

p.4.12

ggsave("Exp_4/figures/rt_barplot_group.jpeg",
        width = 6, height = 8)
```


## section 5 - save out some files ##

This is useful for future modelling and/or plotting without re-doing the wrangle
file.

